### 2024-11-18 supp-mat/supp-mat.tex
Add supplementary materials

\documentclass[%
%  reprint,
superscriptaddress,
% groupedaddress,
%unsortedaddress,
% runinaddress,
% frontmatterverbose, 
% preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
%aps,
prl,
%pra,
prb,
% rmp,
%prstab,
% prstper,
%floatfix,
]{revtex4-2}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{blindtext}
\usepackage{float}
\usepackage{caption}
\usepackage{cleveref}
\usepackage{subcaption}
\usepackage{xcolor}

\newcommand{\etal}{{\it et al.}~}
\newcommand{\bom}{\boldsymbol{\omega}}
\newcommand{\hel}{\textsuperscript{4}He }

\def\red#1{\textcolor{red}{#1}}
\def\blue#1{\textcolor{blue}{#1}}
\def\magenta#1{\textcolor{magenta}{#1}}
\newcommand*{\NOTE}[1]{\textbf{\color{red}[#1]}}

\def \s{\mathbf{s}}
\def \v{\mathbf{v}}
\def \x{\mathbf{x}}
\def \r{\mathbf{r}}
\def \k{\mathbf{k}}

\def \cm{\mathrm{cm}}
\def \cms{\mathrm{cm/s}}
\def \sec{\mathrm{s}}
\def \K{\mathrm{K}}

\def\red{\textcolor{red}}

\begin{document}
\preprint{APS/123-QED}

\title{Supplementary Materials: Inverse energy transfer in finite-temperature superfluid vortex reconnections}

\author{P. Z. Stasiak}
\affiliation{School of Mathematics, Statistics and Physics, Newcastle University, Newcastle upon Tyne, NE1 7RU, United Kingdom}

\author{C.F. Barenghi}
\author{A. Baggaley}
\affiliation{School of Mathematics, Statistics and Physics, Newcastle University, Newcastle upon Tyne, NE1 7RU, United Kingdom}

\author{L. Galantucci}
\affiliation{Istituto per le Applicazioni del Calcolo ``M. Picone" IAC CNR, Via dei Taurini 19, 00185 Roma, Italy}

\author{G. Krstulovic}
\affiliation{Universit\'e C\^ote d'Azur, Observatoire de la C\^ote d'Azur, CNRS,Laboratoire Lagrangre, Boulevard de l'Observatoire CS 34229 - F 06304 NICE Cedex 4, France}

\maketitle

\section{Numerical Method}

Using Schwarz mesoscopic model \cite{schwarzThreedimensionalVortexDynamics1988a}, vortex lines can be described as space curves $\s(\xi,t)$ of infinitesimal thickness, with a single quantum of circulation $\kappa=h/m_4=9.97\times10^{-8}\text{m}^2/\text{s}$, where $h$ is Planck's constant, $m_4=6.65\times10^{-27}\text{kg}$ is the mass of one helium atom, $\xi$ is the natural parameterisation, arclength, and $t$ is time. These conditions are a good approximation, since the vortex core radius of superfluid \textsuperscript{4}He($a_0=10^{-10}\text{m}$) is much smaller than any of the length scale of interest in turbulent flows. The equation of motion is
\begin{equation}
	\dot{\s}(\xi,t) = \v_s + \frac{\beta}{1+\beta}\left[\v_{ns}\cdot \s'\right]\s' + \beta\s'\times\v_{ns}+\beta'\s'\times\left[\s'\times \v_{ns}\right],
\end{equation}
where $\dot{\s}=\partial\s/\partial t$, $\s'=\partial\s/\partial \xi$ is the unit tangent vector, $\v_{ns}=\v_n - \v_s$, $\v_n$ and $\v_s$ are the normal fluid and superfluid velocities at $\s$ and $\beta$,$\beta'$ are temperature and Reynolds number dependent mutual fricition coefficients \cite{galantucciNewSelfconsistentApproach2020b}. The superfluid velocity $\v_s$ at a point $\x$ is determined by the Biot-Savart law
\begin{equation}
	\v_s(\x,t) = \frac{\kappa}{4\pi}\oint_{\mathcal{T}}\frac{\s'(\xi,t)\times\left[\x-\s(\xi,t)\right]}{|\x-\s(\xi,t)|}d\xi,
\end{equation}
where $\mathcal{T}$ represents the entire vortex configuration.
There is currently a lack of a well-defined theory of vortex reconnections in superfluid helium, like for the Gross-Pitaevskii equation \cite{villoisIrreversibleDynamicsVortex2020,villoisUniversalNonuniversalAspects2017a,promentMatchingTheoryCharacterize2020a}. An \emph{ad hoc} vortex reconnection algorithm is employed to resolve the collisions of vortex lines \cite{baggaleySensitivityVortexFilament2012a}.

A \emph{two-way model} is crucial to understand the accurately interept the back-reaction effect of the normal fluid on the vortex line and vice-versa \cite{stasiakCrossComponentEnergyTransfer2024}. We self-consistently evolve the normal fluid $\v_n$ with a modified Navier-Stokes equation
\begin{equation}
	\frac{\partial \v_n}{\partial t} + (\v_n\cdot\nabla)\v_n = -\nabla\frac{p}{\rho} + \nu_n\nabla^2\v_n + \frac{\mathbf{F}_{ns}}{\rho_n},
\end{equation}
\begin{equation}
	\mathbf{F}_{ns} = \oint_{\mathcal{T}}\mathbf{f}_{ns}\delta(\x-\x)d\xi, \quad \nabla\cdot\v_n=0,
\end{equation}
where $\rho=\rho_n + \rho_s$ is the total density, $\rho_n$ and $\rho_s$ are the normal fluid and superfluid densities, $p$ is the pressure, $\nu_n$ is the kinematic viscosity of the normal fluid and $\mathbf{f}_{ns}$ is the local friction per unit length \cite{galantucciCoupledNormalFluid2015a}
\begin{equation}
	\mathbf{f}_{ns} = -D\s'\times\left[\s'\times(\dot{\s}-\v_n)\right]-\rho_n\kappa\s'\times(\v_n-\dot{\s}), 
\end{equation}
where $D$ is a coefficient dependent on the vortex Reynolds number and intrinsic properties of the normal fluid.

The results in this Letter are reported in dimensionless units, where the characteristic length scale is $\tilde{\lambda}=D/D_0$, where $D^3=(1\times10^{-3}\text{m})^3$ is the dimensional cube size, $D_0^3=(2\pi)^3$ is the non-dimensional cubic computational domain. The time scale is given by $\tilde{\tau} = \tilde{\lambda}^2\nu_n^0/\nu_n$, where the non-dimensional viscosity $\nu_n^0$ resolves the small scales of the normal fluid. In these simulations, these quantities are $\tilde{\lambda}=1.59\times10^{-4}\text{cm}$, $\nu_n^0=0.16$ and $\tilde{\tau} = 0.183$s at $T=0K$ and at $T=1.9K$ and $\tilde{\tau}=0.242$s at $T=2.1K$.

\bibliography{references}% Produces the bibliography via BibTeX.
\end{document}

### 2024-11-19 supp-mat/supp-mat.tex
Update Supp. Mat.

@@
 
-The results in this Letter are reported in dimensionless units, where the characteristic length scale is $\tilde{\lambda}=D/D_0$, where $D^3=(1\times10^{-3}\text{m})^3$ is the dimensional cube size, $D_0^3=(2\pi)^3$ is the non-dimensional cubic computational domain.
-The time scale is given by $\tilde{\tau} = \tilde{\lambda}^2\nu_n^0/\nu_n$, where the non-dimensional viscosity $\nu_n^0$ resolves the small scales of the normal fluid.
-In these simulations, these quantities are $\tilde{\lambda}=1.59\times10^{-4}\text{cm}$, $\nu_n^0=0.16$ and $\tilde{\tau} = 0.183$s at $T=0K$ and at $T=1.9K$ and $\tilde{\tau}=0.242$s at $T=2.1K$.
-
 \bibliography{references}% Produces the bibliography via BibTeX.

### 2024-11-20 supp-mat/supp-mat.tex
Add text to supp materials

@@
 
+\begin{figure}
+	\centering
+	\includegraphics[width=0.4\textwidth]{schematic.png}
+	\caption{Schematic diagram of the initial vortex configuration.}
+	\label{fig:schematic}
+\end{figure}
+
 Using Schwarz mesoscopic model \cite{schwarzThreedimensionalVortexDynamics1988a}, vortex lines can be described as space curves $\s(\xi,t)$ of infinitesimal thickness, with a single quantum of circulation $\kappa=h/m_4=9.97\times10^{-8}\text{m}^2/\text{s}$, where $h$ is Planck's constant, $m_4=6.65\times10^{-27}\text{kg}$ is the mass of one helium atom, $\xi$ is the natural parameterisation, arclength, and $t$ is time.
-These conditions are a good approximation, since the vortex core radius of superfluid \textsuperscript{4}He($a_0=10^{-10}\text{m}$) is much smaller than any of the length scale of interest in turbulent flows.
+These conditions are a good approximation, since the vortex core radius of superfluid \textsuperscript{4}He($a_0=10^{-10}\text{m}$) is much smaller than any of the length scales of interest in turbulent flows.
 The equation of motion is
@@
 \begin{equation}
-	\mathbf{f}_{ns} = -D\s'\times\left[\s'\times(\dot{\s}-\v_n)\right]-\rho_n\kappa\s'\times(\v_n-\dot{\s}), 
+	\mathbf{f}_{ns} = -\mathcal{D}\s'\times\left[\s'\times(\dot{\s}-\v_n)\right]-\rho_n\kappa\s'\times(\v_n-\dot{\s}), 
+	\label{eq:mutual-friction}
 \end{equation}
-where $D$ is a coefficient dependent on the vortex Reynolds number and intrinsic properties of the normal fluid.
+where $\mathcal{D}$ is a coefficient dependent on the vortex Reynolds number and intrinsic properties of the normal fluid.
+The regularisation of the mutual fricition force onto the normal fluid grid is physically motivated by the strongly localised injection of vorticity during the momentum exchange of point-like particles and viscous flow in classical fluid dynamics \cite{gualtieri2015exact,gualtieri2017turbulence}.
+In short, the localised vorticity induced by the relative motion between the vortex lines and the normal fluid is diffused to discretisation of the grid spacing $\Delta x$ in a time interval $\epsilon_R$.
+In this way, the delta-forced fricition as defined in Eq.~\ref{eq:mutual-friction} is regularised by a Gaussian function, the fundamental solution of the diffusion equation.
+Further details of the method for classical fluids are contained in \cite{gualtieri2015exact,gualtieri2017turbulence} and for FOUCAULT in \cite{galantucciNewSelfconsistentApproach2020b}.
+
+In this Letter, we report all results using dimensionless units, where the characteristic length scale is $\tilde{\lambda} = D/D_0$, where $D^3=(1\times10^{-3}\mathrm{m})^3$ is the dimensional cube size, $D_0^3=(2\pi)^3$ is the non-dimensional cubic computational domain.
+The time scale is given by $\tilde{\tau}=\tilde{\lambda}^2\nu_n^0\nu_n$, where the non-dimensional viscosity $\nu_n^0$ resolves the small scales of the normal fluid.
+In these simulations, these quanties are $\tilde{\lambda}=1.59\times10^{-4}$m, $\nu_n^0=0.32$ and $\tilde{\tau}=0.366$s at $T=1.9K$ and $\tilde{\tau}=0.485$s at $T=2.1K$.
+We consider an initial configuration of two pairs of orthongal vortices, initialised as shown in the schematic of Fig.~\ref{fig:schematic}.
 

### 2024-11-25 supp-mat/supp-mat.tex
Update Supp Materials
Finish supplementary materials

@@
 \affiliation{Istituto per le Applicazioni del Calcolo ``M. Picone" IAC CNR, Via dei Taurini 19, 00185 Roma, Italy}
+\affiliation{School of Mathematics, Statistics and Physics, Newcastle University, Newcastle upon Tyne, NE1 7RU, United Kingdom}
 
@@
 	\centering
-	\includegraphics[width=0.4\textwidth]{schematic.png}
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=0.8\textwidth]{schematic.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=0.9\textwidth]{schematic-2.png}
+	\end{subfigure}
 	\caption{Schematic diagram of the initial vortex configuration.}
@@
 We consider an initial configuration of two pairs of orthongal vortices, initialised as shown in the schematic of Fig.~\ref{fig:schematic}.
+The seperation between vortices in each pair $d$ is set to be $d_v=0.5$ in dimensionless units, and the shortest distance between pairs is $D_v=\sqrt{(\pi-d_v/2)^2+\pi^2}\approx 3.08$, so that $d_v\ll D_v$.
+The Lagrangian discretisation of vortex lines is $\Delta \xi = 0.025$ (a total of 1340 discretisation points across the 4 vortex lines), using a timestep of $\Delta t_{VF} = 5.56\times10^{-6}$.
+For the normal fluid, a total of $N=256^3$ mesh point were used, with a timestep of $\Delta t_{NS} = 45\Delta t_{VF}$.
 

### 2025-03-04 cover_letter_CFB.tex
Add files via upload
conclusions added

\documentclass[a4paper,10pt]{letter}
\usepackage[margin=1in]{geometry}
\usepackage{lipsum}
\usepackage{xcolor}
\def\red#1{\textcolor{black}{#1}}

\begin{document}

% Sender Information
\begin{flushright}
    \begin{tabular}{l}
        \textbf{Piotr Stasiak} \\
        School of Mathematics, Statistics and Physics\\
        Newcastle University \\
        Newcastle  upon Tyne \\
        p.stasiak@newcastle.ac.uk \\
        \today
    \end{tabular}
\end{flushright}

\vspace{1cm}

% Recipient Information
The Editors,\\
Physical Review Letters\\
APS\\

\vspace{1cm}

Dear Editor,

\vspace{0.5cm}

We are pleased to submit our manuscript entitled 
\textbf{``Inverse energy transfer in three-dimensional quantum vortex flows''}
 to be considerated for publication in \textit{Physical Review Letters}. 
Our paper shows numerical evidence of the impact of superfluid vortex motion 
on the embedding \red{thermal excitations - the so-called normal
fluid}. Namely, a topological change in the superfluid vortex configuration 
(a \red{vortex} reconnection) triggers
a flux of normal fluid energy towards \red{large-scale motions}. 
This is surprising, as in \red{ordinary} fluids vortex 
reconnections generate an energy transfer in the opposite direction of
k-space, towards small-scale motions.

We clearly identify the underlying physical mechanism for this inverse 
energy transfer: the Kelvin waves 
generated on the superfluid vortices by the reconnection force 
helically the normal fluid, producing a
chiral flow \red{of thermal excitations}.  
\red{This helical imbalance is similar to what happens in 
\red{ordinary}
turbulence if it is artificially decimated by the numerics (as
demonstrated in Phys. Rev. Lett.
{\bf 108}, 164202, 2012).}
The important element to emphasize is that 
in superfluid \red{helium} this imbalance occurs naturally in the physical
world.

We believe that our findings will be of interest to readers of 
\textit{Physical Review Letters}, as they contribute to 
\red{a deeper understanding of turbulence};
%the lively, trans-disciplinary discussion regarding similiarities and 
%differences between turbulent flows in classical and quantum fluids;
\red{they will also} stimulate investigations
on the role of helicity in quantum turbulence, an aspect until now 
overlooked in the low-temperature community.

Thank you for considering this manuscript; we look forward to your response.
\vspace{0.5cm}

On behalf of the authors,

\vspace{1cm}

\textbf{Piotr Stasiak}

\end{document}

### 2025-03-05 arxiv-submission.tex
Added arxiv submission tex file with supplementary materials

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.2 distribution.
%   Version 4.2a of REVTeX, December 2014
%
%   Copyright (c) 2014 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.2
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[%
 reprint,
% superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
 prl,
%pra,
% prb,
% rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-2}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{blindtext}
\usepackage{float}
\usepackage{caption}
\usepackage{cleveref}
\usepackage{subcaption}
\usepackage{xcolor}
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

%\usepackage[showframe,%Uncomment any one of the following lines to test 
%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
%%text={7in,10in},centering,
%%margin=1.5in,
%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
%%height=10in,a5paper,hmargin={3cm,0.8in},
%]{geometry}

\newcommand{\etal}{{\it et al.}~}
\newcommand{\bom}{\boldsymbol{\omega}}

% \newcommand{\sd}[3][\null]{\ensuremath{\dfrac{\d^{#1} #2}{\d #3^{#1}}}}%Standard derivative 
% \newcommand{\pd}[3][\null]{\ensuremath{\dfrac{\partial^{#1} #2}{\partial #3^{#1}}}}%Partial derivative
% \newcommand{\matd}[2][\null]{\ensuremath{\dfrac{\mathrm{D}^{#1} #2}{\mathrm{D} t^{#1}}}} %Material derivative

\def \s{\mathbf{s}}
\def \v{\mathbf{v}}
\def \x{\mathbf{x}}
\def \r{\mathbf{r}}
\def \k{\mathbf{k}}
\def \h{\mathbf{h}}

\def \cm{\mathrm{cm}}
\def \cms{\mathrm{cm/s}}
\def \sec{\mathrm{s}}
\def \K{\mathrm{K}}

\def\red#1{\textcolor{red}{#1}}
\def\blue#1{\textcolor{blue}{#1}}
\def\magenta#1{\textcolor{magenta}{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand*{\NOTE}[1]{\textbf{\color{red}[#1]}}
\newcommand*{\CHANGE}[1]{{\color{brown}#1}}
\newcommand*{\DEL}[1]{{\color{green}#1}}

\begin{document}

\preprint{APS/123-QED}

%\title{Inverse energy transfer in finite-temperature superfluid vortex reconnections}
\title{Inverse energy transfer in three-dimensional quantum vortex flows}

\author{P. Z. Stasiak}
\author{A. Baggaley}
\author{C.F. Barenghi}
\affiliation{School of Mathematics, Statistics and Physics, Newcastle University, Newcastle upon Tyne, NE1 7RU, United Kingdom}

\author{G. Krstulovic}
\affiliation{Universit\'e C\^ote d'Azur, Observatoire de la C\^ote d'Azur, CNRS,Laboratoire Lagrangre, Boulevard de l'Observatoire CS 34229 - F 06304 NICE Cedex 4, France}

\author{L. Galantucci}
\affiliation{Istituto per le Applicazioni del Calcolo ``M. Picone" IAC CNR, Via dei Taurini 19, 00185 Roma, Italy}

\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

\begin{abstract}
Vortex reconnections play a fundamental role in fluids.
% and they are typically considered as a mechanism to 
They increase the complexity of flow and develop small-scale motions.
In this work, we report that in superfluids, they can also excite large scales.
We numerically illustrate that during a superfluid vortex reconnection energy 
is injected 
into the thermal (normal) component of helium~II at small length scales, but is transferred nonlinearly  to larger length scales, increasing the integral length scale of the normal
fluid.  
We show that this inverse energy transfer is triggered by the helical imbalance generated 
%at reconnection 
in the normal fluid flow by
the mutual friction force coupling the superfluid vortices and the normal component. We finally discuss
%by decomposing the velocity and the mutual friction (which couples superfluid and normal fluid) into helical modes, showing 
%that the imbalance of homochiral modes results from the punctuated energy and helicity injection during the reconnection. Finally, we discuss 
the relevance of our findings to 
the problem of superfluid turbulence.
\end{abstract}

%\keywords{Suggested keywords}%Use showkeys class option if keyword
   %display desired
\maketitle

\begin{figure*}
	\centering
    \begin{subfigure}[b]{0.24\textwidth}
		\centering
		\includegraphics*[width=\textwidth]{snap-1.pdf}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\textwidth}
		\centering
		\includegraphics*[width=\textwidth]{snap-2.pdf}
	\end{subfigure}
    \begin{subfigure}[b]{0.24\textwidth}
		\centering
		\includegraphics*[width=\textwidth]{snap-3.pdf}
	\end{subfigure}
    \begin{subfigure}[b]{0.24\textwidth}
		\centering
		\includegraphics*[width=\textwidth]{snap-4.pdf}

	\end{subfigure} \hfill
    %
	\begin{subfigure}[b]{0.24\textwidth}
		\centering
		\includegraphics*[width=\textwidth]{snaps-hel-1.pdf}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\textwidth}
		\centering
		\includegraphics*[width=\textwidth]{snaps-hel-2.pdf}
	\end{subfigure}
    \begin{subfigure}[b]{0.24\textwidth}
		\centering
		\includegraphics*[width=\textwidth]{snaps-hel-3.pdf}
	\end{subfigure}
    \begin{subfigure}[b]{0.24\textwidth}
		\centering
		\includegraphics*[width=\textwidth]{snaps-hel-4.pdf}
	\end{subfigure} \hfill
	\caption{
Three-dimensional rendering of the time evolution of
an initially orthogonal vortex configuration 
undergoing a vortex reconnection at $T = 1.9$K at dimensionless
times (from left to right)
$(t-t_R)/\tau_R=-7.47\times10^{-2}$, $-3.09\times10^{-3}$, $8.79\times10^{-4}$ and $5.39\times10^{-3}$, where $\tau_R = E^{1/2}_R/ L_R$. The green
tubes represent the superfluid vortex lines (the tubes’ radii have been 
greatly exaggerated for visual purpose). In the top sequence,
the blue volume rendering represents the scaled normal fluid enstrophy 
$\bom^2/\bom^2_{max}$. Note the Kelvin wave on the superfluid
vortex at $(t-t_0)/\tau_R=8.79\times10^{-4}$ . In the bottom sequence, the red/blue volume
rendering at the same times represent scaled positive/negative normal fluid
helicity.	
%Three-dimensional rendering of an orthogonal vortex configuration 
%undergoing a vortex reconnection at $T=1.9K$. The red tubes represent
%the superfluid vortex
%lines (the tubes' radii have been greatly exaggerated for visual purposes), 
%and the blue volume rendering represents the scaled normal fluid enstrophy 
%$\bom^2/\bom^2_{max}$. In the third panel, note the Kelvin waves on the superfluid vortices.
}
    \label{fig:visualisation}
\end{figure*}

%\paragraph*{Introduction.---} 
Turbulence is ubiquitous in the universe.  It occurs in systems
as large as nebulae of interstellar gas, and as small as clouds of
few thousands atoms confined by lasers in the laboratory.
Turbulence shapes patterns and properties of fluids of all
kinds, from ordinary
 viscous fluids (Navier-Stokes turbulence\cite{frisch1995}) 
to electrically conducting fluids (magneto-hydrodynamics turbulence
\cite{canuto-dalsgaard-1998}) to quantum fluid
(quantum turbulence \cite{barenghi-etal-2023,
Barenghi_Skrbek_Sreenivasan_2023}).
All turbulent systems are characterised by 
the existence of a wide range 
of length scales across which inviscid conserved quantities 
are transferred without loss in the spirit of the cascade 
depicted by Richardson \cite{richardson1922weather}.

In three-dimensional (3D) classical fluids, turbulence 
is characterised by a direct cascade: the
non-linear dissipationless transfer of kinetic energy from the scale of
the large eddies (at which energy is injected) to the smallest length scales
at which energy is dissipated into heat
\cite{richardson1922weather,kolmogorov-1941}. 
The resulting distribution of energy across length scales is
the celebrated Kolmogorov energy spectrum 
\cite{kolmogorov-1941,frisch1995}.

Confining Navier-Stokes turbulence to two-dimensions (2D) entails 
fundamentally distinct physics: a dual cascade emerges of energy and enstrophy 
(mean squared vorticity) \cite{kraichnan-1967,boffetta-ecke-2012}, 
the two conserved quantities in ideal two-dimensional flows.
% \magenta{(in
%three dimensions the conserved quantities are energy and helicity)}. 
%In particular, while 
While the enstrophy cascade is direct (from large to small
scales), the energy cascade is inverse (from small to large scales)
\cite{boffetta-musacchio-2010}. This inverse cascade 
may favour the generation and persistence of large coherent 
structures \cite{laurie-etal-2014}.

Remarkably, the same cascade phenomenology is observed in turbulent flows 
of quantum fluids, {\textit{i.e.} fluids at very low temperatures whose physics is
dominated by quantum effects.
Examples of such fluids are superfluid helium 
and atomic Bose-Einstein Condensates (BECs). 
The dynamics of these systems can be successfully depicted in terms of 
a two-fluid model \cite{tisza-1938,landau-1949,skrbek-sreenivasan-2012} 
describing the quantum fluid as the mixture of two components, 
the superfluid component and the thermal (or normal) component, which 
interact by means of a mutual friction force 
\cite{jackson-etal-2009,hall-vinen-1956a,hall-vinen-1956b}. 
The superfluid component flows without viscosity and
vanishing entropy; its vorticity is
confined to effectively one-dimensional vortex filaments
of atomic core thickness (called quantum vortices or vortex lines), 
around which the circulation of the velocity is quantised.
In BECs the thermal component forms a ballistic gas,
whereas in superfluid $^4$He it can be described as
a classical viscous fluid.
Despite these significant differences with respect to ordinary fluids, 
the direct
%forward 
kinetic energy cascade has
indeed been observed in three-dimensional superfluid
turbulence 
\cite{maurer1998,salort2010turbulent,baggaley2012,sherwin-robson2015,Muller_KolmogorovKelvinWave_2020,Muller_IntermittencyVelocityCirculation_2021}.
Evidence of this 
%forward 
direct
cascade has been found also in
three-dimensional turbulent BECs \cite{middleton-spencer2022}. Similarly to 2D classical turbulence, 
an inverse energy cascade characterises turbulence in two-dimensional BECs, 
as shown in theoretical \cite{bradley2012energy,reeves2013,simula2014emergence,Muller_ExploringEquivalenceTwoDimensional_2024} and experimental \cite{johnstone2019evolution,gauthier2019giant} studies.

In turbulent systems, the type and the number of sign-defined ideal invariants determine the direction of cascades. Indeed, the famous 
%and simple 
Fjørtoft argument \cite{fjortoft1953changes} predicts 
the existence of an inverse energy cascade
in 2D classical turbulence. 
%Similarly, for 3D wave-turbulent 3D BECs, the Fjørtoft argument predicts 
It also predicts an inverse particle and a direct energy cascade 
for 3D wave turbulent BECs, as recently addressed theoretically \cite{Zhu_DirectInverseCascades_2023}. In 3D classical fluids, helicity, which is also an inviscid invariant, is not sign-defined and thus only a direct energy cascade is possible. However, recent studies have demonstrated that the direction of the energy 
cascade may be inverted by artificially controlling the chirality of the 
flow, \textit{i.e.} the balance between positive and negative helical 
modes \cite{moffatt1969}.
%, eventually making helicity almost a sign defined quantity. 
Indeed, by restricting the non-linear energy transfer to homochiral 
interactions via a suitable decimation of the Navier-Stokes equation 
\cite{biferaleInverseEnergyCascade2012a,biferale-etal-2013}, by
controlling the weight of homochiral interactions \cite{sahoo-etal-2017},
or by the external injection 
of positive helical modes at all length scales 
\cite{plunianInverseCascadeEnergy2020a}, inverse energy cascades 
have been observed in three-dimensional turbulence of classical fluids. 
In brief, when the flow is synthetically designed to have an 
enhanced chirality, an inverse energy cascade can observed.

In this work, we unveil a similar dynamics occurring in superfluid helium
($^4$He) as a result of vortex reconnections.  
Reconnections occur continuously in turbulence: they take place when
two vortex lines collide and recombine, exchanging heads and tails, 
altering the overall topology of the flow
\cite{koplik-levine-1993,bewley-etal-2008,rorai-etal-2016,serafini-etal-2017,galantucci-baggaley-parker-barenghi-2019,villoisUniversalNonuniversalAspects2017,villois2020irreversible}. 
We show that the mutual friction force arising from the  
vortex reconnection is chiral, injecting in the normal fluid prevalently 
helicity of a given sign. Thus, as a consequence of vortex reconnections,
we observe an increase of the chiral imbalance of the quantum fluid, producing a transfer of kinetic energy from small to large scales, similarly to the phenomenology observed in 3D helical-decimated classical flows. 
 Unlike classical fluids, such a chiral imbalance arises naturally as physical process in the normal fluid.% because of vortex reconnections. 
%This is contrast to classical fluid dynamics,  where the helical characteristics of the flows producing 
% an inverse energy transfer require a careful synthetic construction 
% \cite{biferaleInverseEnergyCascade2012a,biferale-etal-2013,sahoo-etal-2017,plunianInverseCascadeEnergy2020a}.

% WE ADD REFERENCE TO OUR FIRST PAPER LATER IN THE TEXT
%Punctuated energy injection resulting from the violent nature of vortex reconnections \cite{stasiak2024quantum} pave the way for an imbalance of chirality by multi-scale energy injection.
%

%% THIS PART IS TOO DETAILED OF WHAT WE WILL DO AT THIS STAGE, ALTHOUGH PART OF IT MIGHT BE USED IN THE ABSTRACT
%We will show that energy is injected at the small length scales immediately in the post reconnection regimes and moves towards larger length scales, increasing the integral length scale $\mathcal{L}_E$ of the normal fluid component. We provide an explanation of the inverse energy transfer by decomposing the velocity and mutual friction fields (the governing interaction force between the two-fluid components) into helical modes, showing that the imbalance of homochiral modes resulting from the punctuated energy and helicity injection during the reconnection process. Finally, we discuss the relevance of our findings to the broader field of transitions to superfluid turbulence.

%\paragraph*{Main results.---}

To model superfluid helium dynamics, we employ the recently developed FOUCAULT model
\cite{galantucciNewSelfconsistentApproach2020b}.  In this approach, superfluid vortex lines are
parametrized as one-dimensional space curves  $\s(\xi,t)$, $\xi$ and $t$ being arclength and time respectively, exploiting the large separation of length scales between the vortex core radius, the Lagrangian discretisation along the vortex lines $\Delta\xi$, and the average radius of curvature $R_c$ of the vortex lines. The vortex lines evolve according to the following equation of motion:
\begin{equation}
    \dot{\s}(\xi,t) = \v_s + \frac{\beta}{1+\beta}\left[\v_{ns}\cdot\s'\right]\s' + \beta\s'\times\v_{ns} + \beta'\s'\times\left[\s'\times\v_{ns}\right],
\end{equation}
where $\dot{\s} = \partial\s/\partial t$, $\s' = \partial\s/\partial\xi$ is the unit tangent vector, $\v_n$ and $\v_s$ are the normal fluid and superfluid velocities at $\s$, $\v_{ns} = \v_n-\v_s$, and $\beta,\, \beta'$ are temperature and Reynolds number dependent mutual friction coefficients \cite{galantucciNewSelfconsistentApproach2020b}. The calculation of the superfluid velocity $\v_s$ is performed via the computation of the Biot-Savart integral de-singularised with standard techniques (see Supplementary Material \cite{suppMat}). The normal fluid is described classically using the incompressible ($\nabla\cdot\v_n=0$) 
Navier-Stokes equation
\begin{equation}
    \frac{\partial\v_n}{\partial t} + (\v_n\cdot\nabla)\v_n = -\frac{1}{\rho}\nabla p  + \nu_n\nabla^2\v_n + \frac{\mathbf{F}_{ns}}{\rho_n} \; \; , 
\end{equation}
%
where $\rho_n$ and $\rho_s$ are the normal fluid and superfluid densities,
$\rho=\rho_n + \rho_s$,  $p$ is the pressure,  $\nu_n$ is the kinematic 
viscosity of the normal fluid, and the mutual friction force per unit
volume, $\mathbf{F}_{ns}$, is the line integral of the mutual friction 
force per unit length, $\mathbf{f}_{ns}$ \cite{suppMat}:
%
\begin{equation}
\mathbf{F}_{ns}(\x) = 
\oint_{\mathcal{C}}\delta(\x-\s)\mathbf{f}_{ns}(\s)d\xi,     
\end{equation}
$\mathcal{C}$ representing the entire vortex configuration. 
The regularisation of mutual friction is performed using a physically self-consistent scheme \cite{galantucciNewSelfconsistentApproach2020b}. %, gualtieri2015exact, gualtieri2017turbulence}. 
We consider a periodical box of size $2\pi$ (so that  wavevectors are integers).

To study the reconnection dynamics, we consider two pairs of initially orthogonal vortices (where the corresponding vortices of each pair have opposite circulation in order to preserve periodicity along the boundaries)
at two distinct temperatures, $T=1.9K$ and $T=2.1K$. The vortex pairs are separated by the distance $D_{\ell}$; each vortex within each pair is initially at distance $d_{\ell}$ to the other vortex, such that $d_{\ell}\ll D_{\ell}$ to ensures that the dynamics in the vicinity of the reconnection is dominated by local interactions, and that the far-field contribution from the other vortex pair is negligible.

The evolution of the vortex reconnection of a single pair is reported in Fig.~\ref{fig:visualisation}. 
The first row shows the reconnecting superfluid vortices (in green) accompanied by normal fluid structures generated by mutual friction, here displayed as enstrophy rendering $\bom(\x)^2=|\nabla\times \v_n|^2$. Such structures are the signature of the violent irreversible energy transfers in vortex reconnections 
\cite{stasiak2024quantum}. The second row shows the rendering of the local helicity $H(\x)=\v_n\cdot\bom$, where we observe a clear local helicity production, with an abrupt change of sign due to the rearrangement of the vortex topology. Remarkably, during reconnection there is a net 
sudden normal fluid helicity production, as shown in Fig.~\ref{fig:total-helicity}. We will come back to this finding later.
\begin{figure}[t]
    \centering
    \includegraphics*[width=0.48\textwidth]{helicity_total}
\caption{Temporal evolution of the normal fluid helicity $\mathcal{H} = \int_{\mathcal{V}}H(\x)dV$ computed over the entire volume $\mathcal{V}$. For superfluid helium, it is proper to make the helicity dimensionless in terms of $\kappa^2$. The quantities $E_R$ and $L_R$ are the energy $E$ and integral length scales $L_0$ of the normal fluid at reconnection time $t_R$.}
\label{fig:total-helicity}
\end{figure}

We now focus on the time evolution of the normal fluid energy spectrum $E(k)$, defined by 
\begin{equation}
    E = \frac{1}{(2\pi)^3}\int_{\mathcal{V}}\frac{1}{2}|\v_n|^2 dV = \int_0^{\infty}E(k)dk
\end{equation}
where $E$ is the total normal fluid energy and $k$ is the magnitude of the three-dimensional wavenumber. The energy at reconnection $E_R$ is given by $E(t_R)$, where $t_R$ is the time at reconnection. The energy spectrum $E(k)$ is displayed in Fig.~\ref{fig:kinetic-energy}.
\begin{figure}[h!]
    \centering
    \begin{subfigure}{0.49\textwidth}
        \centering
        \includegraphics*[width=\textwidth]{energy-spec.pdf}
        \caption{}\label{fig:kinetic-energy}
    \end{subfigure}
    \begin{subfigure}{0.49\textwidth}
        \centering
        \includegraphics*[width=\textwidth]{flux-spec.pdf}
        \caption{}\label{fig:energy-flux}
    \end{subfigure}
    \caption{\emph{(a):} Normal fluid kinetic energy spectrum $E(k)$ before 
reconnection (dashed lines), at reconnection (solid lines) 
and after reconnection (dotted lines) for $T=1.9K$ (red)
and $T=2.1K$ (blue).\emph{(b):} Spectral normal fluid kinetic energy flux, $\Pi (k)$. It is normalised using the integral scale and the normal fluid energy at reconnection.
\emph{Inset:} Post reconnection evolution of the integral length scale, $L_0$.
Times and temperatures are labelled as in Fig.~\ref{fig:kinetic-energy}.}
\end{figure}
%

It clearly emerges that, during the reconnection, energy is predominantly injected into the normal fluid at intermediate and small length scales. 
For $k>5$ in correspondence of the reconnection time $t_R$,
we observe a significant increase of the normal fluid energy spectral density:
$E(k,\, t\approx t_R)/E(k,\, t\ll t_R) \approx 10^2$. 
%
In the post-reconnection regime, we simultaneously observe a small 
decrease of the spectrum at intermediate 
and small scales ($k > 5$) and an increase at large scales, 
suggesting the existence of a mechanism by 
which energy generated at small length scales is transferred to larger scales. 
To shed light on this mechanism, as customary for turbulent flows, we analyse the spectral energy flux 
\begin{equation}
    \Pi(k)=\int_{|{\bf p}|<k}  \hat{\mathbf{v}}_n^*\cdot \left [\widehat{(\v_n\cdot\nabla)\v_n} \right ]d {\bf p} +c.c. \;\; ,
\end{equation}
where $\widehat{\cdot}$ indicates the Fourier transform.

% the dynamics of the normal fluid flow using the 
% spectral energy budget equation: 
% %
% \begin{equation}
%     \frac{\partial E(k)}{\partial t} = T(k) - D(k) + I(k)
% \end{equation}
% where $T(k)$ is the spectral kinetic energy transfer function,
% %(\textit{i.e.} $T(k)dk$ is the energy transfered per unit time by modes with $k < |\mathbf{k}| < k +dk$, determined by non-linear effects), 
% $D(k)=2\nu_n k^2 E_k$ is the dissipation spectrum and
% %=\mathrm{Re}(\hat{\mathbf{F}}_{ns}(\k)\cdot\hat{\v}^*(\k))$ 
% $I(k)$ is the injection spectrum arising from the mutual friction 
% force $\mathbf{F}_{ns}$.  
We observe that $\Pi(k) < 0$ for all $k$ during and after reconnection;
we also observe that, near the time of reconnection,
the peak value of $|\Pi(k)|$ is in the range $15 < k < 25$.
%
The negative sign of $\Pi(k)$ is evidence of a flux of kinetic  energy from small to large scales, exciting larger and larger scales. % In other words, at non-zero temperatures,
% vortex reconnections trigger an inverse transfer of energy, 
% which implies the creation of large scale structures, visible
% in Fig.~\ref{fig:visualisation}} \NOTE{GK: the figure shows small scale structures...}
This behaviour is quantified by the evolution of the integral length scale $L_0$, defined as
\begin{equation}
    L_0 = \frac{\pi}{2 E}\int_0^{\infty}\frac{E(k)}{k}dk, %\Big/ \int_0^{\infty}\!\!E(k)dk.
\end{equation}
The inset of Fig.~\ref{fig:energy-flux} shows that
$L_0$ indeed  increases steadily in the post-reconnection regime. Note that times have been normalised by the largest eddy-turnover-time at the reconnection event, evidencing  it fast evolution.

To explain the inverse energy transfer shown in Fig.~\ref{fig:kinetic-energy},
we look whether the reconnection triggers a chirality imbalance. 
We decompose the incompressible Fourier modes of the normal fluid velocity 
into helical modes \cite{waleffe-1992}:
\begin{equation}
\hat{\mathbf{v}}_n (\k) = \hat{\mathbf{v}}_n^+(\k) +\hat{\mathbf{v}}_n^-(\k)=
 v_n^+(\mathbf{k}) \mathbf{h}^+(\mathbf{k})+v_n^-(\mathbf{k}) \mathbf{h}^-(\mathbf{k}),
\end{equation}
%
where $\mathbf{h}^\pm (\mathbf{k})$ are the two eigenvectors of the curl 
operator, \textit{i.e.} $i\k~\times~\h^{\pm}(\k)~=~\pm k \h^{\pm}(\k)$. 
Similarly, we decompose the transverse modes of the mutual friction force:
$\hat{\mathbf{F}}_{ns}^{\perp}(\k) = f^+(\k) \mathbf{h}^+ + f^-(\k) \mathbf{h}^-$
(the  Fourier modes of $\mathbf{F}_{ns}$ parallel to the wavemumber 
$\k$ do not play any role in the time evolution of $\mathbf{v}_n$ 
due to the incompressible constraint). Finally, the helical decomposition naturally allow us decompose the total helicity as $\mathcal{H}=\mathcal{H}^+-\mathcal{H}^-$ \cite{plunianInverseCascadeEnergy2020a}.
% %
% The spectral energy densities corresponding to the helical modes are
% $E^{\pm}(\k) = (1/2) |v_n^\pm(\k)|^2$, the total spectral density 
% being $E(\k) = E^{+}(\k) + E^{-}(\k)$. Similarly the spectral helicity 
% density is 
% \begin{equation}
% \begin{split}
% H(\k) & = (1/2) \hat{\mathbf{v}}_n (\k)\!\!\! ~\cdot~\!\!\! \hat{\bm{\omega}}_n^* (\k) = \\
% & = k E^+(\k) - k E^-(\k)  = H^+(\k) - H^-(\k),
% \end{split}
% \end{equation}
% where $\bm{\omega}_n$ is the normal fluid vorticity, the star indicates 
% complex conjugate and $H^\pm$ is the helicity contribution of each 
% separate helical mode. \NOTE{GK: the standard definition of the energy and helicity spectra contains the sum over the angles, so the previous definition are wrong (except if you redifined them for some reason).}
%The rate of change $I^\pm(\k)$ of the energies $E^{\pm}(\k)$ arising from the mutual friction is proportional to the corresponding helical coefficients $f^\pm$, \textit{i.e.} $I^\pm(\k) = \mathrm{Re} [f^\pm (v_n^\pm)^*] /\rho_n$, and the related signed helicity injection is $I_H^\pm(\k) = k \mathrm{Re} [f^\pm (v_n^\pm)^*] /\rho_n$.

A chiral imbalance occurs if the mutual friction force is helical, 
\textit{i.e.} if the ratio $|f^+|^2/|f^-|^2 \neq 1$, with $|f^\pm|^2$ the total squared norm of the mutual friction components. 
In Fig.~\ref{fig:mutual-friction-decomp}, we show the temporal evolution of $|f^+|^2/|f^-|^2$, for both temperatures. 
%
\begin{figure}[h!]
    \centering
    \includegraphics*[width=0.48\textwidth]{fmfDecompFig.pdf}
    \caption{Temporal evolution of projected mutual friction force components $f^\pm$/ Inset: temporal evolution of total helical components.}.
    \label{fig:mutual-friction-decomp}
\end{figure}
%
It is apparent
that during and after the reconnection, the mutual friction force is strongly chiral,
injecting more negative helicity than positive helicity. 
As a result, the ratio $\mathcal{H}^+/\mathcal{H}^-$ 
(reported in the inset of Fig.~\ref{fig:mutual-friction-decomp}) 
decreases significantly at reconnection and remains smaller than unity even at later times, 
indicating that the flow is persistently chiral. We conclude that the reconnection triggers indeed a chiral imbalance.
From Fig.~\ref{fig:mutual-friction-decomp} we determine the non-dimensional timescale $\tau = (t^*-t_R)E_R^{1/2}/L_R$
during which the mutual friction force is chiral as a result of reconnections: $\tau \approx 0.01$ and $\tau \approx 0.005$
for $T=1.9$K and $T=2.1$K, respectively, corresponding dimensionally to $\tau \approx 0.1$s for both temperatures. 
In superfluid turbulence, the timescale between two consecutive reconnections can be smaller than $\tau$ provided that the
vortex line density $\mathcal{L}$ (length of vortices per unit volume) is larger than $10^8 \text{m}^{-2}$ \cite{stasiak2024quantum,barenghi2004},
a condition which is easily met in superfluid helium experiments \cite{roche2007,Babuin2014}.

%Furthermore, as observed in
%Ref.~\cite{plunianInverseCascadeEnergy2020a}, to observe a negative energy flux the forcing needs to cover the entire spectrum of $k$, which  from the inset of Fig.~\ref{fig:kinetic-energy}, it is evident that this indeed the case.

%we follow recent work in classical fluids outlined in Refs.~\cite{biferaleInverseEnergyCascade2012a,plunianInverseCascadeEnergy2020a}, where it is even possible to sustain an inverse energy cascade under a helical forcing applied at all length scales. Typically, velocity coefficients $\hat{\v}(\k)$ can be decomposed into their helical modes, where $\hat{\v}(\k)=v^+(\k)\h^+(\k) + v^-(\k)\h^-(\k)$ and satisfies $\k\cdot\hat{\v}(\k)=0$, where $\v^{\pm}$ are complex scalars and $\h^{\pm}(\k)$ are the two eigenvectors of the curl operator, such that $i\k\times\h^{\pm}(\k)=\pm k \h^{\pm}(\k)$. To explain the inverse energy transfer in terms of helical modes, we show that in fact the driving force, which in our case is a punctuated burst due to superfluid vortex reconnections, is of a helical nature. The mutual friction modes $\hat{\mathbf{F}}_{ns}(\k)$ are not incompressible, and so we take the projection of the modes orthogonal to the wavenumber $\k$. The projected modes $\hat{\mathbf{f}}(\k)$ are then decomposed into helical modes $\hat{\mathbf{f}}(\k)=f^+\h^{+}(\k) + f^-\h^{-}(\k)$. The ratio of the two helical modes $|f^+|^2/|f^-|^2$ are shown in Fig.~\ref{fig:mutual-friction-decomp}. At reconnection time $t_0$, the ratio is much larger, indicating that indeed this force is chiral and that a clear inbalance that favours the injection of positive helical modes, changing the chirality of the flow (as seen in Fig.~\ref{fig:mutual-friction-decomp}). In the same way, helicity modes $\hat{\mathcal{H}}(\k)$ can be decomposed,
%\begin{equation}
%    \hat{\mathcal{H}}(\k) = k(E^+(\k) - E^-(\k)) = \mathcal{H}^+ + \mathcal{H}^-
%\end{equation}
%where $E^{\pm}=\frac{1}{2}|\v^{\pm}(\k)|^2$ are the helical energy modes. The evolution of the ratio $\mathcal{H}^+/\mathcal{H}^-$ is shown in the inset of Fig.~\ref{fig:mutual-friction-decomp}. The sharp increase at reconnection time $t_0$ is evidence of a large influx of positive helical modes as a result of the vortex reconnection, which is in agreement with the conditions to facilitate an inverse energy transfer by a helical injection. Finally, as observed in Ref.~\cite{plunianInverseCascadeEnergy2020a}, it is necessary for the forcing to cover the entire spectrum of $k$, which from the inset of Fig.~\ref{fig:kinetic-energy}, it is evident that this indeed the case.

%\paragraph*{Closing remarks.---}
In conclusion, the reconnection of quantum vortices in the two-fluid regime
($T\gtrsim 1.5$K) not only injects punctuated
energy in the normal fluid \cite{stasiak2024quantum}, but also triggers in the normal fluid
a transfer of kinetic energy towards the large scales. 
%This inverse 
%energy transfer arises from the fact that the mutual friction force (injecting energy and 
%helicity in the normal fluid) is helical, as Kelvin waves develop on the vortices as a result of the reconnection itself.
%The helical character of the mutual friction produces a chiral imbalance in the normal fluid, driving this inverse transfer, as previously observed in turbulent Navier-Stokes flows
This inverse energy transfer arises from the helical character of the
friction generated by the Kelvin waves released by the reconnecting
cusp, which produces a chiral imbalance in the normal fluid, as 
previously observed in turbulent Navier-Stokes flows
\cite{biferaleInverseEnergyCascade2012a,plunianInverseCascadeEnergy2020a}.

Our findings have profound implications for the nature of turbulence in 
finite temperature superfluids. In circumstances where the vortex density 
$\mathcal{L}$ is large and where the isotropy of the vortex tangle 
is broken by external forcing, the chirality of the flow generated by the 
frequent reconnections may be strong enough to induce an inverse energy 
cascade \cite{notes_recon}.
%The asymmetry of the reconnecting vortex configurations is a key element; 
%when perfectly symmetrical vortex configurations (with corresponding 
%opposite vortex line orientations) reconnect, the injected helicity 
%globally cancels out, as verified in our study if we take also into 
%account the reconnection.
The microscopic mechanism that we have described is probably what
triggers the inverse energy cascade which is observed numerically in  
large-scale simulations of counterflow turbulence at large heat fluxes \cite{polanco2020}, which
indeed inherently not isotropic.
%, hence triggering non-fully reconnections. 
Our work hence motivates further detailed studies of
the role played by helicity in superfluid dynamics 
\cite{dileoni2016,galantucci2021},
moving the emphasis from few vortex systems \cite{scheeler2014} 
to fully coupled superfluid turbulence.

\begin{acknowledgments}
    G.K. was supported by the Agence Nationale de la Recherche through the project the project QuantumVIW ANR-23-CE30-0024-02.
    This work has been also supported by the French government, through the UCAJEDI Investments in the Future project managed by the National Research Agency (ANR) with the reference number ANR-15-IDEX-01. P.Z.S. acknowledges the financial support of the UniCA ``visiting doctoral student program'' on complex systems. Computations were carried out at the Mésocentre SIGAMM hosted at the Observatoire de la Côte d’Azur.

  \end{acknowledgments}

\bibliography{references}% Produces the bibliography via BibTeX

\appendix
\section*{Supplementary Materials}

Using Schwarz mesoscopic model \cite{schwarz1988}, vortex lines can be described as space curves $\s(\xi,t)$ of infinitesimal thickness, with a single quantum of circulation $\kappa=h/m_4=9.97\times10^{-8}\text{m}^2/\text{s}$, where $h$ is Planck's constant, $m_4=6.65\times10^{-27}\text{kg}$ is the mass of one helium atom, $\xi$ is the natural parameterisation, arclength, and $t$ is time. These conditions are a good approximation, since the vortex core radius of superfluid \textsuperscript{4}He($a_0=10^{-10}\text{m}$) is much smaller than any of the length scales of interest in turbulent flows. The equation of motion is
\begin{equation}
	\dot{\s}(\xi,t) = \v_s + \frac{\beta}{1+\beta}\left[\v_{ns}\cdot \s'\right]\s' + \beta\s'\times\v_{ns}+\beta'\s'\times\left[\s'\times \v_{ns}\right],
\end{equation}
where $\dot{\s}=\partial\s/\partial t$, $\s'=\partial\s/\partial \xi$ is the unit tangent vector, $\v_{ns}=\v_n - \v_s$, $\v_n$ and $\v_s$ are the normal fluid and superfluid velocities at $\s$ and $\beta$,$\beta'$ are temperature and Reynolds number dependent mutual fricition coefficients \cite{galantucciNewSelfconsistentApproach2020b}. The superfluid velocity $\v_s$ at a point $\x$ is determined by the Biot-Savart law
\begin{equation}
	\v_s(\x,t) = \frac{\kappa}{4\pi}\oint_{\mathcal{T}}\frac{\s'(\xi,t)\times\left[\x-\s(\xi,t)\right]}{|\x-\s(\xi,t)|}d\xi,
\end{equation}
where $\mathcal{T}$ represents the entire vortex configuration.
There is currently a lack of a well-defined theory of vortex reconnections in superfluid helium, like for the Gross-Pitaevskii equation \cite{villois2020irreversible,villoisUniversalNonuniversalAspects2017,promentMatchingTheoryCharacterize2020a}. An \emph{ad hoc} vortex reconnection algorithm is employed to resolve the collisions of vortex lines \cite{baggaleySensitivityVortexFilament2012a}.

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=0.8\textwidth]{schematic.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=0.9\textwidth]{schematic-2.png}
	\end{subfigure}
	\caption{Schematic diagram of the initial vortex configuration.}
	\label{fig:schematic}
\end{figure}

A \emph{two-way model} is crucial to understand the accurately interept the back-reaction effect of the normal fluid on the vortex line and vice-versa \cite{stasiak2024quantum}. We self-consistently evolve the normal fluid $\v_n$ with a modified Navier-Stokes equation
\begin{equation}
	\frac{\partial \v_n}{\partial t} + (\v_n\cdot\nabla)\v_n = -\nabla\frac{p}{\rho} + \nu_n\nabla^2\v_n + \frac{\mathbf{F}_{ns}}{\rho_n},
\end{equation}
\begin{equation}
	\mathbf{F}_{ns} = \oint_{\mathcal{T}}\mathbf{f}_{ns}\delta(\x-\x)d\xi, \quad \nabla\cdot\v_n=0,
\end{equation}
where $\rho=\rho_n + \rho_s$ is the total density, $\rho_n$ and $\rho_s$ are the normal fluid and superfluid densities, $p$ is the pressure, $\nu_n$ is the kinematic viscosity of the normal fluid and $\mathbf{f}_{ns}$ is the local friction per unit length \cite{galantucciCoupledNormalFluid2015a}
\begin{equation}
	\mathbf{f}_{ns} = -\mathcal{D}\s'\times\left[\s'\times(\dot{\s}-\v_n)\right]-\rho_n\kappa\s'\times(\v_n-\dot{\s}), 
	\label{eq:mutual-friction}
\end{equation}
where $\mathcal{D}$ is a coefficient dependent on the vortex Reynolds number and intrinsic properties of the normal fluid. The regularisation of the mutual fricition force onto the normal fluid grid is physically motivated by the strongly localised injection of vorticity during the momentum exchange of point-like particles and viscous flow in classical fluid dynamics \cite{gualtieri2015exact,gualtieri2017turbulence}. In short, the localised vorticity induced by the relative motion between the vortex lines and the normal fluid is diffused to discretisation of the grid spacing $\Delta x$ in a time interval $\epsilon_R$. In this way, the delta-forced fricition as defined in Eq.~\ref{eq:mutual-friction} is regularised by a Gaussian function, the fundamental solution of the diffusion equation. Further details of the method for classical fluids are contained in \cite{gualtieri2015exact,gualtieri2017turbulence} and for FOUCAULT in \cite{galantucciNewSelfconsistentApproach2020b}.

In this Letter, we report all results using dimensionless units, where the characteristic length scale is $\tilde{\lambda} = D/D_0$, where $D^3=(1\times10^{-3}\mathrm{m})^3$ is the dimensional cube size, $D_0^3=(2\pi)^3$ is the non-dimensional cubic computational domain. The time scale is given by $\tilde{\tau}=\tilde{\lambda}^2\nu_n^0\nu_n$, where the non-dimensional viscosity $\nu_n^0$ resolves the small scales of the normal fluid. In these simulations, these quanties are $\tilde{\lambda}=1.59\times10^{-4}$m, $\nu_n^0=0.32$ and $\tilde{\tau}=0.366$s at $T=1.9K$ and $\tilde{\tau}=0.485$s at $T=2.1K$. We consider an initial configuration of two pairs of orthongal vortices, initialised as shown in the schematic of Fig.~\ref{fig:schematic}. The seperation between vortices in each pair $d$ is set to be $d_v=0.5$ in dimensionless units, and the shortest distance between pairs is $D_v=\sqrt{(\pi-d_v/2)^2+\pi^2}\approx 3.08$, so that $d_v\ll D_v$. The Lagrangian discretisation of vortex lines is $\Delta \xi = 0.025$ (a total of 1340 discretisation points across the 4 vortex lines), using a timestep of $\Delta t_{VF} = 5.56\times10^{-6}$. For the normal fluid, a total of $N=256^3$ mesh point were used, with a timestep of $\Delta t_{NS} = 45\Delta t_{VF}$.

\end{document}
%
% ****** End of file apssamp.tex ******

### 2025-03-05 arxiv-submission.tex
Added .bbl file to tex for arxiv submission

@@
 
-\bibliography{references}% Produces the bibliography via BibTeX
+% \bibliography{references}% Produces the bibliography via BibTeX
+
+%apsrev4-2.bst 2019-01-14 (MD) hand-edited version of apsrev4-1.bst
+%Control: key (0)
+%Control: author (8) initials jnrlst
+%Control: editor formatted (1) identically to author
+%Control: production of article title (0) allowed
+%Control: page (0) single
+%Control: year (1) truncated
+%Control: production of eprint (0) enabled
+\begin{thebibliography}{61}%
+    \makeatletter
+    \providecommand \@ifxundefined [1]{%
+     \@ifx{#1\undefined}
+    }%
+    \providecommand \@ifnum [1]{%
+     \ifnum #1\expandafter \@firstoftwo
+     \else \expandafter \@secondoftwo
+     \fi
+    }%
+    \providecommand \@ifx [1]{%
+     \ifx #1\expandafter \@firstoftwo
+     \else \expandafter \@secondoftwo
+     \fi
+    }%
+    \providecommand \natexlab [1]{#1}%
+    \providecommand \enquote  [1]{``#1''}%
+    \providecommand \bibnamefont  [1]{#1}%
+    \providecommand \bibfnamefont [1]{#1}%
+    \providecommand \citenamefont [1]{#1}%
+    \providecommand \href@noop [0]{\@secondoftwo}%
+    \providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+    \providecommand \@href[1]{\@@startlink{#1}\@@href}%
+    \providecommand \@@href[1]{\endgroup#1\@@endlink}%
+    \providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+      `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+    \providecommand \@@startlink[1]{}%
+    \providecommand \@@endlink[0]{}%
+    \providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+    \providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+    \providecommand \urlprefix  [0]{URL }%
+    \providecommand \Eprint [0]{\href }%
+    \providecommand \doibase [0]{https://doi.org/}%
+    \providecommand \selectlanguage [0]{\@gobble}%
+    \providecommand \bibinfo  [0]{\@secondoftwo}%
+    \providecommand \bibfield  [0]{\@secondoftwo}%
+    \providecommand \translation [1]{[#1]}%
+    \providecommand \BibitemOpen [0]{}%
+    \providecommand \bibitemStop [0]{}%
+    \providecommand \bibitemNoStop [0]{.\EOS\space}%
+    \providecommand \EOS [0]{\spacefactor3000\relax}%
+    \providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+    \let\auto@bib@innerbib\@empty
+    %</preamble>
+    \bibitem [{\citenamefont {Frisch}(1995)}]{frisch1995}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {U.}~\bibnamefont
+      {Frisch}},\ }\href@noop {} {\bibinfo {title} {\emph{Turbulence: {{The
+      Legacy}} of {{A}}. {{N}}. {{Kolmogorov}}}}} (\bibinfo {year}
+      {1995})\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Canuto}\ and\ \citenamefont
+      {Christensen-Dalsgaard}(1998)}]{canuto-dalsgaard-1998}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.~M.}\ \bibnamefont
+      {Canuto}}\ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+      {Christensen-Dalsgaard}},\ }\bibfield  {title} {\bibinfo {title} {Turbulence
+      in astrophysics: stars},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+      {journal} {Ann. Rev. Fluid Mech.}\ }\textbf {\bibinfo {volume} {30}},\
+      \bibinfo {pages} {167} (\bibinfo {year} {1998})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Barenghi}\ \emph
+      {et~al.}(2023{\natexlab{a}})\citenamefont {Barenghi}, \citenamefont
+      {Middleton-Spencer}, \citenamefont {Galantucci},\ and\ \citenamefont
+      {Parker}}]{barenghi-etal-2023}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~F.}\ \bibnamefont
+      {Barenghi}}, \bibinfo {author} {\bibfnamefont {H.~A.~J.}\ \bibnamefont
+      {Middleton-Spencer}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+      {Galantucci}},\ and\ \bibinfo {author} {\bibfnamefont {N.~G.}\ \bibnamefont
+      {Parker}},\ }\bibfield  {title} {\bibinfo {title} {Types of quantum
+      turbulence},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {AVS
+      Quantum Sci.}\ }\textbf {\bibinfo {volume} {5}},\ \bibinfo {pages} {025601}
+      (\bibinfo {year} {2023}{\natexlab{a}})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Barenghi}\ \emph
+      {et~al.}(2023{\natexlab{b}})\citenamefont {Barenghi}, \citenamefont
+      {Skrbek},\ and\ \citenamefont
+      {Sreenivasan}}]{Barenghi_Skrbek_Sreenivasan_2023}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~F.}\ \bibnamefont
+      {Barenghi}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Skrbek}},\
+      and\ \bibinfo {author} {\bibfnamefont {K.~R.}\ \bibnamefont {Sreenivasan}},\
+      }\href@noop {} {\emph {\bibinfo {title} {Quantum Turbulence}}}\ (\bibinfo
+      {publisher} {Cambridge University Press},\ \bibinfo {year}
+      {2023})\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Richardson}(1922)}]{richardson1922weather}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~F.}\ \bibnamefont
+      {Richardson}},\ }\href@noop {} {\emph {\bibinfo {title} {{W}eather
+      {P}rediction by {N}umerical {P}rocess}}}\ (\bibinfo  {publisher} {University
+      Press},\ \bibinfo {year} {1922})\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Kolmogorov}(1941)}]{kolmogorov-1941}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+      {Kolmogorov}},\ }\bibfield  {title} {\bibinfo {title} {The local structure of
+      turbulence in an incompressible viscous fluid for very large {{R}}eynolds
+      numbers},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Dokl.
+      Akad. Nauk. SSSR}\ }\textbf {\bibinfo {volume} {30}},\ \bibinfo {pages} {301}
+      (\bibinfo {year} {1941})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Kraichnan}(1967)}]{kraichnan-1967}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+      {Kraichnan}},\ }\bibfield  {title} {\bibinfo {title} {Inertial ranges in
+      two‐dimensional turbulence},\ }\href@noop {} {\bibfield  {journal}
+      {\bibinfo  {journal} {Phys. Fluids}\ }\textbf {\bibinfo {volume} {10}},\
+      \bibinfo {pages} {1417} (\bibinfo {year} {1967})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Boffetta}\ and\ \citenamefont
+      {Ecke}(2012)}]{boffetta-ecke-2012}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+      {Boffetta}}\ and\ \bibinfo {author} {\bibfnamefont {R.~E.}\ \bibnamefont
+      {Ecke}},\ }\bibfield  {title} {\bibinfo {title} {Two-dimensional
+      turbulence},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Ann.
+      Rev. Fluid Mech.}\ }\textbf {\bibinfo {volume} {44}},\ \bibinfo {pages} {427}
+      (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Boffetta}\ and\ \citenamefont
+      {Musacchio}(2010)}]{boffetta-musacchio-2010}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+      {Boffetta}}\ and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+      {Musacchio}},\ }\bibfield  {title} {\bibinfo {title} {Evidence for the double
+      cascade scenario in two-dimensional turbulence},\ }\href
+      {https://doi.org/10.1103/PhysRevE.82.016307} {\bibfield  {journal} {\bibinfo
+      {journal} {Phys. Rev. E}\ }\textbf {\bibinfo {volume} {82}},\ \bibinfo
+      {pages} {016307} (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Laurie}\ \emph {et~al.}(2014)\citenamefont {Laurie},
+      \citenamefont {Boffetta}, \citenamefont {Falkovich}, \citenamefont
+      {Kolokolov},\ and\ \citenamefont {Lebedev}}]{laurie-etal-2014}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+      {Laurie}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Boffetta}},
+      \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Falkovich}}, \bibinfo
+      {author} {\bibfnamefont {I.}~\bibnamefont {Kolokolov}},\ and\ \bibinfo
+      {author} {\bibfnamefont {V.}~\bibnamefont {Lebedev}},\ }\bibfield  {title}
+      {\bibinfo {title} {Universal profile of the vortex condensate in
+      two-dimensional turbulence},\ }\href
+      {https://doi.org/10.1103/PhysRevLett.113.254503} {\bibfield  {journal}
+      {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {113}},\
+      \bibinfo {pages} {254503} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Tisza}(1938)}]{tisza-1938}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+      {Tisza}},\ }\bibfield  {title} {\bibinfo {title} {Transport phenomena in
+      helium {{II}}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+      {Nature}\ }\textbf {\bibinfo {volume} {141}},\ \bibinfo {pages} {913}
+      (\bibinfo {year} {1938})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Landau}(1949)}]{landau-1949}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+      {Landau}},\ }\bibfield  {title} {\bibinfo {title} {On the theory of
+      superfluidity},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+      {Phys. Rev.}\ }\textbf {\bibinfo {volume} {75}},\ \bibinfo {pages} {884}
+      (\bibinfo {year} {1949})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Skrbek}\ and\ \citenamefont
+      {Sreenivasan}(2012)}]{skrbek-sreenivasan-2012}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+      {Skrbek}}\ and\ \bibinfo {author} {\bibfnamefont {K.~R.}\ \bibnamefont
+      {Sreenivasan}},\ }\bibfield  {title} {\bibinfo {title} {Developed quantum
+      turbulence and its decay},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+      {journal} {Phys. Fluids}\ }\textbf {\bibinfo {volume} {24}},\ \bibinfo
+      {pages} {011301} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Jackson}\ \emph {et~al.}(2009)\citenamefont
+      {Jackson}, \citenamefont {Proukakis}, \citenamefont {Barenghi},\ and\
+      \citenamefont {Zaremba}}]{jackson-etal-2009}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+      {Jackson}}, \bibinfo {author} {\bibfnamefont {N.~P.}\ \bibnamefont
+      {Proukakis}}, \bibinfo {author} {\bibfnamefont {C.~F.}\ \bibnamefont
+      {Barenghi}},\ and\ \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+      {Zaremba}},\ }\bibfield  {title} {\bibinfo {title} {Finite-temperature vortex
+      dynamics in bose-einstein condensates},\ }\href@noop {} {\bibfield  {journal}
+      {\bibinfo  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume} {79}},\
+      \bibinfo {pages} {053615} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Hall}\ and\ \citenamefont
+      {Vinen}(1956{\natexlab{a}})}]{hall-vinen-1956a}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.~E.}\ \bibnamefont
+      {Hall}}\ and\ \bibinfo {author} {\bibfnamefont {W.~F.}\ \bibnamefont
+      {Vinen}},\ }\bibfield  {title} {\bibinfo {title} {The rotation of liquid
+      helium~{{II}}. i. experiments on the propagation of secound sound in
+      uniformly rotating helium {{II}}},\ }\href@noop {} {\bibfield  {journal}
+      {\bibinfo  {journal} {Proc. R. Soc. London A}\ }\textbf {\bibinfo {volume}
+      {238}},\ \bibinfo {pages} {204} (\bibinfo {year}
+      {1956}{\natexlab{a}})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Hall}\ and\ \citenamefont
+      {Vinen}(1956{\natexlab{b}})}]{hall-vinen-1956b}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.~E.}\ \bibnamefont
+      {Hall}}\ and\ \bibinfo {author} {\bibfnamefont {W.~F.}\ \bibnamefont
+      {Vinen}},\ }\bibfield  {title} {\bibinfo {title} {The rotation of liquid
+      helium~{{II}}. ii. the theory of mutual friction in uniformly rotating helium
+      {{II}}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Proc. R.
+      Soc. London A}\ }\textbf {\bibinfo {volume} {238}},\ \bibinfo {pages} {215}
+      (\bibinfo {year} {1956}{\natexlab{b}})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Maurer}\ and\ \citenamefont
+      {Tabeling}(1998)}]{maurer1998}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+      {Maurer}}\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+      {Tabeling}},\ }\bibfield  {title} {\bibinfo {title} {Local investigation of
+      superfluid turbulence},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+      {journal} {Europhys. Lett.}\ }\textbf {\bibinfo {volume} {43}},\ \bibinfo
+      {pages} {29} (\bibinfo {year} {1998})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Salort}\ \emph {et~al.}(2010)\citenamefont {Salort},
+      \citenamefont {Baudet}, \citenamefont {Castaing}, \citenamefont {Chabaud},
+      \citenamefont {Daviaud}, \citenamefont {Didelot}, \citenamefont {Diribarne},
+      \citenamefont {Dubrulle}, \citenamefont {Gagne}, \citenamefont {Gauthier},
+      \citenamefont {Girard}, \citenamefont {H\'ebral}, \citenamefont {B.},
+      \citenamefont {Thibault},\ and\ \citenamefont {Roche}}]{salort2010turbulent}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+      {Salort}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Baudet}},
+      \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Castaing}}, \bibinfo
+      {author} {\bibfnamefont {B.}~\bibnamefont {Chabaud}}, \bibinfo {author}
+      {\bibfnamefont {F.}~\bibnamefont {Daviaud}}, \bibinfo {author} {\bibfnamefont
+      {T.}~\bibnamefont {Didelot}}, \bibinfo {author} {\bibfnamefont
+      {P.}~\bibnamefont {Diribarne}}, \bibinfo {author} {\bibfnamefont
+      {B.}~\bibnamefont {Dubrulle}}, \bibinfo {author} {\bibfnamefont
+      {Y.}~\bibnamefont {Gagne}}, \bibinfo {author} {\bibfnamefont
+      {F.}~\bibnamefont {Gauthier}}, \bibinfo {author} {\bibfnamefont
+      {A.}~\bibnamefont {Girard}}, \bibinfo {author} {\bibfnamefont
+      {B.}~\bibnamefont {H\'ebral}}, \bibinfo {author} {\bibfnamefont
+      {R.}~\bibnamefont {B.}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+      {Thibault}},\ and\ \bibinfo {author} {\bibfnamefont {P.-E.}\ \bibnamefont
+      {Roche}},\ }\bibfield  {title} {\bibinfo {title} {Turbulent velocity spectra
+      in superfluid flows},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+      {journal} {Phys. Fluids}\ }\textbf {\bibinfo {volume} {22}} (\bibinfo {year}
+      {2010})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Baggaley}\ \emph {et~al.}(2012)\citenamefont
+      {Baggaley}, \citenamefont {Sherwin}, \citenamefont {Barenghi},\ and\
+      \citenamefont {Sergeev}}]{baggaley2012}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~W.}\ \bibnamefont
+      {Baggaley}}, \bibinfo {author} {\bibfnamefont {L.~K.}\ \bibnamefont
+      {Sherwin}}, \bibinfo {author} {\bibfnamefont {C.~F.}\ \bibnamefont
+      {Barenghi}},\ and\ \bibinfo {author} {\bibfnamefont {Y.~A.}\ \bibnamefont
+      {Sergeev}},\ }\bibfield  {title} {\bibinfo {title} {Thermally and
+      mechanically driven quantum turbulence in helium {{II}}},\ }\href@noop {}
+      {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo
+      {volume} {86}},\ \bibinfo {pages} {104501} (\bibinfo {year}
+      {2012})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {{Sherwin-Robson}}\ \emph {et~al.}(2015)\citenamefont
+      {{Sherwin-Robson}}, \citenamefont {Barenghi},\ and\ \citenamefont
+      {Baggaley}}]{sherwin-robson2015}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~K.}\ \bibnamefont
+      {{Sherwin-Robson}}}, \bibinfo {author} {\bibfnamefont {C.~F.}\ \bibnamefont
+      {Barenghi}},\ and\ \bibinfo {author} {\bibfnamefont {A.~W.}\ \bibnamefont
+      {Baggaley}},\ }\bibfield  {title} {\bibinfo {title} {Local and nonlocal
+      dynamics in superfluid turbulence},\ }\href@noop {} {\bibfield  {journal}
+      {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {91}},\
+      \bibinfo {pages} {104517} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Müller}\ and\ \citenamefont
+      {Krstulovic}(2020)}]{Muller_KolmogorovKelvinWave_2020}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~P.}\ \bibnamefont
+      {Müller}}\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+      {Krstulovic}},\ }\bibfield  {title} {\bibinfo {title} {Kolmogorov and
+      {Kelvin} wave cascades in a generalized model for quantum turbulence},\
+      }\href {https://doi.org/10.1103/PhysRevB.102.134513} {\bibfield  {journal}
+      {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
+      {102}},\ \bibinfo {pages} {134513} (\bibinfo {year} {2020})}\BibitemShut
+      {NoStop}%
+    \bibitem [{\citenamefont {Müller}\ \emph {et~al.}(2021)\citenamefont
+      {Müller}, \citenamefont {Polanco},\ and\ \citenamefont
+      {Krstulovic}}]{Muller_IntermittencyVelocityCirculation_2021}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~P.}\ \bibnamefont
+      {Müller}}, \bibinfo {author} {\bibfnamefont {J.~I.}\ \bibnamefont
+      {Polanco}},\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+      {Krstulovic}},\ }\bibfield  {title} {\bibinfo {title} {Intermittency of
+      {Velocity} {Circulation} in {Quantum} {Turbulence}},\ }\href
+      {https://doi.org/10.1103/PhysRevX.11.011053} {\bibfield  {journal} {\bibinfo
+      {journal} {Phys. Rev. X}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo
+      {pages} {011053} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Middleton-Spencer}\ \emph {et~al.}(2022)\citenamefont
+      {Middleton-Spencer}, \citenamefont {Orozco}, \citenamefont {Galantucci},
+      \citenamefont {Moreno}, \citenamefont {Parker}, \citenamefont {Machado},
+      \citenamefont {Bagnato},\ and\ \citenamefont
+      {Barenghi}}]{middleton-spencer2022}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.~A.~J.}\
+      \bibnamefont {Middleton-Spencer}}, \bibinfo {author} {\bibfnamefont
+      {A.~D.~G.}\ \bibnamefont {Orozco}}, \bibinfo {author} {\bibfnamefont
+      {L.}~\bibnamefont {Galantucci}}, \bibinfo {author} {\bibfnamefont
+      {M.}~\bibnamefont {Moreno}}, \bibinfo {author} {\bibfnamefont {N.~G.}\
+      \bibnamefont {Parker}}, \bibinfo {author} {\bibfnamefont {L.~A.}\
+      \bibnamefont {Machado}}, \bibinfo {author} {\bibfnamefont {V.~S.}\
+      \bibnamefont {Bagnato}},\ and\ \bibinfo {author} {\bibfnamefont {C.~F.}\
+      \bibnamefont {Barenghi}},\ }\bibfield  {title} {\bibinfo {title} {Evidence of
+      strong quantum turbulence in {{B}}ose-{{E}}instein condensates},\ }\href@noop
+      {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Research}\ }\textbf
+      {\bibinfo {volume} {5}},\ \bibinfo {pages} {043081} (\bibinfo {year}
+      {2022})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Bradley}\ and\ \citenamefont
+      {Anderson}(2012)}]{bradley2012energy}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~S.}\ \bibnamefont
+      {Bradley}}\ and\ \bibinfo {author} {\bibfnamefont {B.~P.}\ \bibnamefont
+      {Anderson}},\ }\bibfield  {title} {\bibinfo {title} {Energy spectra of vortex
+      distributions in two-dimensional quantum turbulence},\ }\href@noop {}
+      {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. X}\ }\textbf {\bibinfo
+      {volume} {2}},\ \bibinfo {pages} {041001} (\bibinfo {year}
+      {2012})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Reeves}\ \emph {et~al.}(2013)\citenamefont {Reeves},
+      \citenamefont {Billam}, \citenamefont {Anderson},\ and\ \citenamefont
+      {Bradley}}]{reeves2013}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~T.}\ \bibnamefont
+      {Reeves}}, \bibinfo {author} {\bibfnamefont {T.~P.}\ \bibnamefont {Billam}},
+      \bibinfo {author} {\bibfnamefont {B.~P.}\ \bibnamefont {Anderson}},\ and\
+      \bibinfo {author} {\bibfnamefont {A.~S.}\ \bibnamefont {Bradley}},\
+      }\bibfield  {title} {\bibinfo {title} {Inverse energy cascade in forced
+      two-dimensional quantum turbulence},\ }\href@noop {} {\bibfield  {journal}
+      {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {110}},\
+      \bibinfo {pages} {104501} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Simula}\ \emph {et~al.}(2014)\citenamefont {Simula},
+      \citenamefont {Davis},\ and\ \citenamefont
+      {Helmerson}}]{simula2014emergence}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+      {Simula}}, \bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont {Davis}},\
+      and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Helmerson}},\
+      }\bibfield  {title} {\bibinfo {title} {Emergence of order from turbulence in
+      an isolated planar superfluid},\ }\href
+      {https://doi.org/10.1103/PhysRevLett.113.165302} {\bibfield  {journal}
+      {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {113}},\
+      \bibinfo {pages} {165302} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Müller}\ and\ \citenamefont
+      {Krstulovic}(2024)}]{Muller_ExploringEquivalenceTwoDimensional_2024}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~P.}\ \bibnamefont
+      {Müller}}\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+      {Krstulovic}},\ }\bibfield  {title} {\bibinfo {title} {Exploring the
+      {Equivalence} between {Two}-{Dimensional} {Classical} and {Quantum}
+      {Turbulence} through {Velocity} {Circulation} {Statistics}},\ }\href
+      {https://doi.org/10.1103/PhysRevLett.132.094002} {\bibfield  {journal}
+      {\bibinfo  {journal} {Phys. Rev. Letters}\ }\textbf {\bibinfo {volume}
+      {132}},\ \bibinfo {pages} {094002} (\bibinfo {year} {2024})}\BibitemShut
+      {NoStop}%
+    \bibitem [{\citenamefont {Johnstone}\ \emph {et~al.}(2019)\citenamefont
+      {Johnstone}, \citenamefont {Groszek}, \citenamefont {Starkey}, \citenamefont
+      {Billington}, \citenamefont {Simula},\ and\ \citenamefont
+      {Helmerson}}]{johnstone2019evolution}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~P.}\ \bibnamefont
+      {Johnstone}}, \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont
+      {Groszek}}, \bibinfo {author} {\bibfnamefont {P.~T.}\ \bibnamefont
+      {Starkey}}, \bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont
+      {Billington}}, \bibinfo {author} {\bibfnamefont {T.~P.}\ \bibnamefont
+      {Simula}},\ and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+      {Helmerson}},\ }\bibfield  {title} {\bibinfo {title} {Evolution of
+      large-scale flow from turbulence in a two-dimensional superfluid},\
+      }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf
+      {\bibinfo {volume} {364}},\ \bibinfo {pages} {1267} (\bibinfo {year}
+      {2019})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Gauthier}\ \emph {et~al.}(2019)\citenamefont
+      {Gauthier}, \citenamefont {Reeves}, \citenamefont {Yu}, \citenamefont
+      {Bradley}, \citenamefont {Baker}, \citenamefont {Bell}, \citenamefont
+      {Rubinsztein-Dunlop}, \citenamefont {Davis},\ and\ \citenamefont
+      {Neely}}]{gauthier2019giant}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+      {Gauthier}}, \bibinfo {author} {\bibfnamefont {M.~T.}\ \bibnamefont
+      {Reeves}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Yu}}, \bibinfo
+      {author} {\bibfnamefont {A.~S.}\ \bibnamefont {Bradley}}, \bibinfo {author}
+      {\bibfnamefont {M.~A.}\ \bibnamefont {Baker}}, \bibinfo {author}
+      {\bibfnamefont {T.~A.}\ \bibnamefont {Bell}}, \bibinfo {author}
+      {\bibfnamefont {H.}~\bibnamefont {Rubinsztein-Dunlop}}, \bibinfo {author}
+      {\bibfnamefont {M.~J.}\ \bibnamefont {Davis}},\ and\ \bibinfo {author}
+      {\bibfnamefont {T.~W.}\ \bibnamefont {Neely}},\ }\bibfield  {title} {\bibinfo
+      {title} {Giant vortex clusters in a two-dimensional quantum fluid},\
+      }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf
+      {\bibinfo {volume} {364}},\ \bibinfo {pages} {1264} (\bibinfo {year}
+      {2019})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Fj{\o}rtoft}(1953)}]{fjortoft1953changes}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+      {Fj{\o}rtoft}},\ }\bibfield  {title} {\bibinfo {title} {On the changes in the
+      spectral distribution of kinetic energy for twodimensional, nondivergent
+      flow},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Tellus}\
+      }\textbf {\bibinfo {volume} {5}},\ \bibinfo {pages} {225} (\bibinfo {year}
+      {1953})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Zhu}\ \emph {et~al.}(2023)\citenamefont {Zhu},
+      \citenamefont {Semisalov}, \citenamefont {Krstulovic},\ and\ \citenamefont
+      {Nazarenko}}]{Zhu_DirectInverseCascades_2023}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+      {Zhu}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Semisalov}},
+      \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Krstulovic}},\ and\
+      \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Nazarenko}},\ }\bibfield
+      {title} {\bibinfo {title} {Direct and {Inverse} {Cascades} in {Turbulent}
+      {Bose}-{Einstein} {Condensates}},\ }\href
+      {https://doi.org/10.1103/PhysRevLett.130.133001} {\bibfield  {journal}
+      {\bibinfo  {journal} {Phys. Rev. Letters}\ }\textbf {\bibinfo {volume}
+      {130}},\ \bibinfo {pages} {133001} (\bibinfo {year} {2023})}\BibitemShut
+      {NoStop}%
+    \bibitem [{\citenamefont {Moffatt}(1969)}]{moffatt1969}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.~K.}\ \bibnamefont
+      {Moffatt}},\ }\bibfield  {title} {\bibinfo {title} {The degree of knottedness
+      of tangled vortex lines},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+      {journal} {J. Fluid Mech.}\ }\textbf {\bibinfo {volume} {36}},\ \bibinfo
+      {pages} {7} (\bibinfo {year} {1969})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Biferale}\ \emph {et~al.}(2012)\citenamefont
+      {Biferale}, \citenamefont {Musacchio},\ and\ \citenamefont
+      {Toschi}}]{biferaleInverseEnergyCascade2012a}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+      {Biferale}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+      {Musacchio}},\ and\ \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+      {Toschi}},\ }\bibfield  {title} {\bibinfo {title} {Inverse energy cascade in
+      three-dimensional isotropic turbulence},\ }\href@noop {} {\bibfield
+      {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
+      {volume} {108}},\ \bibinfo {pages} {164501} (\bibinfo {year}
+      {2012})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Biferale}\ \emph {et~al.}(2013)\citenamefont
+      {Biferale}, \citenamefont {Musacchio},\ and\ \citenamefont
+      {Toschi}}]{biferale-etal-2013}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+      {Biferale}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+      {Musacchio}},\ and\ \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+      {Toschi}},\ }\bibfield  {title} {\bibinfo {title} {Split energy–helicity
+      cascades in three-dimensional homogeneous and isotropic turbulence},\ }\href
+      {https://doi.org/10.1017/jfm.2013.349} {\bibfield  {journal} {\bibinfo
+      {journal} {J. Fluid Mech.}\ }\textbf {\bibinfo {volume} {730}},\ \bibinfo
+      {pages} {309–327} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Sahoo}\ \emph {et~al.}(2017)\citenamefont {Sahoo},
+      \citenamefont {Alexakis},\ and\ \citenamefont {Biferale}}]{sahoo-etal-2017}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+      {Sahoo}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Alexakis}},\
+      and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Biferale}},\
+      }\bibfield  {title} {\bibinfo {title} {Discontinuous transition from direct
+      to inverse cascade in three-dimensional turbulence},\ }\href@noop {}
+      {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
+      {\bibinfo {volume} {118}},\ \bibinfo {pages} {164501} (\bibinfo {year}
+      {2017})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Plunian}\ \emph {et~al.}(2020)\citenamefont
+      {Plunian}, \citenamefont {Teimurazov}, \citenamefont {Stepanov},\ and\
+      \citenamefont {Verma}}]{plunianInverseCascadeEnergy2020a}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+      {Plunian}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Teimurazov}},
+      \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Stepanov}},\ and\
+      \bibinfo {author} {\bibfnamefont {M.~K.}\ \bibnamefont {Verma}},\ }\bibfield
+      {title} {\bibinfo {title} {Inverse cascade of energy in helical turbulence},\
+      }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {J. Fluid Mech.}\
+      }\textbf {\bibinfo {volume} {895}},\ \bibinfo {pages} {A13} (\bibinfo {year}
+      {2020})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Koplik}\ and\ \citenamefont
+      {Levine}(1993)}]{koplik-levine-1993}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+      {Koplik}}\ and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+      {Levine}},\ }\bibfield  {title} {\bibinfo {title} {Vortex reconnection in
+      superfluid helium},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+      {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {71}},\ \bibinfo
+      {pages} {1375} (\bibinfo {year} {1993})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Bewley}\ \emph {et~al.}(2008)\citenamefont {Bewley},
+      \citenamefont {Paoletti}, \citenamefont {Sreenivasan},\ and\ \citenamefont
+      {Lathrop}}]{bewley-etal-2008}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~P.}\ \bibnamefont
+      {Bewley}}, \bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont
+      {Paoletti}}, \bibinfo {author} {\bibfnamefont {K.~R.}\ \bibnamefont
+      {Sreenivasan}},\ and\ \bibinfo {author} {\bibfnamefont {D.~P.}\ \bibnamefont
+      {Lathrop}},\ }\bibfield  {title} {\bibinfo {title} {Characterization of
+      reconnecting vortices in superfluid helium},\ }\href@noop {} {\bibfield
+      {journal} {\bibinfo  {journal} {Proc. Natl. Acad. Sci. USA}\ }\textbf
+      {\bibinfo {volume} {105}},\ \bibinfo {pages} {13707} (\bibinfo {year}
+      {2008})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Rorai}\ \emph {et~al.}(2016)\citenamefont {Rorai},
+      \citenamefont {Skipper}, \citenamefont {Kerr},\ and\ \citenamefont
+      {Sreenivasan}}]{rorai-etal-2016}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+      {Rorai}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Skipper}},
+      \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Kerr}},\ and\ \bibinfo
+      {author} {\bibfnamefont {K.}~\bibnamefont {Sreenivasan}},\ }\bibfield
+      {title} {\bibinfo {title} {Approach and separation of quantum vortices with
+      balanced cores},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+      {J. Fluid Mech.}\ }\textbf {\bibinfo {volume} {808}},\ \bibinfo {pages} {641}
+      (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Serafini}\ \emph {et~al.}(2017)\citenamefont
+      {Serafini}, \citenamefont {Galantucci}, \citenamefont {Iseni}, \citenamefont
+      {Bienaime}, \citenamefont {Bisset}, \citenamefont {Barenghi}, \citenamefont
+      {Dalfovo}, \citenamefont {Lamporesi},\ and\ \citenamefont
+      {Ferrari}}]{serafini-etal-2017}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+      {Serafini}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+      {Galantucci}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Iseni}},
+      \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Bienaime}}, \bibinfo
+      {author} {\bibfnamefont {R.}~\bibnamefont {Bisset}}, \bibinfo {author}
+      {\bibfnamefont {C.~F.}\ \bibnamefont {Barenghi}}, \bibinfo {author}
+      {\bibfnamefont {F.}~\bibnamefont {Dalfovo}}, \bibinfo {author} {\bibfnamefont
+      {G.}~\bibnamefont {Lamporesi}},\ and\ \bibinfo {author} {\bibfnamefont
+      {G.}~\bibnamefont {Ferrari}},\ }\bibfield  {title} {\bibinfo {title} {Vortex
+      reconnections and rebounds in trapped atomic {{B}}ose-{{E}}instein
+      condensates},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+      {Phys. Rev. X}\ }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages} {021031}
+      (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Galantucci}\ \emph {et~al.}(2019)\citenamefont
+      {Galantucci}, \citenamefont {Baggaley}, \citenamefont {Parker},\ and\
+      \citenamefont {Barenghi}}]{galantucci-baggaley-parker-barenghi-2019}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+      {Galantucci}}, \bibinfo {author} {\bibfnamefont {A.~W.}\ \bibnamefont
+      {Baggaley}}, \bibinfo {author} {\bibfnamefont {N.~G.}\ \bibnamefont
+      {Parker}},\ and\ \bibinfo {author} {\bibfnamefont {C.~F.}\ \bibnamefont
+      {Barenghi}},\ }\bibfield  {title} {\bibinfo {title} {Crossover from
+      interaction to driven regimes in quantum vortex reconnections},\ }\href@noop
+      {} {\bibfield  {journal} {\bibinfo  {journal} {Proc. Natl. Acad. Sci. USA}\
+      }\textbf {\bibinfo {volume} {116}},\ \bibinfo {pages} {12204} (\bibinfo
+      {year} {2019})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Villois}\ \emph {et~al.}(2017)\citenamefont
+      {Villois}, \citenamefont {Proment},\ and\ \citenamefont
+      {Krstulovic}}]{villoisUniversalNonuniversalAspects2017}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+      {Villois}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Proment}},\
+      and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Krstulovic}},\
+      }\bibfield  {title} {\bibinfo {title} {Universal and nonuniversal aspects of
+      vortex reconnections in superfluids},\ }\href
+      {https://doi.org/10.1103/PhysRevFluids.2.044701} {\bibfield  {journal}
+      {\bibinfo  {journal} {Phys. Rev. Fluids}\ }\textbf {\bibinfo {volume}
+      {2}},\ \bibinfo {pages} {044701} (\bibinfo {year} {2017})}\BibitemShut
+      {NoStop}%
+    \bibitem [{\citenamefont {Villois}\ \emph {et~al.}(2020)\citenamefont
+      {Villois}, \citenamefont {Proment},\ and\ \citenamefont
+      {Krstulovic}}]{villois2020irreversible}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+      {Villois}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Proment}},\
+      and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Krstulovic}},\
+      }\bibfield  {title} {\bibinfo {title} {Irreversible dynamics of vortex
+      reconnections in quantum fluids},\ }\href@noop {} {\bibfield  {journal}
+      {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {125}},\
+      \bibinfo {pages} {164501} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Galantucci}\ \emph {et~al.}(2020)\citenamefont
+      {Galantucci}, \citenamefont {Baggaley}, \citenamefont {Barenghi},\ and\
+      \citenamefont {Krstulovic}}]{galantucciNewSelfconsistentApproach2020b}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+      {Galantucci}}, \bibinfo {author} {\bibfnamefont {A.~W.}\ \bibnamefont
+      {Baggaley}}, \bibinfo {author} {\bibfnamefont {C.~F.}\ \bibnamefont
+      {Barenghi}},\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+      {Krstulovic}},\ }\bibfield  {title} {\bibinfo {title} {A new self-consistent
+      approach of quantum turbulence in superfluid helium},\ }\href@noop {}
+      {\bibfield  {journal} {\bibinfo  {journal} {Eur. Phys. J. Plus}\ }\textbf
+      {\bibinfo {volume} {135}},\ \bibinfo {pages} {547} (\bibinfo {year}
+      {2020})}\BibitemShut {NoStop}%
+    \bibitem [{sup()}]{suppMat}%
+      \BibitemOpen
+      \href@noop {} {\bibinfo {title} {See supplementary materials}}\BibitemShut
+      {NoStop}%
+    \bibitem [{\citenamefont {Stasiak}\ \emph {et~al.}(2024)\citenamefont
+      {Stasiak}, \citenamefont {Xing}, \citenamefont {Alihosseini}, \citenamefont
+      {Barenghi}, \citenamefont {Baggaley}, \citenamefont {Guo}, \citenamefont
+      {Galantucci},\ and\ \citenamefont {Krstulovic}}]{stasiak2024quantum}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~Z.}\ \bibnamefont
+      {Stasiak}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Xing}},
+      \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Alihosseini}}, \bibinfo
+      {author} {\bibfnamefont {C.~F.}\ \bibnamefont {Barenghi}}, \bibinfo {author}
+      {\bibfnamefont {A.~W.}\ \bibnamefont {Baggaley}}, \bibinfo {author}
+      {\bibfnamefont {W.}~\bibnamefont {Guo}}, \bibinfo {author} {\bibfnamefont
+      {L.}~\bibnamefont {Galantucci}},\ and\ \bibinfo {author} {\bibfnamefont
+      {G.}~\bibnamefont {Krstulovic}},\ }\bibfield  {title} {\bibinfo {title}
+      {Experimental and theoretical evidence of universality in superfluid vortex
+      reconnections},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+      {arXiv}\ ,\ \bibinfo {pages} {2411.08942}} (\bibinfo {year}
+      {2024})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Waleffe}(1992)}]{waleffe-1992}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+      {Waleffe}},\ }\bibfield  {title} {\bibinfo {title} {The nature of triad
+      interactions in homogeneous turbulence},\ }\href@noop {} {\bibfield
+      {journal} {\bibinfo  {journal} {Phys. Fluids A}\ }\textbf {\bibinfo {volume}
+      {4}},\ \bibinfo {pages} {350} (\bibinfo {year} {1992})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Barenghi}\ and\ \citenamefont
+      {Samuels}(2004)}]{barenghi2004}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~F.}\ \bibnamefont
+      {Barenghi}}\ and\ \bibinfo {author} {\bibfnamefont {D.~C.}\ \bibnamefont
+      {Samuels}},\ }\bibfield  {title} {\bibinfo {title} {Scaling laws of vortex
+      reconnections},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+      {J. Low Temp. Phys.}\ }\textbf {\bibinfo {volume} {136}},\ \bibinfo {pages}
+      {281} (\bibinfo {year} {2004})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Roche}\ \emph {et~al.}(2007)\citenamefont {Roche},
+      \citenamefont {Diribarne}, \citenamefont {Didelot}, \citenamefont {Fran{\c
+      c}ais}, \citenamefont {Rousseau},\ and\ \citenamefont
+      {Willaime}}]{roche2007}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.-E.}\ \bibnamefont
+      {Roche}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Diribarne}},
+      \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Didelot}}, \bibinfo
+      {author} {\bibfnamefont {O.}~\bibnamefont {Fran{\c c}ais}}, \bibinfo {author}
+      {\bibfnamefont {L.}~\bibnamefont {Rousseau}},\ and\ \bibinfo {author}
+      {\bibfnamefont {H.}~\bibnamefont {Willaime}},\ }\bibfield  {title} {\bibinfo
+      {title} {Vortex density spectrum of quantum turbulence},\ }\href@noop {}
+      {\bibfield  {journal} {\bibinfo  {journal} {EPL}\ }\textbf {\bibinfo {volume}
+      {77}},\ \bibinfo {pages} {66002} (\bibinfo {year} {2007})}\BibitemShut
+      {NoStop}%
+    \bibitem [{\citenamefont {Babuin}\ \emph {et~al.}(2014)\citenamefont {Babuin},
+      \citenamefont {Varga}, \citenamefont {Skrbek}, \citenamefont {L\'ev\^eque},\
+      and\ \citenamefont {Roche}}]{Babuin2014}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+      {Babuin}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Varga}},
+      \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Skrbek}}, \bibinfo
+      {author} {\bibfnamefont {E.}~\bibnamefont {L\'ev\^eque}},\ and\ \bibinfo
+      {author} {\bibfnamefont {P.-E.}\ \bibnamefont {Roche}},\ }\bibfield  {title}
+      {\bibinfo {title} {Effective viscosity in quantum turbulence: a steady state
+      approach},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+      {Europhys. Lett.}\ }\textbf {\bibinfo {volume} {106}},\ \bibinfo {pages}
+      {24006} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
+    \bibitem [{not()}]{notes_recon}%
+      \BibitemOpen
+      \href@noop {} {\bibinfo {title} {The symmetry breaking of the vortex
+      configuration is a key element, as perfectly symmetrical reconnections (with
+      opposite vortex line orientations) would inject net helicities of opposite
+      sign leading globally to a non-chiral flow.}}\BibitemShut {Stop}%
+    \bibitem [{\citenamefont {Polanco}\ and\ \citenamefont
+      {Krstulovic}(2020)}]{polanco2020}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+      {Polanco}}\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+      {Krstulovic}},\ }\bibfield  {title} {\bibinfo {title} {Counterflow-induced
+      inverse energy cascade in three-dimensional superfluid turbulence},\
+      }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\
+      }\textbf {\bibinfo {volume} {125}},\ \bibinfo {pages} {254504} (\bibinfo
+      {year} {2020})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Di~Leoni}\ \emph {et~al.}(2026)\citenamefont
+      {Di~Leoni}, \citenamefont {Mininni},\ and\ \citenamefont {ME}}]{dileoni2016}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+      {Di~Leoni}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Mininni}},\
+      and\ \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {ME}},\ }\bibfield
+      {title} {\bibinfo {title} {Dual cascade and dissipation mechanisms in helical
+      quantum turbulence},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+      {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume} {95}},\ \bibinfo
+      {pages} {053636} (\bibinfo {year} {2026})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Galantucci}\ \emph {et~al.}(2021)\citenamefont
+      {Galantucci}, \citenamefont {Barenghi}, \citenamefont {Parker},\ and\
+      \citenamefont {Baggaley}}]{galantucci2021}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+      {Galantucci}}, \bibinfo {author} {\bibfnamefont {{\relax CF}.}~\bibnamefont
+      {Barenghi}}, \bibinfo {author} {\bibfnamefont {{\relax NG}.}~\bibnamefont
+      {Parker}},\ and\ \bibinfo {author} {\bibfnamefont {{\relax AW}.}~\bibnamefont
+      {Baggaley}},\ }\bibfield  {title} {\bibinfo {title} {Mesoscale helicity
+      distinguishes {{Vinen}} from {{Kolmogorov}} turbulence in helium-{{II}}},\
+      }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
+      }\textbf {\bibinfo {volume} {103}},\ \bibinfo {pages} {144503} (\bibinfo
+      {year} {2021})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Scheeler}\ \emph {et~al.}(2014)\citenamefont
+      {Scheeler}, \citenamefont {Kleckner}, \citenamefont {Proment}, \citenamefont
+      {Kindlmann},\ and\ \citenamefont {WTM}}]{scheeler2014}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+      {Scheeler}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Kleckner}},
+      \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Proment}}, \bibinfo
+      {author} {\bibfnamefont {G.}~\bibnamefont {Kindlmann}},\ and\ \bibinfo
+      {author} {\bibfnamefont {I.}~\bibnamefont {WTM}},\ }\bibfield  {title}
+      {\bibinfo {title} {Helicity conservation by flow across scales in
+      reconnecting vortex links and knots},\ }\href@noop {} {\bibfield  {journal}
+      {\bibinfo  {journal} {Proc Natl Acad Sci Usa}\ }\textbf {\bibinfo {volume}
+      {111}},\ \bibinfo {pages} {15350} (\bibinfo {year} {2014})}\BibitemShut
+      {NoStop}%
+    \bibitem [{\citenamefont {Schwarz}(1988)}]{schwarz1988}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {{\relax
+      KW}.}~\bibnamefont {Schwarz}},\ }\bibfield  {title} {\bibinfo {title}
+      {Three-dimensional vortex dynamics in superfluid {$^{4}$}{{He}}},\
+      }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
+      }\textbf {\bibinfo {volume} {38}},\ \bibinfo {pages} {2398} (\bibinfo {year}
+      {1988})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Proment}\ and\ \citenamefont
+      {Krstulovic}(2020)}]{promentMatchingTheoryCharacterize2020a}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+      {Proment}}\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+      {Krstulovic}},\ }\bibfield  {title} {\bibinfo {title} {Matching theory to
+      characterize sound emission during vortex reconnection in quantum fluids},\
+      }\href {https://doi.org/10.1103/PhysRevFluids.5.104701} {\bibfield  {journal}
+      {\bibinfo  {journal} {Phys. Rev. Fluids}\ }\textbf {\bibinfo {volume} {5}},\
+      \bibinfo {pages} {104701} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont
+      {Baggaley}(2012)}]{baggaleySensitivityVortexFilament2012a}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~W.}\ \bibnamefont
+      {Baggaley}},\ }\bibfield  {title} {\bibinfo {title} {The sensitivity of the
+      vortex filament method to different reconnection models},\ }\href@noop {}
+      {\bibfield  {journal} {\bibinfo  {journal} {J. Low Temp. Phys.}\ }\textbf
+      {\bibinfo {volume} {168}},\ \bibinfo {pages} {18} (\bibinfo {year}
+      {2012})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Galantucci}\ \emph {et~al.}(2015)\citenamefont
+      {Galantucci}, \citenamefont {Sciacca},\ and\ \citenamefont
+      {Barenghi}}]{galantucciCoupledNormalFluid2015a}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+      {Galantucci}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+      {Sciacca}},\ and\ \bibinfo {author} {\bibfnamefont {{\relax
+      CF}.}~\bibnamefont {Barenghi}},\ }\bibfield  {title} {\bibinfo {title}
+      {Coupled normal fluid and superfluid profiles of turbulent helium {{II}} in
+      channels},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys
+      Rev B}\ }\textbf {\bibinfo {volume} {92}},\ \bibinfo {pages} {174530}
+      (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+    \bibitem [{\citenamefont {Gualtieri}\ \emph {et~al.}(2015)\citenamefont
+      {Gualtieri}, \citenamefont {Picano}, \citenamefont {Sardina},\ and\
+      \citenamefont {Casciola}}]{gualtieri2015exact}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+      {Gualtieri}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Picano}},
+      \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Sardina}},\ and\ \bibinfo
+      {author} {\bibfnamefont {C.~M.}\ \bibnamefont {Casciola}},\ }\bibfield
+      {title} {\bibinfo {title} {Exact regularized point particle method for
+      multiphase flows in the two-way coupling regime},\ }\href@noop {} {\bibfield
+      {journal} {\bibinfo  {journal} {J. Fluid Mech.}\ }\textbf {\bibinfo {volume}
+      {773}},\ \bibinfo {pages} {520} (\bibinfo {year} {2015})}\BibitemShut
+      {NoStop}%
+    \bibitem [{\citenamefont {Gualtieri}\ \emph {et~al.}(2017)\citenamefont
+      {Gualtieri}, \citenamefont {Battista},\ and\ \citenamefont
+      {Casciola}}]{gualtieri2017turbulence}%
+      \BibitemOpen
+      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+      {Gualtieri}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+      {Battista}},\ and\ \bibinfo {author} {\bibfnamefont {C.~M.}\ \bibnamefont
+      {Casciola}},\ }\bibfield  {title} {\bibinfo {title} {Turbulence modulation in
+      heavy-loaded suspensions of tiny particles},\ }\href@noop {} {\bibfield
+      {journal} {\bibinfo  {journal} {Phys. Rev. Fluids}\ }\textbf {\bibinfo
+      {volume} {2}},\ \bibinfo {pages} {034304} (\bibinfo {year}
+      {2017})}\BibitemShut {NoStop}%
+    \end{thebibliography}%
 

### 2025-03-06 arxiv-submission.tex
Fixed typos

@@
 triggers the inverse energy cascade which is observed numerically in  
-large-scale simulations of counterflow turbulence at large heat fluxes \cite{polanco2020}, which
+large-scale simulations of counterflow turbulence at large heat fluxes \cite{polanco2020}, which is
 indeed inherently not isotropic.

### 2025-04-22 initial_submission.tex
Added initial submission file for comparisons

--- 2025-03-06 arxiv-submission.tex
@@
 %Control: production of eprint (0) enabled
-\begin{thebibliography}{61}%
+\begin{thebibliography}{55}%
 \makeatletter
@@
   {https://doi.org/10.1103/PhysRevLett.132.094002} {\bibfield  {journal}
-      {\bibinfo  {journal} {Phys. Rev. Letters}\ }\textbf {\bibinfo {volume}
+  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume}
   {132}},\ \bibinfo {pages} {094002} (\bibinfo {year} {2024})}\BibitemShut
@@
   {https://doi.org/10.1103/PhysRevLett.130.133001} {\bibfield  {journal}
-      {\bibinfo  {journal} {Phys. Rev. Letters}\ }\textbf {\bibinfo {volume}
+  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume}
   {130}},\ \bibinfo {pages} {133001} (\bibinfo {year} {2023})}\BibitemShut
@@
   reconnecting vortex links and knots},\ }\href@noop {} {\bibfield  {journal}
-      {\bibinfo  {journal} {Proc Natl Acad Sci Usa}\ }\textbf {\bibinfo {volume}
+  {\bibinfo  {journal} {Proc. Natl. Acad. Sci. Usa}\ }\textbf {\bibinfo {volume}
   {111}},\ \bibinfo {pages} {15350} (\bibinfo {year} {2014})}\BibitemShut
   {NoStop}%
-    \bibitem [{\citenamefont {Schwarz}(1988)}]{schwarz1988}%
-      \BibitemOpen
-      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {{\relax
-      KW}.}~\bibnamefont {Schwarz}},\ }\bibfield  {title} {\bibinfo {title}
-      {Three-dimensional vortex dynamics in superfluid {$^{4}$}{{He}}},\
-      }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\
-      }\textbf {\bibinfo {volume} {38}},\ \bibinfo {pages} {2398} (\bibinfo {year}
-      {1988})}\BibitemShut {NoStop}%
-    \bibitem [{\citenamefont {Proment}\ and\ \citenamefont
-      {Krstulovic}(2020)}]{promentMatchingTheoryCharacterize2020a}%
-      \BibitemOpen
-      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-      {Proment}}\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-      {Krstulovic}},\ }\bibfield  {title} {\bibinfo {title} {Matching theory to
-      characterize sound emission during vortex reconnection in quantum fluids},\
-      }\href {https://doi.org/10.1103/PhysRevFluids.5.104701} {\bibfield  {journal}
-      {\bibinfo  {journal} {Phys. Rev. Fluids}\ }\textbf {\bibinfo {volume} {5}},\
-      \bibinfo {pages} {104701} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
-    \bibitem [{\citenamefont
-      {Baggaley}(2012)}]{baggaleySensitivityVortexFilament2012a}%
-      \BibitemOpen
-      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~W.}\ \bibnamefont
-      {Baggaley}},\ }\bibfield  {title} {\bibinfo {title} {The sensitivity of the
-      vortex filament method to different reconnection models},\ }\href@noop {}
-      {\bibfield  {journal} {\bibinfo  {journal} {J. Low Temp. Phys.}\ }\textbf
-      {\bibinfo {volume} {168}},\ \bibinfo {pages} {18} (\bibinfo {year}
-      {2012})}\BibitemShut {NoStop}%
-    \bibitem [{\citenamefont {Galantucci}\ \emph {et~al.}(2015)\citenamefont
-      {Galantucci}, \citenamefont {Sciacca},\ and\ \citenamefont
-      {Barenghi}}]{galantucciCoupledNormalFluid2015a}%
-      \BibitemOpen
-      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-      {Galantucci}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-      {Sciacca}},\ and\ \bibinfo {author} {\bibfnamefont {{\relax
-      CF}.}~\bibnamefont {Barenghi}},\ }\bibfield  {title} {\bibinfo {title}
-      {Coupled normal fluid and superfluid profiles of turbulent helium {{II}} in
-      channels},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys
-      Rev B}\ }\textbf {\bibinfo {volume} {92}},\ \bibinfo {pages} {174530}
-      (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
-    \bibitem [{\citenamefont {Gualtieri}\ \emph {et~al.}(2015)\citenamefont
-      {Gualtieri}, \citenamefont {Picano}, \citenamefont {Sardina},\ and\
-      \citenamefont {Casciola}}]{gualtieri2015exact}%
-      \BibitemOpen
-      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-      {Gualtieri}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Picano}},
-      \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Sardina}},\ and\ \bibinfo
-      {author} {\bibfnamefont {C.~M.}\ \bibnamefont {Casciola}},\ }\bibfield
-      {title} {\bibinfo {title} {Exact regularized point particle method for
-      multiphase flows in the two-way coupling regime},\ }\href@noop {} {\bibfield
-      {journal} {\bibinfo  {journal} {J. Fluid Mech.}\ }\textbf {\bibinfo {volume}
-      {773}},\ \bibinfo {pages} {520} (\bibinfo {year} {2015})}\BibitemShut
-      {NoStop}%
-    \bibitem [{\citenamefont {Gualtieri}\ \emph {et~al.}(2017)\citenamefont
-      {Gualtieri}, \citenamefont {Battista},\ and\ \citenamefont
-      {Casciola}}]{gualtieri2017turbulence}%
-      \BibitemOpen
-      \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-      {Gualtieri}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-      {Battista}},\ and\ \bibinfo {author} {\bibfnamefont {C.~M.}\ \bibnamefont
-      {Casciola}},\ }\bibfield  {title} {\bibinfo {title} {Turbulence modulation in
-      heavy-loaded suspensions of tiny particles},\ }\href@noop {} {\bibfield
-      {journal} {\bibinfo  {journal} {Phys. Rev. Fluids}\ }\textbf {\bibinfo
-      {volume} {2}},\ \bibinfo {pages} {034304} (\bibinfo {year}
-      {2017})}\BibitemShut {NoStop}%
 \end{thebibliography}%
-
-\appendix
-\section*{Supplementary Materials}
-
-Using Schwarz mesoscopic model \cite{schwarz1988}, vortex lines can be described as space curves $\s(\xi,t)$ of infinitesimal thickness, with a single quantum of circulation $\kappa=h/m_4=9.97\times10^{-8}\text{m}^2/\text{s}$, where $h$ is Planck's constant, $m_4=6.65\times10^{-27}\text{kg}$ is the mass of one helium atom, $\xi$ is the natural parameterisation, arclength, and $t$ is time.
-These conditions are a good approximation, since the vortex core radius of superfluid \textsuperscript{4}He($a_0=10^{-10}\text{m}$) is much smaller than any of the length scales of interest in turbulent flows.
-The equation of motion is
-\begin{equation}
-	\dot{\s}(\xi,t) = \v_s + \frac{\beta}{1+\beta}\left[\v_{ns}\cdot \s'\right]\s' + \beta\s'\times\v_{ns}+\beta'\s'\times\left[\s'\times \v_{ns}\right],
-\end{equation}
-where $\dot{\s}=\partial\s/\partial t$, $\s'=\partial\s/\partial \xi$ is the unit tangent vector, $\v_{ns}=\v_n - \v_s$, $\v_n$ and $\v_s$ are the normal fluid and superfluid velocities at $\s$ and $\beta$,$\beta'$ are temperature and Reynolds number dependent mutual fricition coefficients \cite{galantucciNewSelfconsistentApproach2020b}.
-The superfluid velocity $\v_s$ at a point $\x$ is determined by the Biot-Savart law
-\begin{equation}
-	\v_s(\x,t) = \frac{\kappa}{4\pi}\oint_{\mathcal{T}}\frac{\s'(\xi,t)\times\left[\x-\s(\xi,t)\right]}{|\x-\s(\xi,t)|}d\xi,
-\end{equation}
-where $\mathcal{T}$ represents the entire vortex configuration.
-There is currently a lack of a well-defined theory of vortex reconnections in superfluid helium, like for the Gross-Pitaevskii equation \cite{villois2020irreversible,villoisUniversalNonuniversalAspects2017,promentMatchingTheoryCharacterize2020a}.
-An \emph{ad hoc} vortex reconnection algorithm is employed to resolve the collisions of vortex lines \cite{baggaleySensitivityVortexFilament2012a}.
-
-\begin{figure}
-	\centering
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=0.8\textwidth]{schematic.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.49\textwidth}
-		\centering
-		\includegraphics[width=0.9\textwidth]{schematic-2.png}
-	\end{subfigure}
-	\caption{Schematic diagram of the initial vortex configuration.}
-	\label{fig:schematic}
-\end{figure}
-
-A \emph{two-way model} is crucial to understand the accurately interept the back-reaction effect of the normal fluid on the vortex line and vice-versa \cite{stasiak2024quantum}.
-We self-consistently evolve the normal fluid $\v_n$ with a modified Navier-Stokes equation
-\begin{equation}
-	\frac{\partial \v_n}{\partial t} + (\v_n\cdot\nabla)\v_n = -\nabla\frac{p}{\rho} + \nu_n\nabla^2\v_n + \frac{\mathbf{F}_{ns}}{\rho_n},
-\end{equation}
-\begin{equation}
-	\mathbf{F}_{ns} = \oint_{\mathcal{T}}\mathbf{f}_{ns}\delta(\x-\x)d\xi, \quad \nabla\cdot\v_n=0,
-\end{equation}
-where $\rho=\rho_n + \rho_s$ is the total density, $\rho_n$ and $\rho_s$ are the normal fluid and superfluid densities, $p$ is the pressure, $\nu_n$ is the kinematic viscosity of the normal fluid and $\mathbf{f}_{ns}$ is the local friction per unit length \cite{galantucciCoupledNormalFluid2015a}
-\begin{equation}
-	\mathbf{f}_{ns} = -\mathcal{D}\s'\times\left[\s'\times(\dot{\s}-\v_n)\right]-\rho_n\kappa\s'\times(\v_n-\dot{\s}), 
-	\label{eq:mutual-friction}
-\end{equation}
-where $\mathcal{D}$ is a coefficient dependent on the vortex Reynolds number and intrinsic properties of the normal fluid.
-The regularisation of the mutual fricition force onto the normal fluid grid is physically motivated by the strongly localised injection of vorticity during the momentum exchange of point-like particles and viscous flow in classical fluid dynamics \cite{gualtieri2015exact,gualtieri2017turbulence}.
-In short, the localised vorticity induced by the relative motion between the vortex lines and the normal fluid is diffused to discretisation of the grid spacing $\Delta x$ in a time interval $\epsilon_R$.
-In this way, the delta-forced fricition as defined in Eq.~\ref{eq:mutual-friction} is regularised by a Gaussian function, the fundamental solution of the diffusion equation.
-Further details of the method for classical fluids are contained in \cite{gualtieri2015exact,gualtieri2017turbulence} and for FOUCAULT in \cite{galantucciNewSelfconsistentApproach2020b}.
-
-In this Letter, we report all results using dimensionless units, where the characteristic length scale is $\tilde{\lambda} = D/D_0$, where $D^3=(1\times10^{-3}\mathrm{m})^3$ is the dimensional cube size, $D_0^3=(2\pi)^3$ is the non-dimensional cubic computational domain.
-The time scale is given by $\tilde{\tau}=\tilde{\lambda}^2\nu_n^0\nu_n$, where the non-dimensional viscosity $\nu_n^0$ resolves the small scales of the normal fluid.
-In these simulations, these quanties are $\tilde{\lambda}=1.59\times10^{-4}$m, $\nu_n^0=0.32$ and $\tilde{\tau}=0.366$s at $T=1.9K$ and $\tilde{\tau}=0.485$s at $T=2.1K$.
-We consider an initial configuration of two pairs of orthongal vortices, initialised as shown in the schematic of Fig.~\ref{fig:schematic}.
-The seperation between vortices in each pair $d$ is set to be $d_v=0.5$ in dimensionless units, and the shortest distance between pairs is $D_v=\sqrt{(\pi-d_v/2)^2+\pi^2}\approx 3.08$, so that $d_v\ll D_v$.
-The Lagrangian discretisation of vortex lines is $\Delta \xi = 0.025$ (a total of 1340 discretisation points across the 4 vortex lines), using a timestep of $\Delta t_{VF} = 5.56\times10^{-6}$.
-For the normal fluid, a total of $N=256^3$ mesh point were used, with a timestep of $\Delta t_{NS} = 45\Delta t_{VF}$.
-
 \end{document}

### 2025-04-25 revision/referee-response.tex
Added .tex referee response file

\documentclass[a4paper,10pt]{letter}
\usepackage[margin=1in]{geometry}
\usepackage{lipsum}
\usepackage{xcolor}
\def\red#1{\textcolor{red}{#1}}

\begin{document}

\begin{enumerate}
    \item The total helicity during the reconnection event is not conserved. The presence of the mutual friction force introduces a dissipation into the normal fluid. Overall, by computing the helicity in the superfluid component, we confirmed this. We decided to omit this plot from the manuscript so as to not introduce further concepts of superfluid helicity to a paper whose narrative is normal fluid centric. We have addressed the referees concern by inserting an additional statement to clarify that the helicity during the reconnection event is not in fact conserved. 
    \item In the timescale of the simulation, we only observe one pair of the vortices which reconnect.  
    \item 
    \item 
    \item The value $t_0$ should in fact be $t_R$, the typo has been corrected.
    \item The authors agree with the comment of the referee that the current notation is not ideal. Instead, the figures have been changed to use the timescale in the horizontal axis of all time plots. Additionally to note, we have replaced the vertical axis label of Fig. 3b with $E_R/\tau_R$, simply a change of symbols to make clear the non-dimensionalisation of units.
    \item The figure has been updated with a power law of $k^{-3}$ 
    \item The time $t^*$ was introduced as the time at which we observe a sufficient decay of the helical force ratio, where the difference is around 5\% between the positive and negative modes and remains relatively stable afterwards. In order to make this clearer, we have added a sente nce in the text to explicity state this.
    \item The value of 0.1s comes from dimensionalising the values of $\tau=0.01$ for $T=1.9K$ and $\tau=0.005$ for $T=2.1K$, using the values of $\tilde{\tau}$ listed in the supplementary materials. 
    \item Incorrect reference corrected as noted by the reviewer.
\end{enumerate}
\end{document}

### 2025-04-25 revision/referee-response.tex
Completed almost all the points for referee 1

@@
-\documentclass[a4paper,10pt]{letter}
+\documentclass[a4paper,10pt]{article}
 \usepackage[margin=1in]{geometry}
 \usepackage{lipsum}
+\usepackage{graphicx, float}
 \usepackage{xcolor}
@@
 \begin{document}
+\section*{\centering Point-by-point response to referee comments}
+
+We thank the reviewers for taking the time to read over and give constructive feedback on our paper titled “\emph{Inverse energy transfer in three-dimensional quantum vortex flows}", submitted to PRL.
+Please see below the point-by-point response to the comments made by the reviewers.
+
+\subsection*{Referee 1}
 
@@
 We have addressed the referees concern by inserting an additional statement to clarify that the helicity during the reconnection event is not in fact conserved.
-    \item In the timescale of the simulation, we only observe one pair of the vortices which reconnect.  
-    \item 
+    \item The initial configuration is set up such that the superfluid velocity circlation in each half box has the opposite sign to the other half box, this is required to satisfy the periodic boundary conditions in the superfluid component.
+In the timescale of the simulation, we only observe one pair of the vortices which reconnect.
+During the reconnection, due to the large injection the helicity from the other pair is anyway negligible.
+The extended version of the simulation shows that the second reconnection injects positive helicity in the normal fluid, which then decays back to zero.
+Additionally, we computed the normal fluid helicity in each respective half box which also confirms this.
+We have added a sentence in the text to further clarify that the effect of the second vortex is negligent.
+\red{Add the new figure helicity\_normal\_fluid.pdf instead of Fig.2?}
+    \item We appreciate the referee’s careful reading of the manuscript and their observation regarding a perceived inconsistency between the plots of the energy spectrum and the energy flux.
+Firstly, we would like to note the following points that should be considered:
+    \begin{itemize}
+        \item The energy spectrum is on a logarithmic scale - the energy flux is on a linear scale.
+        \item The two plots are scaled differently: The energy spectrum is displayed in units of the code, while the energy flux is scaled by the energy flux at reconnection.
+        \item The energy spectrum and energy flux don't have the same units.
+    \end{itemize}
+    We would like to clarify that what may appear as an inconsistency arises from the omission of the injection spectrum in the figures presented in the paper, which shows that the injection is larger postreconnection for $T=1.9$K.
+
+    In the Navier-Stokes model that we employ, the rate of the energy spectrum is given by
+    \begin{equation}
+        \frac{\partial E(k)}{\partial t} = -\frac{\partial \Pi(k,t)}{\partial k} + D(k,t) + I(k,t)
+    \end{equation}
+    where $\Pi(k,t)$ represents the energy flux, $D(k,t)$ the dissipation spectrum and $I(k,t)$ the injectrum spectrum, resulting from the mutual fricition force.
+The injection spectrum was not included in the manuscript for brevity but is fully consistent with the presented data.
+
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.4\textwidth]{inj-spec.pdf}
+    \end{figure}
+
+    To clarify this point, we have included a supplementary figure showing the injection spectrum, which demonstrates how it complements the energy flux and spectrum, thereby resolving the apparent discrepancy.
+We have also updated Fig.3a to ensure consistency with the scaling used throughout the manuscript.
+    %We will also include a brief explanatory note in the revised manuscript to ensure this is clear to readers.
+
     \item 
@@
 \end{enumerate}
+
+\subsection*{Referee 2}
+
 \end{document}

### 2025-05-06 revision/referee-response.tex
Added Giorgios comment to referee B

@@
 \def\red#1{\textcolor{red}{#1}}
+\def\blue#1{\textcolor{blue}{#1}}
 
+\def\refcomment#1{\textbf{\blue{\emph{#1}}}\\}
 \begin{document}
@@
 
-\subsection*{Referee 1}
+\subsection*{Referee A}
 
-\begin{enumerate}
-    \item The total helicity during the reconnection event is not conserved.
+    \refcomment{1) p.1, right, "helicity, which is also an inviscid invariant": During
+    the reconnection in a finite temperature, the total helicity including
+    mutual friction force and normal fluid velocity is conserved? Normal
+    fluid is handled as a viscous flow. Please describe to readers.}
+
+    The total helicity during the reconnection event is not conserved.
 The presence of the mutual friction force introduces a dissipation into the normal fluid.
@@
 We have addressed the referees concern by inserting an additional statement to clarify that the helicity during the reconnection event is not in fact conserved.
-    \item The initial configuration is set up such that the superfluid velocity circlation in each half box has the opposite sign to the other half box, this is required to satisfy the periodic boundary conditions in the superfluid component.
+\\
+
+    \refcomment{2) p.3, right: Two pairs of initially orthogonal vortices are
+    considered in the present configuration. This paper reports that one
+    pair of vortices yield a negative helicity to the normal fluid
+    velocity. Please mention whether the other pair of vortices yields the
+    positive helicity or not. If both of them yield the negative helicity,
+    the initial setup already causes a symmetry breaking.}
+
+    The initial configuration is set up such that the superfluid velocity circlation in each half box has the opposite sign to the other half box, this is required to satisfy the periodic boundary conditions in the superfluid component.
 In the timescale of the simulation, we only observe one pair of the vortices which reconnect.
@@
 We have added a sentence in the text to further clarify that the effect of the second vortex is negligent.
-\red{Add the new figure helicity\_normal\_fluid.pdf instead of Fig.2?}
-    \item We appreciate the referee’s careful reading of the manuscript and their observation regarding a perceived inconsistency between the plots of the energy spectrum and the energy flux.
+\\
+
+    \red{\bfseries PZS: Add the new figure helicity\_normal\_fluid.pdf instead of Fig.2?}\\
+
+    \refcomment{3) Fig.3: In Fig.3(b), at $t = t_R$ the energy transfer at $T = 2.1K$ is
+    higher than that at $T = 1.9K$. However, the energy at $T = 2.1K$ is lower
+    than that at $T = 1.9K$. This is inconsistent. Please describe what
+    happens. Is it better to normalize the $E(k)$ by $E_R$?}
+
+    We appreciate the referee’s careful reading of the manuscript and their observation regarding a perceived inconsistency between the plots of the energy spectrum and the energy flux.
 Firstly, we would like to note the following points that should be considered:
@@
 We have also updated Fig.3a to ensure consistency with the scaling used throughout the manuscript.
+\\
     %We will also include a brief explanatory note in the revised manuscript to ensure this is clear to readers.
 
-    \item 
-    \item The value $t_0$ should in fact be $t_R$, the typo has been corrected.
-    \item The authors agree with the comment of the referee that the current notation is not ideal.
+    \refcomment{4) p.4, right, "This inverse energy transfer arises from the helical
+    character of the friction generated by the Kelvin waves released by
+    the reconnecting cusp": Is the inverse energy transfer due to the
+    Kelvin wave? This reviewer thought that it is due to the mutual
+    friction force being helical as described on the left of p.4.}
+
+    \refcomment{5) Figure caption in Fig.1, $(t - t_0)/\tau_R$: $t_0$ is $t_R$ ?}
+
+    The value $t_0$ should in fact be $t_R$, the typo has been corrected.\\
+
+    \refcomment{6) Horizontal label in Fig.2: $(t - t_R)/\tau_R$ would be better than $(t- \tau_R)E_R^{1/2}/L_R$ ?}
+
+    The authors agree with the comment of the referee that the current notation is not ideal.
 Instead, the figures have been changed to use the timescale in the horizontal axis of all time plots.
 Additionally to note, we have replaced the vertical axis label of Fig.
-3b with $E_R/\tau_R$, simply a change of symbols to make clear the non-dimensionalisation of units.
-    \item The figure has been updated with a power law of $k^{-3}$ 
-    \item The time $t^*$ was introduced as the time at which we observe a sufficient decay of the helical force ratio, where the difference is around 5\% between the positive and negative modes and remains relatively stable afterwards.
-In order to make this clearer, we have added a sente nce in the text to explicity state this.
-    \item The value of 0.1s comes from dimensionalising the values of $\tau=0.01$ for $T=1.9K$ and $\tau=0.005$ for $T=2.1K$, using the values of $\tilde{\tau}$ listed in the supplementary materials. 
-    \item Incorrect reference corrected as noted by the reviewer.
-\end{enumerate}
+3b with $E_R/\tau_R$, simply a change of symbols to make clear the non-dimensionalisation of units.\\
 
-\subsection*{Referee 2}
+    \refcomment{7) Figure 3(a): Is there a power law for the slope of $E(k)$?}
+
+    The figure has been updated with a power law of $k^{-3}$.\\
+
+    \refcomment{8) p.4, left, "From Fig. 4 we determine the non-dimensional
+    timescale...": Please describe the meaning of $t^*$.}
+
+    The time $t^*$ was introduced as the time at which we observe a sufficient decay of the helical force ratio, where the difference is around 5\% between the positive and negative modes and remains relatively stable afterwards.
+In order to make this clearer, we have added a sentence in the text to explicity state this.
+
+    \refcomment{9) p.4, left, "corresponding dimensionally to $\tau = 0.1$s for both
+    temperatures.": Please describe where "$\tau = 0.1$s" comes from or what
+    that means. Is the time when the helicity is changing?}
+
+    The value of 0.1s comes from dimensionalising the values of $\tau=0.01$ for $T=1.9K$ and $\tau=0.005$ for $T=2.1K$, using the values of $\tilde{\tau}$ listed in the supplementary materials. \\
+
+    \refcomment{10) Reference 53: B. ME should be M. E. Brachet. The year of 2026
+    should be 2017.}
+
+    Incorrect reference corrected as noted by the reviewer.\\
+
+\subsection*{Referee B}
+
+\refcomment{The authors’ main motivation, as far as I understand, is to propose a mechanism for the inverse energy cascade which is numerically observed in counterflow superfluid turbulence [Polanco and Krstulovic, PRL (2020)].}
+
+We want to clarify to the Referee that the purpose of our work is not at all to explain Polanco \& Krstulovic PRL 2020.
+Indeed, this article is only cited at the end of our manuscript, as a possible physical setting where the new physical phenomena described in our manuscript could be relevant, and it could be perhaps at the origin of the inverse cascade reported in that paper (that one of us co-authors).  To avoid possible confusion, we have reformulated the only paragraph in the conclusion where we cite Polanco\&Krstulovic.\\
+
+\refcomment{As recalled by the authors, inverse energy cascades show up when helicity symmetry is explicitely broken by external forcing as in [Plunian et al., JFM (2020)].
+Their claim, then, is that vortex reconnection events in superfluid turbulence will similarly break helicity symmetry and trigger, in this way, an inverse energy cascade in the flow.}
+
+Regarding this point, the referee understood the most important claim of our paper concerning the sign-defined helicity injections.
+We would like to highlight that we have consciously avoided talking about the inverse energy cascade, as we are well aware that our system is not turbulent.
+We have used the words “inverse energy transfers” instead.\\
+
+\refcomment{While the paper’s idea is interesting and worth pursuing, I believe the authors fail to provide even minimal evidence to support their case. Below, I address my main points.
+(i) First, the use of the word “turbulence” in the very first line (and used 16 times in other parts) of the manuscript is misleading: the flow studied by the authors is just a collision of vortex filaments.
+There is no turbulent flow at all here.
+It is all about a specific problem on superfluid flow instability.}
+
+As the Referee is certainly aware, vortex reconnections play an important role in turbulence.  We have never claimed that our system is turbulent, but we do think that our findings have a strong impact on quantum turbulence.  As the Referee might have noticed while counting how many times we used the word “turbulence”, we only used it in the introduction to motivate our work and to explain its relevance to a broad audience, and at the very end of our manuscript end to comment on its implications in the conclusions.
+Explaining cascades and then turbulence is necessary to understand the role of helicity on transfer towards large scales.
+We still believe that the use of the word turbulence is appropriate in our manuscript.
+We have nevertheless added a sentence in the introduction to remind the reader of the importance of vortex reconnections in turbulent flows and a comment in the conclusions about when our finding might be important for quantum turbulence.
+\\
+
+\refcomment{(ii) The work of Polanco and Krstulovic [PRL (2020)] gives strong indication that counterflow superfluid turbulence behaves (for large enough counterflow velocities) as a quasi two-dimensional syste and, therefore, an inverse energy cascade is expected to occur.
+Polanco and Krstulovic have also observed, by the way, the energy spectrum decay of the direct enstrophy cascade, in further qualitative agreement with the Batchelor-Kraichnan picture of 2D turbulence.}
+
+We do agree with the Referee’s understanding of Polanco\& Krstulovic main result. However, we do not understand why the Referee mentions it as they have not formulated any question or critcism.\\
+
+\red{\textbf{GK: Something better to say?}}
+
+\refcomment{(iii) The helicity production for an individual vortex reconnection event can be, of course, positive or negative.
+However, it is unlikley that this will be the case for the global helicity production associated to the complex vortex tangle of counterflow turbulence.
+I note that the previous results of [Plunian et al., JFM (2020)] refer to flow regimes where helicity symmetry is broken across all scales by the external forcing.}
+
+Indeed, the helicity injection produced by random vortex reconnections is not sign-defined, but by a single one, it is.  In isotropic turbulence, the helicity injection produced by vortex reconnection is certainly positive and negative.
+In the case when the system is highly anisotropic and the vortex density is sufficiently large, it is less clear if such a symmetry breaking could favour the production of helicity of one given sign.
+For this reason,  at the end of the conclusion, we mentioned counterflow turbulence as such an example and raised the question of whether the findings of Polanco\&Krstulovic could be ultimately related to the new mechanism reported in our Letter.  Providing a definitive answer to this open question is undoubtedly challenging and beyond the scope of our work.
+In the revised version, we have softened and reformulated the sentence referring to Polanco\&Krstulovic.\\
+
+\refcomment{(iv) The vortex reconnection mechanism for the inverse energy cascade would imply that energy would flow from very small scales (around the atomic sizes of the vortex cores) towards the integral length scales.
+That is not what is observed, as discussed by Polanco and Krstulovic [PRL (2020)].}
+
+We remind the Referee that Polanco\&Krstulovic used the HVBK model.
+This model does not describe quantised vortices, and the energy injection was made through an external term, which acting scale can be chosen arbitrarily.  The inverse cascade is triggered by the nonlinear term when the counterflow is strong enough, which leads to a strong anisotropy.
+In our coupled model, the normal fluid energy injection is produced by vortex reconnections, and it is indeed transferred towards large scales.  We remind the Referee that one needs to be careful while comparing HVBK and our couple model as they describe the physics at very different scales.  Again, by writing the sentence about Polanco\&Krstulovic, we simply raise a question that needs further investigation.\\
+
+\refcomment{(v) Finally, the “inverse energy cascade” detected by the authors may be unrelated to helicity production.
+One could just as easily argue that the perturbation/production of the standard component of the fluid through vortex reconnection is initially local- ized around the point where the filaments come into close contact.
+Subsequently, this normal component perturbation is strained by the specific background velocity configu- ration of the surrounding normal fluid.
+Helicity would not play any relevant dynamical role here.}
+
+The Referee has raised a good point.  In a recent paper [arXiv:2501.08309 ], three of us studied the wakes generated by moving superfluid vortices (with respect to the normal fluid).
+In this case, energy is transferred to small scales, discarding the scenario proposed by the Referee.\\
+
+\red{\textbf{GK: Shall we add a comment like this in the letter? GK:a figure in the suplemental? }}\\
+
+\refcomment{For the above reasons, I do not recommend the paper for publication in the PRL.}
+
+We hope that we have provided enough arguments to the Referee and they see now the impact of our Letter.
 

### 2025-05-21 revision/referee-response.tex
Updated figure and text

@@
     The initial configuration is set up such that the superfluid velocity circlation in each half box has the opposite sign to the other half box, this is required to satisfy the periodic boundary conditions in the superfluid component.
-In the timescale of the simulation, we only observe one pair of the vortices which reconnect.
+In the timescale of the simulation, we only observe one pair of the vortices which reconnect, as the reconnection events occur asynchronously.
 During the reconnection, due to the large injection the helicity from the other pair is anyway negligible.
@@
 We have added a sentence in the text to further clarify that the effect of the second vortex is negligent.
+
+    To illustrate this point, we have modified the text to explicity state thet reconnections occur asynchronously, and we have added some extra details to Fig.2 in the manuscript which highlight this visually.
 \\
-
-    \red{\bfseries PZS: Add the new figure helicity\_normal\_fluid.pdf instead of Fig.2?}\\
 
@@
     We appreciate the referee’s careful reading of the manuscript and their observation regarding a perceived inconsistency between the plots of the energy spectrum and the energy flux.
-Firstly, we would like to note the following points that should be considered:
-    \begin{itemize}
-        \item The energy spectrum is on a logarithmic scale - the energy flux is on a linear scale.
-        \item The two plots are scaled differently: The energy spectrum is displayed in units of the code, while the energy flux is scaled by the energy flux at reconnection.
-        \item The energy spectrum and energy flux don't have the same units.
-    \end{itemize}
+Firstly, we would like to note that the two plots are scaled differently: The energy spectrum is displayed in units of the code, while the energy flux is scaled by the energy flux at reconnection.\\
+
     We would like to clarify that what may appear as an inconsistency arises from the omission of the injection spectrum in the figures presented in the paper, which shows that the injection is larger postreconnection for $T=1.9$K.
-
 In the Navier-Stokes model that we employ, the rate of the energy spectrum is given by
@@
 
-As the Referee is certainly aware, vortex reconnections play an important role in turbulence.  We have never claimed that our system is turbulent, but we do think that our findings have a strong impact on quantum turbulence.  As the Referee might have noticed while counting how many times we used the word “turbulence”, we only used it in the introduction to motivate our work and to explain its relevance to a broad audience, and at the very end of our manuscript end to comment on its implications in the conclusions.
+As the Referee is certainly aware, vortex reconnections play an important role in turbulence.  We have never claimed that our system is turbulent, but we do think that our findings have a strong impact on quantum turbulence.  In the text, we have only referred to `turbuelnce' in the introduction to motivate our work and to explain its relevance to a broad audience, and at the very end to comment on its implications in the conclusions.
 Explaining cascades and then turbulence is necessary to understand the role of helicity on transfer towards large scales.
@@
 
-We hope that we have provided enough arguments to the Referee and they see now the impact of our Letter.
+\noindent We hope that we have provided enough arguments to the Referee and they see now the impact of our Letter.
 

### 2025-05-21 revision/referee-response.tex
Updated part 4) on referee A comments

@@
     We appreciate the referee’s careful reading of the manuscript and their observation regarding a perceived inconsistency between the plots of the energy spectrum and the energy flux.
-Firstly, we would like to note that the two plots are scaled differently: The energy spectrum is displayed in units of the code, while the energy flux is scaled by the energy flux at reconnection.\\
-
-    We would like to clarify that what may appear as an inconsistency arises from the omission of the injection spectrum in the figures presented in the paper, which shows that the injection is larger postreconnection for $T=1.9$K.
-In the Navier-Stokes model that we employ, the rate of the energy spectrum is given by
-    \begin{equation}
-        \frac{\partial E(k)}{\partial t} = -\frac{\partial \Pi(k,t)}{\partial k} + D(k,t) + I(k,t)
-    \end{equation}
-    where $\Pi(k,t)$ represents the energy flux, $D(k,t)$ the dissipation spectrum and $I(k,t)$ the injectrum spectrum, resulting from the mutual fricition force.
-The injection spectrum was not included in the manuscript for brevity but is fully consistent with the presented data.
-
-    \begin{figure}[H]
-        \centering
-        \includegraphics[width=0.4\textwidth]{inj-spec.pdf}
-    \end{figure}
-
-    To clarify this point, we have included a supplementary figure showing the injection spectrum, which demonstrates how it complements the energy flux and spectrum, thereby resolving the apparent discrepancy.
-We have also updated Fig.3a to ensure consistency with the scaling used throughout the manuscript.
+Firstly, we would like to note that the two plots are scaled differently: The energy spectrum is displayed in units of the code, while the energy flux is scaled by the energy flux at reconnection.
+The discreplency that can be seen is a result of the scalings used.
+In the Fig.3b the values are scaled at the reconnection values, which are different at both the temperatures.
+In dimensional units, we have verified that in fact that both the flux and the energy spectrum are larger for $T=1.9K$ than $T=2.1K$.
 \\
-    %We will also include a brief explanatory note in the revised manuscript to ensure this is clear to readers.
 
@@
     friction force being helical as described on the left of p.4.}
+
+    The referee is correct in thinking that the inverse energy transfer is due to the Kelvin waves.
+After the reconnection event, Kelvin waves are released by the reconnection cusp, which propagate outwards along both sides of the vortex.
+This in turn generates a helical profile in the normal fluid, however these Kelvin waves are damped at different rates.
+This in turn is what creates the imbalance of helicity.
 

### 2025-05-26 revision/referee-response.tex
Updated some parts of the text

@@
 
-As the Referee is certainly aware, vortex reconnections play an important role in turbulence.  We have never claimed that our system is turbulent, but we do think that our findings have a strong impact on quantum turbulence.  In the text, we have only referred to `turbuelnce' in the introduction to motivate our work and to explain its relevance to a broad audience, and at the very end to comment on its implications in the conclusions.
+As the Referee is certainly aware, vortex reconnections play an important role in turbulence.  We have never claimed that our system is turbulent, but we do think that our findings have a strong impact on quantum turbulence.  In the text, we have only referred to `turbulence' in the introduction to motivate our work and to explain its relevance to a broad audience, and at the very end to comment on its implications in the conclusions.
 Explaining cascades and then turbulence is necessary to understand the role of helicity on transfer towards large scales.
@@
 \refcomment{(v) Finally, the “inverse energy cascade” detected by the authors may be unrelated to helicity production.
-One could just as easily argue that the perturbation/production of the standard component of the fluid through vortex reconnection is initially local- ized around the point where the filaments come into close contact.
-Subsequently, this normal component perturbation is strained by the specific background velocity configu- ration of the surrounding normal fluid.
+One could just as easily argue that the perturbation/production of the standard component of the fluid through vortex reconnection is initially localized around the point where the filaments come into close contact.
+Subsequently, this normal component perturbation is strained by the specific background velocity configuration of the surrounding normal fluid.
 Helicity would not play any relevant dynamical role here.}

### 2025-06-13 revision/referee-response.tex
Lucas Updates #1

@@
 \usepackage{lipsum}
-\usepackage{graphicx, float}
+\usepackage{amsmath}
+\usepackage{graphicx}% Include figure files
+\usepackage{dcolumn}% Align table columns on decimal point
+\usepackage{bm}% bold math
+\usepackage{blindtext}
+\usepackage{float}
+\usepackage{caption}
+\usepackage{cleveref}
+\usepackage{subcaption}
 \usepackage{xcolor}
@@
 
-    The total helicity during the reconnection event is not conserved.
-The presence of the mutual friction force introduces a dissipation into the normal fluid.
-Overall, by computing the helicity in the superfluid component, we confirmed this.
+    The presence of the mutual friction force introduces an \red{additional source of} dissipation into the normal fluid.
+Overall, by \red{also} computing the helicity in the superfluid component, we observe that the total helicity during the reconnection event is not conserved.
 We decided to omit this plot from the manuscript so as to not introduce further concepts of superfluid helicity to a paper whose narrative is normal fluid centric.
-We have addressed the referees concern by inserting an additional statement to clarify that the helicity during the reconnection event is not in fact conserved.
+We have addressed the referee's concern by inserting an additional statement to clarify that the total helicity during the reconnection event is not conserved.
 \\
@@
     The initial configuration is set up such that the superfluid velocity circlation in each half box has the opposite sign to the other half box, this is required to satisfy the periodic boundary conditions in the superfluid component.
-In the timescale of the simulation, we only observe one pair of the vortices which reconnect, as the reconnection events occur asynchronously.
+In the timescale of the simulation, we only observe one pair of vortices which reconnects, as the reconnection events occur asynchronously.
 During the reconnection, due to the large injection the helicity from the other pair is anyway negligible.
@@
 Additionally, we computed the normal fluid helicity in each respective half box which also confirms this.
-We have added a sentence in the text to further clarify that the effect of the second vortex is negligent.
-
-    To illustrate this point, we have modified the text to explicity state thet reconnections occur asynchronously, and we have added some extra details to Fig.2 in the manuscript which highlight this visually.
+To illustrate this point, we have modified the text to explicity state thet reconnections occur asynchronously \red{and that we focus on the first one}, and we have added some extra details to Fig.2 in the manuscript which highlight this visually.
 \\
@@
 
-    We appreciate the referee’s careful reading of the manuscript and their observation regarding a perceived inconsistency between the plots of the energy spectrum and the energy flux.
-Firstly, we would like to note that the two plots are scaled differently: The energy spectrum is displayed in units of the code, while the energy flux is scaled by the energy flux at reconnection.
+    \red{We appreciate the referee’s careful reading of the manuscript and their observation regarding a perceived inconsistency between the plots of the energy and energy flux spectra.
+The perceived inconsistency arises from the scalings employed.
+While the energy spectrum is in arbitrary units (in particular, in the non dimensional units of the code), the energy flux is normalised with quantities at reconnection which depend on the temperature.
+If, in fact, we plot the spectra in dimensional units (Figures 1 attached) no inconsistency emerges.
+In the revised version of the code, following the referee's suggestion, we have scaled $E(k)$ by $E_R L_R$.}
+
+    \begin{figure}[h!]
+    \centering
+    \begin{subfigure}{0.49\textwidth}
+        \centering
+        \includegraphics*[width=\textwidth]{K_dimensional_clean.png}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}{0.49\textwidth}
+        \centering
+        \includegraphics*[width=\textwidth]{K_flux_dimensional_clean.png}
+        \caption{}
+    \end{subfigure}
+    \caption{\emph{(a):} Normal fluid kinetic energy spectrum $E(k)$ before 
+reconnection (dashed lines), at reconnection (solid lines) 
+and after reconnection (dotted lines) for $T=1.9K$ (red)
+and $T=2.1K$ (blue).\emph{(b):} Spectral normal fluid kinetic energy flux, $\Pi (k)$. 
+}
+\end{figure}
+%Firstly, we would like to note that the two plots are scaled differently: The energy spectrum is displayed in units of the code, while the energy flux is scaled by the energy flux at reconnection.
 The discreplency that can be seen is a result of the scalings used.
@@
 
-    The referee is correct in thinking that the inverse energy transfer is due to the Kelvin waves.
+    The mutual friction force is helical as a result of the presence of Kelvin wave packets released along the vortices after the relaxation of the cusp generated at reconnection.
+The two elements, helical character of the mutual friction force and the presence of Kelvin wave are hence inter-twinned.
+We have
+underlined this aspect in the revised version of the manuscript, by slightly modifying the sentence pointed by the referee.  
+%    The referee is correct in thinking that the inverse energy transfer is due to the Kelvin waves.
 After the reconnection event, Kelvin waves are released by the reconnection cusp, which propagate outwards along both sides of the vortex.
@@
 Additionally to note, we have replaced the vertical axis label of Fig.
-3b with $E_R/\tau_R$, simply a change of symbols to make clear the non-dimensionalisation of units.\\
+3b with $E_R \red{L_R}/\tau_R$, simply a change of symbols to make clear the non-dimensionalisation of units.\\
 
@@
 
+\newpage
 \subsection*{Referee B}
@@
 We want to clarify to the Referee that the purpose of our work is not at all to explain Polanco \& Krstulovic PRL 2020.
-Indeed, this article is only cited at the end of our manuscript, as a possible physical setting where the new physical phenomena described in our manuscript could be relevant, and it could be perhaps at the origin of the inverse cascade reported in that paper (that one of us co-authors).  To avoid possible confusion, we have reformulated the only paragraph in the conclusion where we cite Polanco\&Krstulovic.\\
+Indeed, this article is only cited at the end of our manuscript, as a possible physical setting where the new physical phenomena described in our manuscript could be relevant, and it could perhaps contribute to the origin of the inverse cascade reported in that paper (that one of us co-authors).  To avoid possible confusion, we have reformulated the only paragraph in the conclusion where we cite Polanco\&Krstulovic.\\
 
@@
 As the Referee is certainly aware, vortex reconnections play an important role in turbulence.  We have never claimed that our system is turbulent, but we do think that our findings have a strong impact on quantum turbulence.  In the text, we have only referred to `turbulence' in the introduction to motivate our work and to explain its relevance to a broad audience, and at the very end to comment on its implications in the conclusions.
-Explaining cascades and then turbulence is necessary to understand the role of helicity on transfer towards large scales.
+Explaining cascades, turbulence and invariants is necessary to understand the role of helicity on transfer towards large scales.
 We still believe that the use of the word turbulence is appropriate in our manuscript.
-We have nevertheless added a sentence in the introduction to remind the reader of the importance of vortex reconnections in turbulent flows and a comment in the conclusions about when our finding might be important for quantum turbulence.
+We have nevertheless added a sentence in the introduction to remind the reader of the importance of vortex reconnections in quantum turbulent flows and a comment in the conclusions about when our finding might be important for quantum turbulence.
 \\
@@
 
-We do agree with the Referee’s understanding of Polanco\& Krstulovic main result. However, we do not understand why the Referee mentions it as they have not formulated any question or critcism.\\
-
-\red{\textbf{GK: Something better to say?}}
+We do agree with the Referee’s understanding of Polanco\& Krstulovic main result. 
+%However, we do not understand why the Referee mentions it as they have not formulated any question or critcism.\\
+However, we would like again to point out that the purpose of our work is not at all to explain Polanco \& Krstulovic PRL 2020.
+Indeed, this article is only cited at the end of our manuscript, as a possible physical setting where the new physical phenomena described in our manuscript could be relevant.
+\red{The relevance of the large counterflow velocities in our mechanism for inverse energy transfer is in addition addressed in the next point.}
 
@@
 
-Indeed, the helicity injection produced by random vortex reconnections is not sign-defined, but by a single one, it is.  In isotropic turbulence, the helicity injection produced by vortex reconnection is certainly positive and negative.
-In the case when the system is highly anisotropic and the vortex density is sufficiently large, it is less clear if such a symmetry breaking could favour the production of helicity of one given sign.
+Indeed, the helicity injection produced by random vortex reconnections is not sign-defined, but the helicity injected by a single one, it is.  In isotropic turbulence, the helicity injection produced by vortex reconnections is certainly positive and negative \red{and the overall helicity injected
+might cancel out.
+However,} in the case where the system is highly anisotropic and the vortex density is sufficiently large \red{(as it is the case when counterflow velocities are large, where vortices tend to lie in a plane perpendicular to the heat flow)}, such symmetry breaking induced by the counterflow velocity could favour an asymmetry in the reconnection events triggering the overall production of helicity of one given sign.
 For this reason, at the end of the conclusion, we mentioned counterflow turbulence as such an example and raised the question of whether the findings of Polanco\&Krstulovic could be ultimately related to the new mechanism reported in our Letter.  Providing a definitive answer to this open question is undoubtedly challenging and beyond the scope of our work.
@@
 We remind the Referee that Polanco\&Krstulovic used the HVBK model.
-This model does not describe quantised vortices, and the energy injection was made through an external term, which acting scale can be chosen arbitrarily.  The inverse cascade is triggered by the nonlinear term when the counterflow is strong enough, which leads to a strong anisotropy.
-In our coupled model, the normal fluid energy injection is produced by vortex reconnections, and it is indeed transferred towards large scales.  We remind the Referee that one needs to be careful while comparing HVBK and our couple model as they describe the physics at very different scales.  Again, by writing the sentence about Polanco\&Krstulovic, we simply raise a question that needs further investigation.\\
+This model does not describe quantised vortices, and the energy injection was made through an external term, whose acting scale can be chosen arbitrarily.  The inverse cascade is triggered by the nonlinear term when the counterflow is strong enough, which leads to a strong anisotropy.
+In our coupled model, the normal fluid energy injection is produced by vortex reconnections, and it is indeed transferred towards large scales \red{by non-linear terms, at $k < 40$ (Fig.
+3b), \textit{i.e.} at scales much larger than the vortex core (we recall that our box is
+$1mm^3$)}. We remind the Referee that one needs to be careful while comparing HVBK and our coupled model as they describe the physics at very different scales.  Again, by writing the sentence about Polanco\&Krstulovic, we simply raise a question that needs further investigation.\\
 
@@
 
-The Referee has raised a good point.  In a recent paper [arXiv:2501.08309 ], three of us studied the wakes generated by moving superfluid vortices (with respect to the normal fluid).
-In this case, energy is transferred to small scales, discarding the scenario proposed by the Referee.\\
+The Referee raises a good point.  In a recent paper [arXiv:2501.08309], three of us studied the wakes generated by moving superfluid vortices (with respect to the normal fluid).
+In this case, however, energy results to be transferred to \textit{small} scales, discarding the scenario proposed by the Referee.
+\red{We attach here (Fig.
+2) the plot of the energy flux spectrum corresponding to the development of the wakes: all values are positive, showing a direct energy cascade.} \\
 
-\red{\textbf{GK: Shall we add a comment like this in the letter? GK:a figure in the suplemental? }}\\
+%
+\begin{figure}[h!]
+    \centering
+    \includegraphics*[width=0.48\textwidth]{flux_wakes.png}
+    \caption{Spectral normal fluid kinetic energy flux, $\Pi (k)$ for the wakes generated in the normal fluid, data from [arXiv:2501.08309].}.
+
+\end{figure}
 

### 2025-06-13 main_REV.tex
Added revised latex file

--- 2025-04-22 initial_submission.tex
@@
 times (from left to right)
-$(t-t_R)/\tau_R=-7.47\times10^{-2}$, $-3.09\times10^{-3}$, $8.79\times10^{-4}$ and $5.39\times10^{-3}$, where $\tau_R = E^{1/2}_R/ L_R$. The green
+$(t-t_R)/\tau_R=-7.47\times10^{-2}$, $-3.09\times10^{-3}$, $8.79\times10^{-4}$ and $5.39\times10^{-3}$, where $\tau_R = L_R/E^{1/2}_R$.
+The quantities $E_R$ and $L_R$ are the energy $E$ and integral length scales \red{$L$} of the normal fluid at reconnection time $t_R$.
+The green
 tubes represent the superfluid vortex lines (the tubes’ radii have been 
@@
 $\bom^2/\bom^2_{max}$. Note the Kelvin wave on the superfluid
-vortex at $(t-t_0)/\tau_R=8.79\times10^{-4}$ . In the bottom sequence, the red/blue volume
+vortex at $(t-t_R)/\tau_R=8.79\times10^{-4}$ . In the bottom sequence, the red/blue volume
 rendering at the same times represent scaled positive/negative normal fluid
@@
 to electrically conducting fluids (magneto-hydrodynamics turbulence
-\cite{canuto-dalsgaard-1998}) to quantum fluid
+\cite{canuto-dalsgaard-1998}) to quantum fluids
 (quantum turbulence \cite{barenghi-etal-2023,
@@
 cascade has been found also in
-three-dimensional turbulent BECs \cite{middleton-spencer2022}. Similarly to 2D classical turbulence, 
+three-dimensional turbulent BECs \cite{middleton-spencer2022}. 
+\red{
+In this forward energy cascade a fundamental role is played by the dynamics and interactions of quantum vortices,
+in particular by their reconnections, phenomena where  
+two vortex lines collide and recombine, exchanging heads and tails, 
+altering the overall topology of the flow
+\cite{koplik-levine-1993,bewley-etal-2008,rorai-etal-2016,serafini-etal-2017,galantucci-baggaley-parker-barenghi-2019,villoisUniversalNonuniversalAspects2017,villois2020irreversible}.
+Reconnections occur continuously in 3D quantum turbulence and are essential to
+the energy transfer towards small scales by engendering the the breakdown of coherent vortex structures
+and triggering the Kelvin-wave cascade \cite{vinen-2001}.
+}
+In 2D, similarly to classical turbulence, 
 an inverse energy cascade characterises turbulence in two-dimensional BECs, 
@@
 ($^4$He) as a result of vortex reconnections. 
-Reconnections occur continuously in turbulence: they take place when
-two vortex lines collide and recombine, exchanging heads and tails, 
-altering the overall topology of the flow
-\cite{koplik-levine-1993,bewley-etal-2008,rorai-etal-2016,serafini-etal-2017,galantucci-baggaley-parker-barenghi-2019,villoisUniversalNonuniversalAspects2017,villois2020irreversible}. 
+%\red{The onset and development of quantum turbulence is fundamentally driven by such reconnections, which facilitates energy transfer and the breakdown of coherent vortex structures.}  
+%Reconnections occur continuously in turbulence: they take place when
+%two vortex lines collide and recombine, exchanging heads and tails, 
+%altering the overall topology of the flow
+%\cite{koplik-levine-1993,bewley-etal-2008,rorai-etal-2016,serafini-etal-2017,galantucci-baggaley-parker-barenghi-2019,villoisUniversalNonuniversalAspects2017,villois2020irreversible}. 
 We show that the mutual friction force arising from the  
 vortex reconnection is chiral, injecting in the normal fluid prevalently 
-helicity of a given sign. Thus, as a consequence of vortex reconnections,
+helicity of a given sign 
+%\red{which is not globally conserved across the reconnection event}. 
+Thus, as a consequence of vortex reconnections,
 we observe an increase of the chiral imbalance of the quantum fluid, producing a transfer of kinetic energy from small to large scales, similarly to the phenomenology observed in 3D helical-decimated classical flows.
@@
 The vortex pairs are separated by the distance $D_{\ell}$; each vortex within each pair is initially at distance $d_{\ell}$ to the other vortex, such that $d_{\ell}\ll D_{\ell}$ to ensures that the dynamics in the vicinity of the reconnection is dominated by local interactions, and that the far-field contribution from the other vortex pair is negligible.
+\red{In our simulations, we consider only the vortex dynamics up to and shortly after the first reconnection, as the reconnection events occur asynchronously (see Fig.~\ref{fig:total-helicity}).
+Hence, all results reported and discussed herafter refer to the first reconnection.}.
 
@@
     \centering
-    \includegraphics*[width=0.48\textwidth]{helicity_total}
+    \includegraphics*[width=0.48\textwidth]{helicity_normal_fluid.pdf}
 \caption{Temporal evolution of the normal fluid helicity $\mathcal{H} = \int_{\mathcal{V}}H(\x)dV$ computed over the entire volume $\mathcal{V}$.
 For superfluid helium, it is proper to make the helicity dimensionless in terms of $\kappa^2$.
-The quantities $E_R$ and $L_R$ are the energy $E$ and integral length scales $L_0$ of the normal fluid at reconnection time $t_R$.}
+\red{The 3D rendering shows the asynchronous nature of the reconnections in the initial configuration, with the same colour scheme as in Fig.~\ref{fig:visualisation}.}}
 \label{fig:total-helicity}
@@
 and $T=2.1K$ (blue).\emph{(b):} Spectral normal fluid kinetic energy flux, $\Pi (k)$. It is normalised using the integral scale and the normal fluid energy at reconnection.
-\emph{Inset:} Post reconnection evolution of the integral length scale, $L_0$.
+\emph{Inset:} Post reconnection evolution of the integral length scale, $L$.
 Times and temperatures are labelled as in Fig.~\ref{fig:kinetic-energy}.}
@@
 % in Fig.~\ref{fig:visualisation}} \NOTE{GK: the figure shows small scale structures...}
-This behaviour is quantified by the evolution of the integral length scale $L_0$, defined as
+This behaviour is quantified by the evolution of the integral length scale $L$, defined as
 \begin{equation}
-    L_0 = \frac{\pi}{2 E}\int_0^{\infty}\frac{E(k)}{k}dk, %\Big/ \int_0^{\infty}\!\!E(k)dk.
+    L = \frac{\pi}{2 E}\int_0^{\infty}\frac{E(k)}{k}dk, %\Big/ \int_0^{\infty}\!\!E(k)dk.
 \end{equation}
 The inset of Fig.~\ref{fig:energy-flux} shows that
-$L_0$ indeed  increases steadily in the post-reconnection regime. Note that times have been normalised by the largest eddy-turnover-time at the reconnection event, evidencing  it fast evolution.
+$L$ indeed  increases steadily in the post-reconnection regime. Note that times have been normalised by the largest eddy-turnover-time at the reconnection event, evidencing  it fast evolution.
 
@@
 indicating that the flow is persistently chiral. We conclude that the reconnection triggers indeed a chiral imbalance.
-From Fig.~\ref{fig:mutual-friction-decomp} we determine the non-dimensional timescale $\tau = (t^*-t_R)E_R^{1/2}/L_R$
-during which the mutual friction force is chiral as a result of reconnections: $\tau \approx 0.01$ and $\tau \approx 0.005$
+\red{
+For the sake of completeness, it is worth noting that the total helicity of the flow (obtained by adding the superfluid helicity to that of the normal fluid $\mathcal{H}$) is not conserved.
+}
+From Fig.~\ref{fig:mutual-friction-decomp}, \red{ we consider a time $t^*$ after reconnection where the ratio $|f^+|^2/|f^-|^2$ has sufficiently decayed to a roughly 5\% difference and} we determine the non-dimensional timescale \red{$\tau = (t^*-t_R)/\tau_R$} during which the mutual friction force is chiral as a result of reconnections: $\tau \approx 0.01$ and $\tau \approx 0.005$
 for $T=1.9$K and $T=2.1$K, respectively, corresponding dimensionally to $\tau \approx 0.1$s for both temperatures. 
@@
 %The helical character of the mutual friction produces a chiral imbalance in the normal fluid, driving this inverse transfer, as previously observed in turbulent Navier-Stokes flows
-This inverse energy transfer arises from the helical character of the
-friction generated by the Kelvin waves released by the reconnecting
+This inverse energy transfer \red{is triggered by} the helical character of the
+mutual friction, \red{directly arising from the} Kelvin waves released by the reconnecting
 cusp, which produces a chiral imbalance in the normal fluid, as 
@@
 Our findings have profound implications for the nature of turbulence in 
-finite temperature superfluids. In circumstances where the vortex density 
+finite temperature superfluids, \red{where vortex reconnections play a key role}. 
+In circumstances where the vortex density 
 $\mathcal{L}$ is large and where the isotropy of the vortex tangle 
-is broken by external forcing, the chirality of the flow generated by the 
-frequent reconnections may be strong enough to induce an inverse energy 
+is broken by external forcing (for instance thermal counterflows \cite{vinen-1957a}), 
+the chirality of the flow generated by the 
+frequent \red{non-symmetrical} reconnections may be strong enough to induce an inverse energy 
 cascade \cite{notes_recon}.
@@
 %account the reconnection.
-The microscopic mechanism that we have described is probably what
-triggers the inverse energy cascade which is observed numerically in  
+The microscopic mechanism that we have described \red{may be relevant in triggering}
+the inverse energy cascade which is observed numerically in  
 large-scale simulations of counterflow turbulence at large heat fluxes \cite{polanco2020}, which is
@@
 
-% \bibliography{references}% Produces the bibliography via BibTeX
-
 %apsrev4-2.bst 2019-01-14 (MD) hand-edited version of apsrev4-1.bst
@@
 %Control: production of eprint (0) enabled
-\begin{thebibliography}{55}%
+\begin{thebibliography}{57}%
 \makeatletter
@@
   }\href {https://doi.org/10.1103/PhysRevB.102.134513} {\bibfield  {journal}
-  {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
+  {\bibinfo  {journal} {Physical Review B}\ }\textbf {\bibinfo {volume}
   {102}},\ \bibinfo {pages} {134513} (\bibinfo {year} {2020})}\BibitemShut
@@
   {https://doi.org/10.1103/PhysRevX.11.011053} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. X}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo
+  {journal} {Physical Review X}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo
   {pages} {011053} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
@@
   {2022})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Koplik}\ and\ \citenamefont
+  {Levine}(1993)}]{koplik-levine-1993}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Koplik}}\ and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Levine}},\ }\bibfield  {title} {\bibinfo {title} {Vortex reconnection in
+  superfluid helium},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {71}},\ \bibinfo
+  {pages} {1375} (\bibinfo {year} {1993})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bewley}\ \emph {et~al.}(2008)\citenamefont {Bewley},
+  \citenamefont {Paoletti}, \citenamefont {Sreenivasan},\ and\ \citenamefont
+  {Lathrop}}]{bewley-etal-2008}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~P.}\ \bibnamefont
+  {Bewley}}, \bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont
+  {Paoletti}}, \bibinfo {author} {\bibfnamefont {K.~R.}\ \bibnamefont
+  {Sreenivasan}},\ and\ \bibinfo {author} {\bibfnamefont {D.~P.}\ \bibnamefont
+  {Lathrop}},\ }\bibfield  {title} {\bibinfo {title} {Characterization of
+  reconnecting vortices in superfluid helium},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Proc. Natl. Acad. Sci. USA}\ }\textbf
+  {\bibinfo {volume} {105}},\ \bibinfo {pages} {13707} (\bibinfo {year}
+  {2008})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Rorai}\ \emph {et~al.}(2016)\citenamefont {Rorai},
+  \citenamefont {Skipper}, \citenamefont {Kerr},\ and\ \citenamefont
+  {Sreenivasan}}]{rorai-etal-2016}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+  {Rorai}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Skipper}},
+  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Kerr}},\ and\ \bibinfo
+  {author} {\bibfnamefont {K.}~\bibnamefont {Sreenivasan}},\ }\bibfield
+  {title} {\bibinfo {title} {Approach and separation of quantum vortices with
+  balanced cores},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {J. Fluid Mech.}\ }\textbf {\bibinfo {volume} {808}},\ \bibinfo {pages} {641}
+  (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Serafini}\ \emph {et~al.}(2017)\citenamefont
+  {Serafini}, \citenamefont {Galantucci}, \citenamefont {Iseni}, \citenamefont
+  {Bienaime}, \citenamefont {Bisset}, \citenamefont {Barenghi}, \citenamefont
+  {Dalfovo}, \citenamefont {Lamporesi},\ and\ \citenamefont
+  {Ferrari}}]{serafini-etal-2017}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Serafini}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Galantucci}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Iseni}},
+  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Bienaime}}, \bibinfo
+  {author} {\bibfnamefont {R.}~\bibnamefont {Bisset}}, \bibinfo {author}
+  {\bibfnamefont {C.~F.}\ \bibnamefont {Barenghi}}, \bibinfo {author}
+  {\bibfnamefont {F.}~\bibnamefont {Dalfovo}}, \bibinfo {author} {\bibfnamefont
+  {G.}~\bibnamefont {Lamporesi}},\ and\ \bibinfo {author} {\bibfnamefont
+  {G.}~\bibnamefont {Ferrari}},\ }\bibfield  {title} {\bibinfo {title} {Vortex
+  reconnections and rebounds in trapped atomic {{B}}ose-{{E}}instein
+  condensates},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. X}\ }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages} {021031}
+  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Galantucci}\ \emph {et~al.}(2019)\citenamefont
+  {Galantucci}, \citenamefont {Baggaley}, \citenamefont {Parker},\ and\
+  \citenamefont {Barenghi}}]{galantucci-baggaley-parker-barenghi-2019}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Galantucci}}, \bibinfo {author} {\bibfnamefont {A.~W.}\ \bibnamefont
+  {Baggaley}}, \bibinfo {author} {\bibfnamefont {N.~G.}\ \bibnamefont
+  {Parker}},\ and\ \bibinfo {author} {\bibfnamefont {C.~F.}\ \bibnamefont
+  {Barenghi}},\ }\bibfield  {title} {\bibinfo {title} {Crossover from
+  interaction to driven regimes in quantum vortex reconnections},\ }\href@noop
+  {} {\bibfield  {journal} {\bibinfo  {journal} {Proc. Natl. Acad. Sci. USA}\
+  }\textbf {\bibinfo {volume} {116}},\ \bibinfo {pages} {12204} (\bibinfo
+  {year} {2019})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Villois}\ \emph {et~al.}(2017)\citenamefont
+  {Villois}, \citenamefont {Proment},\ and\ \citenamefont
+  {Krstulovic}}]{villoisUniversalNonuniversalAspects2017}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Villois}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Proment}},\
+  and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Krstulovic}},\
+  }\bibfield  {title} {\bibinfo {title} {Universal and nonuniversal aspects of
+  vortex reconnections in superfluids},\ }\href
+  {https://doi.org/10.1103/PhysRevFluids.2.044701} {\bibfield  {journal}
+  {\bibinfo  {journal} {Physical Review Fluids}\ }\textbf {\bibinfo {volume}
+  {2}},\ \bibinfo {pages} {044701} (\bibinfo {year} {2017})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Villois}\ \emph {et~al.}(2020)\citenamefont
+  {Villois}, \citenamefont {Proment},\ and\ \citenamefont
+  {Krstulovic}}]{villois2020irreversible}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Villois}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Proment}},\
+  and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Krstulovic}},\
+  }\bibfield  {title} {\bibinfo {title} {Irreversible dynamics of vortex
+  reconnections in quantum fluids},\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {125}},\
+  \bibinfo {pages} {164501} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Vinen}(2001)}]{vinen-2001}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.~F.}\ \bibnamefont
+  {Vinen}},\ }\bibfield  {title} {\bibinfo {title} {Decay of superfluid
+  turbulence at a very low temperature: The radiation of sound from a kelvin
+  wave on a quantized vortex},\ }\href
+  {https://doi.org/10.1103/PhysRevB.64.134520} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {64}},\ \bibinfo
+  {pages} {134520} (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Bradley}\ and\ \citenamefont
@@
   {https://doi.org/10.1103/PhysRevLett.132.094002} {\bibfield  {journal}
-  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume}
+  {\bibinfo  {journal} {Physical Review Letters}\ }\textbf {\bibinfo {volume}
   {132}},\ \bibinfo {pages} {094002} (\bibinfo {year} {2024})}\BibitemShut
@@
   {https://doi.org/10.1103/PhysRevLett.130.133001} {\bibfield  {journal}
-  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume}
+  {\bibinfo  {journal} {Physical Review Letters}\ }\textbf {\bibinfo {volume}
   {130}},\ \bibinfo {pages} {133001} (\bibinfo {year} {2023})}\BibitemShut
@@
   {2020})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Koplik}\ and\ \citenamefont
-  {Levine}(1993)}]{koplik-levine-1993}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Koplik}}\ and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-  {Levine}},\ }\bibfield  {title} {\bibinfo {title} {Vortex reconnection in
-  superfluid helium},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {71}},\ \bibinfo
-  {pages} {1375} (\bibinfo {year} {1993})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Bewley}\ \emph {et~al.}(2008)\citenamefont {Bewley},
-  \citenamefont {Paoletti}, \citenamefont {Sreenivasan},\ and\ \citenamefont
-  {Lathrop}}]{bewley-etal-2008}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~P.}\ \bibnamefont
-  {Bewley}}, \bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont
-  {Paoletti}}, \bibinfo {author} {\bibfnamefont {K.~R.}\ \bibnamefont
-  {Sreenivasan}},\ and\ \bibinfo {author} {\bibfnamefont {D.~P.}\ \bibnamefont
-  {Lathrop}},\ }\bibfield  {title} {\bibinfo {title} {Characterization of
-  reconnecting vortices in superfluid helium},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Proc. Natl. Acad. Sci. USA}\ }\textbf
-  {\bibinfo {volume} {105}},\ \bibinfo {pages} {13707} (\bibinfo {year}
-  {2008})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Rorai}\ \emph {et~al.}(2016)\citenamefont {Rorai},
-  \citenamefont {Skipper}, \citenamefont {Kerr},\ and\ \citenamefont
-  {Sreenivasan}}]{rorai-etal-2016}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
-  {Rorai}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Skipper}},
-  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Kerr}},\ and\ \bibinfo
-  {author} {\bibfnamefont {K.}~\bibnamefont {Sreenivasan}},\ }\bibfield
-  {title} {\bibinfo {title} {Approach and separation of quantum vortices with
-  balanced cores},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {J. Fluid Mech.}\ }\textbf {\bibinfo {volume} {808}},\ \bibinfo {pages} {641}
-  (\bibinfo {year} {2016})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Serafini}\ \emph {et~al.}(2017)\citenamefont
-  {Serafini}, \citenamefont {Galantucci}, \citenamefont {Iseni}, \citenamefont
-  {Bienaime}, \citenamefont {Bisset}, \citenamefont {Barenghi}, \citenamefont
-  {Dalfovo}, \citenamefont {Lamporesi},\ and\ \citenamefont
-  {Ferrari}}]{serafini-etal-2017}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Serafini}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Galantucci}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Iseni}},
-  \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Bienaime}}, \bibinfo
-  {author} {\bibfnamefont {R.}~\bibnamefont {Bisset}}, \bibinfo {author}
-  {\bibfnamefont {C.~F.}\ \bibnamefont {Barenghi}}, \bibinfo {author}
-  {\bibfnamefont {F.}~\bibnamefont {Dalfovo}}, \bibinfo {author} {\bibfnamefont
-  {G.}~\bibnamefont {Lamporesi}},\ and\ \bibinfo {author} {\bibfnamefont
-  {G.}~\bibnamefont {Ferrari}},\ }\bibfield  {title} {\bibinfo {title} {Vortex
-  reconnections and rebounds in trapped atomic {{B}}ose-{{E}}instein
-  condensates},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {Phys. Rev. X}\ }\textbf {\bibinfo {volume} {7}},\ \bibinfo {pages} {021031}
-  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Galantucci}\ \emph {et~al.}(2019)\citenamefont
-  {Galantucci}, \citenamefont {Baggaley}, \citenamefont {Parker},\ and\
-  \citenamefont {Barenghi}}]{galantucci-baggaley-parker-barenghi-2019}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Galantucci}}, \bibinfo {author} {\bibfnamefont {A.~W.}\ \bibnamefont
-  {Baggaley}}, \bibinfo {author} {\bibfnamefont {N.~G.}\ \bibnamefont
-  {Parker}},\ and\ \bibinfo {author} {\bibfnamefont {C.~F.}\ \bibnamefont
-  {Barenghi}},\ }\bibfield  {title} {\bibinfo {title} {Crossover from
-  interaction to driven regimes in quantum vortex reconnections},\ }\href@noop
-  {} {\bibfield  {journal} {\bibinfo  {journal} {Proc. Natl. Acad. Sci. USA}\
-  }\textbf {\bibinfo {volume} {116}},\ \bibinfo {pages} {12204} (\bibinfo
-  {year} {2019})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Villois}\ \emph {et~al.}(2017)\citenamefont
-  {Villois}, \citenamefont {Proment},\ and\ \citenamefont
-  {Krstulovic}}]{villoisUniversalNonuniversalAspects2017}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Villois}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Proment}},\
-  and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Krstulovic}},\
-  }\bibfield  {title} {\bibinfo {title} {Universal and nonuniversal aspects of
-  vortex reconnections in superfluids},\ }\href
-  {https://doi.org/10.1103/PhysRevFluids.2.044701} {\bibfield  {journal}
-  {\bibinfo  {journal} {Phys. Rev. Fluids}\ }\textbf {\bibinfo {volume}
-  {2}},\ \bibinfo {pages} {044701} (\bibinfo {year} {2017})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Villois}\ \emph {et~al.}(2020)\citenamefont
-  {Villois}, \citenamefont {Proment},\ and\ \citenamefont
-  {Krstulovic}}]{villois2020irreversible}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Villois}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Proment}},\
-  and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Krstulovic}},\
-  }\bibfield  {title} {\bibinfo {title} {Irreversible dynamics of vortex
-  reconnections in quantum fluids},\ }\href@noop {} {\bibfield  {journal}
-  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {125}},\
-  \bibinfo {pages} {164501} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Galantucci}\ \emph {et~al.}(2020)\citenamefont
@@
   {24006} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Vinen}(1957)}]{vinen-1957a}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.~F.}\ \bibnamefont
+  {Vinen}},\ }\bibfield  {title} {\bibinfo {title} {Mutual friction in a heat
+  current in liquid helium ii. i. experiments on steady heat currents},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Proc. R. Soc.
+  London A}\ }\textbf {\bibinfo {volume} {240}},\ \bibinfo {pages} {114}
+  (\bibinfo {year} {1957})}\BibitemShut {NoStop}%
 \bibitem [{not()}]{notes_recon}%
@@
   {year} {2020})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Di~Leoni}\ \emph {et~al.}(2026)\citenamefont
-  {Di~Leoni}, \citenamefont {Mininni},\ and\ \citenamefont {ME}}]{dileoni2016}%
+\bibitem [{\citenamefont {Di~Leoni}\ \emph {et~al.}(2017)\citenamefont
+  {Di~Leoni}, \citenamefont {Mininni},\ and\ \citenamefont
+  {Brachet}}]{dileoni2016}%
   \BibitemOpen
@@
   {Di~Leoni}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Mininni}},\
-  and\ \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {ME}},\ }\bibfield
-  {title} {\bibinfo {title} {Dual cascade and dissipation mechanisms in helical
-  quantum turbulence},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume} {95}},\ \bibinfo
-  {pages} {053636} (\bibinfo {year} {2026})}\BibitemShut {NoStop}%
+  and\ \bibinfo {author} {\bibfnamefont {M.~E.}\ \bibnamefont {Brachet}},\
+  }\bibfield  {title} {\bibinfo {title} {Dual cascade and dissipation
+  mechanisms in helical quantum turbulence},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume}
+  {95}},\ \bibinfo {pages} {053636} (\bibinfo {year} {2017})}\BibitemShut
+  {NoStop}%
 \bibitem [{\citenamefont {Galantucci}\ \emph {et~al.}(2021)\citenamefont
@@
   reconnecting vortex links and knots},\ }\href@noop {} {\bibfield  {journal}
-  {\bibinfo  {journal} {Proc. Natl. Acad. Sci. Usa}\ }\textbf {\bibinfo {volume}
+  {\bibinfo  {journal} {Proc Natl Acad Sci Usa}\ }\textbf {\bibinfo {volume}
   {111}},\ \bibinfo {pages} {15350} (\bibinfo {year} {2014})}\BibitemShut
@@
 \end{thebibliography}%
+
+% \bibliography{references}
+
+    % \include{main_REV.bbl}
 \end{document}

### 2025-06-17 revision/referee-response-2.tex
Updated respones from Carlo

--- 2025-06-13 revision/referee-response.tex
@@
     The presence of the mutual friction force introduces an \red{additional source of} dissipation into the normal fluid.
-Overall, by \red{also} computing the helicity in the superfluid component, we observe that the total helicity during the reconnection event is not conserved.
-We decided to omit this plot from the manuscript so as to not introduce further concepts of superfluid helicity to a paper whose narrative is normal fluid centric.
-We have addressed the referee's concern by inserting an additional statement to clarify that the total helicity during the reconnection event is not conserved.
-\\
+By \red{also} computing the helicity in the superfluid component, we observe that during the reconnection event
+the total helicity \red{(sum of normal fluid helicity and superfluid helicity)} is not conserved. We omitted \red{the plot of the superfluid helicity}
+from the \red{original} manuscript so as to \red{avoid introducing}
+\red{the further concept} 
+of superfluid helicity to a paper whose narrative is \red{dedicated to the
+normal fluid}. \red{In the revised manuscript} we have addressed the 
+referee's concern by inserting \red{(in page 4)} an additional statement 
+to clarify that the total helicity during the reconnection event is 
+\textbf{not} conserved. \\
 
@@
 
-    The initial configuration is set up such that the superfluid velocity circlation in each half box has the opposite sign to the other half box, this is required to satisfy the periodic boundary conditions in the superfluid component.
-In the timescale of the simulation, we only observe one pair of vortices which reconnects, as the reconnection events occur asynchronously.
-During the reconnection, due to the large injection the helicity from the other pair is anyway negligible.
-The extended version of the simulation shows that the second reconnection injects positive helicity in the normal fluid, which then decays back to zero.
-Additionally, we computed the normal fluid helicity in each respective half box which also confirms this.
-To illustrate this point, we have modified the text to explicity state thet reconnections occur asynchronously \red{and that we focus on the first one}, and we have added some extra details to Fig.2 in the manuscript which highlight this visually.
-\\
+    The initial \red{vortex} configuration is set up such that the 
+superfluid velocity circulation in each half-box has the opposite sign to 
+the other half-box; \red{in this way, the superfluid velocity satisfies
+periodic boundary conditions over the entire computational 
+domain}.
+\red{It is important to appreciate that the two reconnection events do
+not occurr at the same time}. 
+In the timescale of the simulation \red{which we report in our manuscript}, 
+we only observe one pair of vortices which reconnects, as the reconnection 
+\red{of the other vortex pair occurs later, when the main impact of the first
+reconnection has vanished}.
+
+\red{We find that} during \red{this first reconnection}, the helicity contribution
+from the other vortex pair is negligible. \red{If we extend the
+simulation for a longer time and observe the second reconnection,
+we notice that} the second reconnection injects positive helicity 
+in the normal fluid, which then decays back to zero.
+
+Additionally, we computed the normal fluid helicity in each respective 
+half-box, confirming that the first reconnection injects negative
+helicity (computed only in its half-box), and, later, the second reconnection
+injects positive helicity (in its own half-box).
+
+To \red{better} illustrate this point, we have modified the text to 
+explicity state that \red{the two} reconnections occur 
+asynchronously, \red{that the second reconnection is required by the
+periodic boundary conditions of our computational domain}, 
+\red{and that, physically, we focus the discussion of our results
+on the first reconnection only}.
+We have also added some extra details to Fig.2 in the \red{revised}
+manuscript which highlight this \red{feature} visually. \\
 
@@
 
-    \red{We appreciate the referee’s careful reading of the manuscript and their observation regarding a perceived inconsistency between the plots of the energy and energy flux spectra.
-The perceived inconsistency arises from the scalings employed.
-While the energy spectrum is in arbitrary units (in particular, in the non dimensional units of the code), the energy flux is normalised with quantities at reconnection which depend on the temperature.
-If, in fact, we plot the spectra in dimensional units (Figures 1 attached) no inconsistency emerges.
-In the revised version of the code, following the referee's suggestion, we have scaled $E(k)$ by $E_R L_R$.}
+    We appreciate the referee’s careful reading of the manuscript and 
+their observation regarding a perceived inconsistency between the plots of 
+the energy and energy flux spectra. The perceived inconsistency arises 
+from the scalings employed. While the energy spectrum is in arbitrary 
+units (in particular, in the non dimensional units \red{used in} the code), 
+the energy flux is normalised with quantities which depend on the temperature. 
+If, in fact, we plot the spectra in dimensional units (Figures 1 attached),
+no inconsistency emerges. In the revised version of the code, following 
+the referee's suggestion, we have scaled $E(k)$ by $E_R L_R$.
 
@@
     The mutual friction force is helical as a result of the presence of Kelvin wave packets released along the vortices after the relaxation of the cusp generated at reconnection.
-The two elements, helical character of the mutual friction force and the presence of Kelvin wave are hence inter-twinned.
-We have
-underlined this aspect in the revised version of the manuscript, by slightly modifying the sentence pointed by the referee.  
+The two elements, \red{the} helical character
+of the mutual friction force and the presence of Kelvin wave, are 
+\red{therefore} inter-twinned. \red{In the revised manuscript} we have 
+underlined this aspect  by slightly modifying the sentence pointed \red{out}
+by the referee.  
 %    The referee is correct in thinking that the inverse energy transfer is due to the Kelvin waves.
@@
 
-    Incorrect reference corrected as noted by the reviewer.\\
+    The incorrect reference \red{noticed by the referee} has been
+    corrected.\\
 
@@
 
-We want to clarify to the Referee that the purpose of our work is not at all to explain Polanco \& Krstulovic PRL 2020.
-Indeed, this article is only cited at the end of our manuscript, as a possible physical setting where the new physical phenomena described in our manuscript could be relevant, and it could perhaps contribute to the origin of the inverse cascade reported in that paper (that one of us co-authors).  To avoid possible confusion, we have reformulated the only paragraph in the conclusion where we cite Polanco\&Krstulovic.\\
+We want to clarify to the Referee that the purpose of our work is not 
+at all to explain Polanco \& Krstulovic PRL 2020. Indeed, this
+ article is only cited at the end of our manuscript as a possible physical 
+setting where the new physical phenomena described in our manuscript 
+could be relevant, and it could perhaps contribute to the origin of 
+the inverse cascade reported in that paper (that one of us co-authors).  
+To avoid possible confusion, we have reformulated the only paragraph 
+in the conclusion where we cite Polanco\&Krstulovic.\\
 
@@
 
-Regarding this point, the referee understood the most important claim of our paper concerning the sign-defined helicity injections.
-We would like to highlight that we have consciously avoided talking about the inverse energy cascade, as we are well aware that our system is not turbulent.
-We have used the words “inverse energy transfers” instead.\\
+The referee \red{correctly} understood \red{that}
+the most important claim of our paper concerns the sign-defined helicity 
+injection. We would like to highlight that we have consciously avoided 
+talking about \red{an} {\it inverse energy cascade}, as we are well aware 
+that our system is not turbulent. We have used the words {\it inverse energy transfer} instead.\\
 
@@
 
+m
 As the Referee is certainly aware, vortex reconnections play an important role in turbulence.  We have never claimed that our system is turbulent, but we do think that our findings have a strong impact on quantum turbulence.  In the text, we have only referred to `turbulence' in the introduction to motivate our work and to explain its relevance to a broad audience, and at the very end to comment on its implications in the conclusions.
 Explaining cascades, turbulence and invariants is necessary to understand the role of helicity on transfer towards large scales.
-We still believe that the use of the word turbulence is appropriate in our manuscript.
-We have nevertheless added a sentence in the introduction to remind the reader of the importance of vortex reconnections in quantum turbulent flows and a comment in the conclusions about when our finding might be important for quantum turbulence.
-\\
+We still believe that the use of the word turbulence is
+appropriate in our manuscript \red{to put our results into the most 
+relevant context}.
+
+\red{Nevertheless, to take the referee's comment into account,}
+we have added a sentence in the introduction \red{(page 1)}
+to remind the reader of the importance of vortex reconnections 
+in quantum turbulent flows, and a comment in the conclusions 
+about when our finding might be important for quantum turbulence. \\
 
@@
 
-Indeed, the helicity injection produced by random vortex reconnections is not sign-defined, but the helicity injected by a single one, it is.  In isotropic turbulence, the helicity injection produced by vortex reconnections is certainly positive and negative \red{and the overall helicity injected
+Indeed, the helicity injection produced by random vortex reconnections 
+is not sign-defined, but the helicity injected by a single \red{reconnection}
+is.  In isotropic turbulence, the helicity injection produced by vortex reconnections is certainly positive and negative \red{and the overall helicity injected
 might cancel out.
@@
 We remind the Referee that Polanco\&Krstulovic used the HVBK model. 
-This model does not describe quantised vortices, and the energy injection was made through an external term, whose acting scale can be chosen arbitrarily.  The inverse cascade is triggered by the nonlinear term when the counterflow is strong enough, which leads to a strong anisotropy.
-In our coupled model, the normal fluid energy injection is produced by vortex reconnections, and it is indeed transferred towards large scales \red{by non-linear terms, at $k < 40$ (Fig.
-3b), \textit{i.e.} at scales much larger than the vortex core (we recall that our box is
-$1mm^3$)}. We remind the Referee that one needs to be careful while comparing HVBK and our coupled model as they describe the physics at very different scales.  Again, by writing the sentence about Polanco\&Krstulovic, we simply raise a question that needs further investigation.\\
+This model does not describe \red{individual} quantised vortices 
+\red{and their reconnections, but only a continuous density of vortex lines}, 
+\red{thus providing information only at lenght scales 
+much larger than the average vortex separation.} In the HVBK model
+the energy injection
+\red{occurs} via an external term whose acting scale can be chosen
+arbitrarily. 
+\red{In the HVBK model} the inverse cascade is triggered by the nonlinear 
+term when the counterflow 
+is strong enough, which leads to a strong anisotropy. 
+In our coupled model, the normal fluid energy injection is produced 
+by vortex reconnections, and it is indeed transferred towards large scales 
+\red{by non-linear terms, at $k < 40$ (Fig. 3b), \textit{i.e.} at scales much larger than the vortex core (we recall that our box is
+$1mm^3$)}. 
+We remind the Referee that one needs to be careful \red{when}
+comparing \red{the HVBK model} and our coupled model,
+as they describe the physics at very different scales.  Again, by writing the sentence about Polanco\&Krstulovic, we simply raise a question that needs further investigation.\\
 
@@
 
-\noindent We hope that we have provided enough arguments to the Referee and they see now the impact of our Letter.
+\noindent \red{We trust} that we have provided enough arguments 
+\red{for the Referee} to see now the impact of our Letter.
 

### 2025-06-17 main_REV.tex
Updated respones from Carlo

@@
 In three-dimensional (3D) classical fluids, turbulence 
-is characterised by a direct cascade: the
+is characterised by a direct (forward) cascade: the
 non-linear dissipationless transfer of kinetic energy from the scale of
@@
 \cite{koplik-levine-1993,bewley-etal-2008,rorai-etal-2016,serafini-etal-2017,galantucci-baggaley-parker-barenghi-2019,villoisUniversalNonuniversalAspects2017,villois2020irreversible}.
-Reconnections occur continuously in 3D quantum turbulence and are essential to
+Reconnections occur frequently in 3D quantum turbulence and are essential to
 the energy transfer towards small scales by engendering the the breakdown of coherent vortex structures
@@
 The vortex pairs are separated by the distance $D_{\ell}$; each vortex within each pair is initially at distance $d_{\ell}$ to the other vortex, such that $d_{\ell}\ll D_{\ell}$ to ensures that the dynamics in the vicinity of the reconnection is dominated by local interactions, and that the far-field contribution from the other vortex pair is negligible.
-\red{In our simulations, we consider only the vortex dynamics up to and shortly after the first reconnection, as the reconnection events occur asynchronously (see Fig.~\ref{fig:total-helicity}).
+\red{In our simulations, the reconnections of the two pairs of vortices occur at different times; here we consider only the vortex dynamics up to and shortly after the first reconnection (see Fig.~\ref{fig:total-helicity}).
 Hence, all results reported and discussed herafter refer to the first reconnection.}.
@@
 For superfluid helium, it is proper to make the helicity dimensionless in terms of $\kappa^2$.
-\red{The 3D rendering shows the asynchronous nature of the reconnections in the initial configuration, with the same colour scheme as in Fig.~\ref{fig:visualisation}.}}
+$\tau_R = L_R/E^{1/2}_R$.
+\red{The 3D rendering shows the asynchronous nature of the reconnections in the initial configuration, with the two reconnections occurring at different times; same colour scheme as in Fig.~\ref{fig:visualisation}.}}
 \label{fig:total-helicity}
@@
 %Control: production of eprint (0) enabled
-\begin{thebibliography}{57}%
+\begin{thebibliography}{55}%
 \makeatletter
@@
   }\href {https://doi.org/10.1103/PhysRevB.102.134513} {\bibfield  {journal}
-  {\bibinfo  {journal} {Physical Review B}\ }\textbf {\bibinfo {volume}
+  {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
   {102}},\ \bibinfo {pages} {134513} (\bibinfo {year} {2020})}\BibitemShut
@@
   {https://doi.org/10.1103/PhysRevX.11.011053} {\bibfield  {journal} {\bibinfo
-  {journal} {Physical Review X}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo
+  {journal} {Phys. Rev. X}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo
   {pages} {011053} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
@@
   {2022})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bradley}\ and\ \citenamefont
+  {Anderson}(2012)}]{bradley2012energy}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~S.}\ \bibnamefont
+  {Bradley}}\ and\ \bibinfo {author} {\bibfnamefont {B.~P.}\ \bibnamefont
+  {Anderson}},\ }\bibfield  {title} {\bibinfo {title} {Energy spectra of vortex
+  distributions in two-dimensional quantum turbulence},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. X}\ }\textbf {\bibinfo
+  {volume} {2}},\ \bibinfo {pages} {041001} (\bibinfo {year}
+  {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Reeves}\ \emph {et~al.}(2013)\citenamefont {Reeves},
+  \citenamefont {Billam}, \citenamefont {Anderson},\ and\ \citenamefont
+  {Bradley}}]{reeves2013}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~T.}\ \bibnamefont
+  {Reeves}}, \bibinfo {author} {\bibfnamefont {T.~P.}\ \bibnamefont {Billam}},
+  \bibinfo {author} {\bibfnamefont {B.~P.}\ \bibnamefont {Anderson}},\ and\
+  \bibinfo {author} {\bibfnamefont {A.~S.}\ \bibnamefont {Bradley}},\
+  }\bibfield  {title} {\bibinfo {title} {Inverse energy cascade in forced
+  two-dimensional quantum turbulence},\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {110}},\
+  \bibinfo {pages} {104501} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Simula}\ \emph {et~al.}(2014)\citenamefont {Simula},
+  \citenamefont {Davis},\ and\ \citenamefont
+  {Helmerson}}]{simula2014emergence}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Simula}}, \bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont {Davis}},\
+  and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Helmerson}},\
+  }\bibfield  {title} {\bibinfo {title} {Emergence of order from turbulence in
+  an isolated planar superfluid},\ }\href
+  {https://doi.org/10.1103/PhysRevLett.113.165302} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {113}},\
+  \bibinfo {pages} {165302} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Müller}\ and\ \citenamefont
+  {Krstulovic}(2024)}]{Muller_ExploringEquivalenceTwoDimensional_2024}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~P.}\ \bibnamefont
+  {Müller}}\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Krstulovic}},\ }\bibfield  {title} {\bibinfo {title} {Exploring the
+  {Equivalence} between {Two}-{Dimensional} {Classical} and {Quantum}
+  {Turbulence} through {Velocity} {Circulation} {Statistics}},\ }\href
+  {https://doi.org/10.1103/PhysRevLett.132.094002} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume}
+  {132}},\ \bibinfo {pages} {094002} (\bibinfo {year} {2024})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Johnstone}\ \emph {et~al.}(2019)\citenamefont
+  {Johnstone}, \citenamefont {Groszek}, \citenamefont {Starkey}, \citenamefont
+  {Billington}, \citenamefont {Simula},\ and\ \citenamefont
+  {Helmerson}}]{johnstone2019evolution}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~P.}\ \bibnamefont
+  {Johnstone}}, \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont
+  {Groszek}}, \bibinfo {author} {\bibfnamefont {P.~T.}\ \bibnamefont
+  {Starkey}}, \bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont
+  {Billington}}, \bibinfo {author} {\bibfnamefont {T.~P.}\ \bibnamefont
+  {Simula}},\ and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Helmerson}},\ }\bibfield  {title} {\bibinfo {title} {Evolution of
+  large-scale flow from turbulence in a two-dimensional superfluid},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf
+  {\bibinfo {volume} {364}},\ \bibinfo {pages} {1267} (\bibinfo {year}
+  {2019})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Gauthier}\ \emph {et~al.}(2019)\citenamefont
+  {Gauthier}, \citenamefont {Reeves}, \citenamefont {Yu}, \citenamefont
+  {Bradley}, \citenamefont {Baker}, \citenamefont {Bell}, \citenamefont
+  {Rubinsztein-Dunlop}, \citenamefont {Davis},\ and\ \citenamefont
+  {Neely}}]{gauthier2019giant}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Gauthier}}, \bibinfo {author} {\bibfnamefont {M.~T.}\ \bibnamefont
+  {Reeves}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Yu}}, \bibinfo
+  {author} {\bibfnamefont {A.~S.}\ \bibnamefont {Bradley}}, \bibinfo {author}
+  {\bibfnamefont {M.~A.}\ \bibnamefont {Baker}}, \bibinfo {author}
+  {\bibfnamefont {T.~A.}\ \bibnamefont {Bell}}, \bibinfo {author}
+  {\bibfnamefont {H.}~\bibnamefont {Rubinsztein-Dunlop}}, \bibinfo {author}
+  {\bibfnamefont {M.~J.}\ \bibnamefont {Davis}},\ and\ \bibinfo {author}
+  {\bibfnamefont {T.~W.}\ \bibnamefont {Neely}},\ }\bibfield  {title} {\bibinfo
+  {title} {Giant vortex clusters in a two-dimensional quantum fluid},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf
+  {\bibinfo {volume} {364}},\ \bibinfo {pages} {1264} (\bibinfo {year}
+  {2019})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Fj{\o}rtoft}(1953)}]{fjortoft1953changes}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {Fj{\o}rtoft}},\ }\bibfield  {title} {\bibinfo {title} {On the changes in the
+  spectral distribution of kinetic energy for twodimensional, nondivergent
+  flow},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Tellus}\
+  }\textbf {\bibinfo {volume} {5}},\ \bibinfo {pages} {225} (\bibinfo {year}
+  {1953})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Zhu}\ \emph {et~al.}(2023)\citenamefont {Zhu},
+  \citenamefont {Semisalov}, \citenamefont {Krstulovic},\ and\ \citenamefont
+  {Nazarenko}}]{Zhu_DirectInverseCascades_2023}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Zhu}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Semisalov}},
+  \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Krstulovic}},\ and\
+  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Nazarenko}},\ }\bibfield
+  {title} {\bibinfo {title} {Direct and {Inverse} {Cascades} in {Turbulent}
+  {Bose}-{Einstein} {Condensates}},\ }\href
+  {https://doi.org/10.1103/PhysRevLett.130.133001} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume}
+  {130}},\ \bibinfo {pages} {133001} (\bibinfo {year} {2023})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Moffatt}(1969)}]{moffatt1969}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.~K.}\ \bibnamefont
+  {Moffatt}},\ }\bibfield  {title} {\bibinfo {title} {The degree of knottedness
+  of tangled vortex lines},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {J. Fluid Mech.}\ }\textbf {\bibinfo {volume} {36}},\ \bibinfo
+  {pages} {7} (\bibinfo {year} {1969})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Biferale}\ \emph {et~al.}(2012)\citenamefont
+  {Biferale}, \citenamefont {Musacchio},\ and\ \citenamefont
+  {Toschi}}]{biferaleInverseEnergyCascade2012a}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Biferale}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Musacchio}},\ and\ \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Toschi}},\ }\bibfield  {title} {\bibinfo {title} {Inverse energy cascade in
+  three-dimensional isotropic turbulence},\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
+  {volume} {108}},\ \bibinfo {pages} {164501} (\bibinfo {year}
+  {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Biferale}\ \emph {et~al.}(2013)\citenamefont
+  {Biferale}, \citenamefont {Musacchio},\ and\ \citenamefont
+  {Toschi}}]{biferale-etal-2013}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Biferale}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Musacchio}},\ and\ \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Toschi}},\ }\bibfield  {title} {\bibinfo {title} {Split energy–helicity
+  cascades in three-dimensional homogeneous and isotropic turbulence},\ }\href
+  {https://doi.org/10.1017/jfm.2013.349} {\bibfield  {journal} {\bibinfo
+  {journal} {J. Fluid Mech.}\ }\textbf {\bibinfo {volume} {730}},\ \bibinfo
+  {pages} {309–327} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Sahoo}\ \emph {et~al.}(2017)\citenamefont {Sahoo},
+  \citenamefont {Alexakis},\ and\ \citenamefont {Biferale}}]{sahoo-etal-2017}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Sahoo}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Alexakis}},\
+  and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Biferale}},\
+  }\bibfield  {title} {\bibinfo {title} {Discontinuous transition from direct
+  to inverse cascade in three-dimensional turbulence},\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
+  {\bibinfo {volume} {118}},\ \bibinfo {pages} {164501} (\bibinfo {year}
+  {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Plunian}\ \emph {et~al.}(2020)\citenamefont
+  {Plunian}, \citenamefont {Teimurazov}, \citenamefont {Stepanov},\ and\
+  \citenamefont {Verma}}]{plunianInverseCascadeEnergy2020a}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Plunian}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Teimurazov}},
+  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Stepanov}},\ and\
+  \bibinfo {author} {\bibfnamefont {M.~K.}\ \bibnamefont {Verma}},\ }\bibfield
+  {title} {\bibinfo {title} {Inverse cascade of energy in helical turbulence},\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {J. Fluid Mech.}\
+  }\textbf {\bibinfo {volume} {895}},\ \bibinfo {pages} {A13} (\bibinfo {year}
+  {2020})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Koplik}\ and\ \citenamefont
@@
   {https://doi.org/10.1103/PhysRevFluids.2.044701} {\bibfield  {journal}
-  {\bibinfo  {journal} {Physical Review Fluids}\ }\textbf {\bibinfo {volume}
+  {\bibinfo  {journal} {Phys. Rev. Fluids}\ }\textbf {\bibinfo {volume}
   {2}},\ \bibinfo {pages} {044701} (\bibinfo {year} {2017})}\BibitemShut
@@
   \bibinfo {pages} {164501} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Vinen}(2001)}]{vinen-2001}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.~F.}\ \bibnamefont
-  {Vinen}},\ }\bibfield  {title} {\bibinfo {title} {Decay of superfluid
-  turbulence at a very low temperature: The radiation of sound from a kelvin
-  wave on a quantized vortex},\ }\href
-  {https://doi.org/10.1103/PhysRevB.64.134520} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {64}},\ \bibinfo
-  {pages} {134520} (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Bradley}\ and\ \citenamefont
-  {Anderson}(2012)}]{bradley2012energy}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~S.}\ \bibnamefont
-  {Bradley}}\ and\ \bibinfo {author} {\bibfnamefont {B.~P.}\ \bibnamefont
-  {Anderson}},\ }\bibfield  {title} {\bibinfo {title} {Energy spectra of vortex
-  distributions in two-dimensional quantum turbulence},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. X}\ }\textbf {\bibinfo
-  {volume} {2}},\ \bibinfo {pages} {041001} (\bibinfo {year}
-  {2012})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Reeves}\ \emph {et~al.}(2013)\citenamefont {Reeves},
-  \citenamefont {Billam}, \citenamefont {Anderson},\ and\ \citenamefont
-  {Bradley}}]{reeves2013}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~T.}\ \bibnamefont
-  {Reeves}}, \bibinfo {author} {\bibfnamefont {T.~P.}\ \bibnamefont {Billam}},
-  \bibinfo {author} {\bibfnamefont {B.~P.}\ \bibnamefont {Anderson}},\ and\
-  \bibinfo {author} {\bibfnamefont {A.~S.}\ \bibnamefont {Bradley}},\
-  }\bibfield  {title} {\bibinfo {title} {Inverse energy cascade in forced
-  two-dimensional quantum turbulence},\ }\href@noop {} {\bibfield  {journal}
-  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {110}},\
-  \bibinfo {pages} {104501} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Simula}\ \emph {et~al.}(2014)\citenamefont {Simula},
-  \citenamefont {Davis},\ and\ \citenamefont
-  {Helmerson}}]{simula2014emergence}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Simula}}, \bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont {Davis}},\
-  and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Helmerson}},\
-  }\bibfield  {title} {\bibinfo {title} {Emergence of order from turbulence in
-  an isolated planar superfluid},\ }\href
-  {https://doi.org/10.1103/PhysRevLett.113.165302} {\bibfield  {journal}
-  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {113}},\
-  \bibinfo {pages} {165302} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Müller}\ and\ \citenamefont
-  {Krstulovic}(2024)}]{Muller_ExploringEquivalenceTwoDimensional_2024}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~P.}\ \bibnamefont
-  {Müller}}\ and\ \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {Krstulovic}},\ }\bibfield  {title} {\bibinfo {title} {Exploring the
-  {Equivalence} between {Two}-{Dimensional} {Classical} and {Quantum}
-  {Turbulence} through {Velocity} {Circulation} {Statistics}},\ }\href
-  {https://doi.org/10.1103/PhysRevLett.132.094002} {\bibfield  {journal}
-  {\bibinfo  {journal} {Physical Review Letters}\ }\textbf {\bibinfo {volume}
-  {132}},\ \bibinfo {pages} {094002} (\bibinfo {year} {2024})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Johnstone}\ \emph {et~al.}(2019)\citenamefont
-  {Johnstone}, \citenamefont {Groszek}, \citenamefont {Starkey}, \citenamefont
-  {Billington}, \citenamefont {Simula},\ and\ \citenamefont
-  {Helmerson}}]{johnstone2019evolution}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~P.}\ \bibnamefont
-  {Johnstone}}, \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont
-  {Groszek}}, \bibinfo {author} {\bibfnamefont {P.~T.}\ \bibnamefont
-  {Starkey}}, \bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont
-  {Billington}}, \bibinfo {author} {\bibfnamefont {T.~P.}\ \bibnamefont
-  {Simula}},\ and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
-  {Helmerson}},\ }\bibfield  {title} {\bibinfo {title} {Evolution of
-  large-scale flow from turbulence in a two-dimensional superfluid},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf
-  {\bibinfo {volume} {364}},\ \bibinfo {pages} {1267} (\bibinfo {year}
-  {2019})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Gauthier}\ \emph {et~al.}(2019)\citenamefont
-  {Gauthier}, \citenamefont {Reeves}, \citenamefont {Yu}, \citenamefont
-  {Bradley}, \citenamefont {Baker}, \citenamefont {Bell}, \citenamefont
-  {Rubinsztein-Dunlop}, \citenamefont {Davis},\ and\ \citenamefont
-  {Neely}}]{gauthier2019giant}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {Gauthier}}, \bibinfo {author} {\bibfnamefont {M.~T.}\ \bibnamefont
-  {Reeves}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Yu}}, \bibinfo
-  {author} {\bibfnamefont {A.~S.}\ \bibnamefont {Bradley}}, \bibinfo {author}
-  {\bibfnamefont {M.~A.}\ \bibnamefont {Baker}}, \bibinfo {author}
-  {\bibfnamefont {T.~A.}\ \bibnamefont {Bell}}, \bibinfo {author}
-  {\bibfnamefont {H.}~\bibnamefont {Rubinsztein-Dunlop}}, \bibinfo {author}
-  {\bibfnamefont {M.~J.}\ \bibnamefont {Davis}},\ and\ \bibinfo {author}
-  {\bibfnamefont {T.~W.}\ \bibnamefont {Neely}},\ }\bibfield  {title} {\bibinfo
-  {title} {Giant vortex clusters in a two-dimensional quantum fluid},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Science}\ }\textbf
-  {\bibinfo {volume} {364}},\ \bibinfo {pages} {1264} (\bibinfo {year}
-  {2019})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Fj{\o}rtoft}(1953)}]{fjortoft1953changes}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
-  {Fj{\o}rtoft}},\ }\bibfield  {title} {\bibinfo {title} {On the changes in the
-  spectral distribution of kinetic energy for twodimensional, nondivergent
-  flow},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Tellus}\
-  }\textbf {\bibinfo {volume} {5}},\ \bibinfo {pages} {225} (\bibinfo {year}
-  {1953})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Zhu}\ \emph {et~al.}(2023)\citenamefont {Zhu},
-  \citenamefont {Semisalov}, \citenamefont {Krstulovic},\ and\ \citenamefont
-  {Nazarenko}}]{Zhu_DirectInverseCascades_2023}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
-  {Zhu}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Semisalov}},
-  \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Krstulovic}},\ and\
-  \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Nazarenko}},\ }\bibfield
-  {title} {\bibinfo {title} {Direct and {Inverse} {Cascades} in {Turbulent}
-  {Bose}-{Einstein} {Condensates}},\ }\href
-  {https://doi.org/10.1103/PhysRevLett.130.133001} {\bibfield  {journal}
-  {\bibinfo  {journal} {Physical Review Letters}\ }\textbf {\bibinfo {volume}
-  {130}},\ \bibinfo {pages} {133001} (\bibinfo {year} {2023})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Moffatt}(1969)}]{moffatt1969}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.~K.}\ \bibnamefont
-  {Moffatt}},\ }\bibfield  {title} {\bibinfo {title} {The degree of knottedness
-  of tangled vortex lines},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
-  {journal} {J. Fluid Mech.}\ }\textbf {\bibinfo {volume} {36}},\ \bibinfo
-  {pages} {7} (\bibinfo {year} {1969})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Biferale}\ \emph {et~al.}(2012)\citenamefont
-  {Biferale}, \citenamefont {Musacchio},\ and\ \citenamefont
-  {Toschi}}]{biferaleInverseEnergyCascade2012a}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Biferale}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Musacchio}},\ and\ \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {Toschi}},\ }\bibfield  {title} {\bibinfo {title} {Inverse energy cascade in
-  three-dimensional isotropic turbulence},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
-  {volume} {108}},\ \bibinfo {pages} {164501} (\bibinfo {year}
-  {2012})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Biferale}\ \emph {et~al.}(2013)\citenamefont
-  {Biferale}, \citenamefont {Musacchio},\ and\ \citenamefont
-  {Toschi}}]{biferale-etal-2013}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Biferale}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Musacchio}},\ and\ \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {Toschi}},\ }\bibfield  {title} {\bibinfo {title} {Split energy–helicity
-  cascades in three-dimensional homogeneous and isotropic turbulence},\ }\href
-  {https://doi.org/10.1017/jfm.2013.349} {\bibfield  {journal} {\bibinfo
-  {journal} {J. Fluid Mech.}\ }\textbf {\bibinfo {volume} {730}},\ \bibinfo
-  {pages} {309–327} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Sahoo}\ \emph {et~al.}(2017)\citenamefont {Sahoo},
-  \citenamefont {Alexakis},\ and\ \citenamefont {Biferale}}]{sahoo-etal-2017}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {Sahoo}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Alexakis}},\
-  and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Biferale}},\
-  }\bibfield  {title} {\bibinfo {title} {Discontinuous transition from direct
-  to inverse cascade in three-dimensional turbulence},\ }\href@noop {}
-  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
-  {\bibinfo {volume} {118}},\ \bibinfo {pages} {164501} (\bibinfo {year}
-  {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Plunian}\ \emph {et~al.}(2020)\citenamefont
-  {Plunian}, \citenamefont {Teimurazov}, \citenamefont {Stepanov},\ and\
-  \citenamefont {Verma}}]{plunianInverseCascadeEnergy2020a}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {Plunian}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Teimurazov}},
-  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Stepanov}},\ and\
-  \bibinfo {author} {\bibfnamefont {M.~K.}\ \bibnamefont {Verma}},\ }\bibfield
-  {title} {\bibinfo {title} {Inverse cascade of energy in helical turbulence},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {J. Fluid Mech.}\
-  }\textbf {\bibinfo {volume} {895}},\ \bibinfo {pages} {A13} (\bibinfo {year}
-  {2020})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Galantucci}\ \emph {et~al.}(2020)\citenamefont
@@
   {24006} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Vinen}(1957)}]{vinen-1957a}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.~F.}\ \bibnamefont
-  {Vinen}},\ }\bibfield  {title} {\bibinfo {title} {Mutual friction in a heat
-  current in liquid helium ii. i. experiments on steady heat currents},\
-  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Proc. R. Soc.
-  London A}\ }\textbf {\bibinfo {volume} {240}},\ \bibinfo {pages} {114}
-  (\bibinfo {year} {1957})}\BibitemShut {NoStop}%
 \bibitem [{not()}]{notes_recon}%
@@
   {year} {2020})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Di~Leoni}\ \emph {et~al.}(2017)\citenamefont
-  {Di~Leoni}, \citenamefont {Mininni},\ and\ \citenamefont
-  {Brachet}}]{dileoni2016}%
+\bibitem [{\citenamefont {Di~Leoni}\ \emph {et~al.}(2026)\citenamefont
+  {Di~Leoni}, \citenamefont {Mininni},\ and\ \citenamefont {ME}}]{dileoni2016}%
   \BibitemOpen
@@
   {Di~Leoni}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Mininni}},\
-  and\ \bibinfo {author} {\bibfnamefont {M.~E.}\ \bibnamefont {Brachet}},\
-  }\bibfield  {title} {\bibinfo {title} {Dual cascade and dissipation
-  mechanisms in helical quantum turbulence},\ }\href@noop {} {\bibfield
-  {journal} {\bibinfo  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume}
-  {95}},\ \bibinfo {pages} {053636} (\bibinfo {year} {2017})}\BibitemShut
-  {NoStop}%
+  and\ \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {ME}},\ }\bibfield
+  {title} {\bibinfo {title} {Dual cascade and dissipation mechanisms in helical
+  quantum turbulence},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume} {95}},\ \bibinfo
+  {pages} {053636} (\bibinfo {year} {2026})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Galantucci}\ \emph {et~al.}(2021)\citenamefont
@@
   reconnecting vortex links and knots},\ }\href@noop {} {\bibfield  {journal}
-  {\bibinfo  {journal} {Proc Natl Acad Sci Usa}\ }\textbf {\bibinfo {volume}
+  {\bibinfo  {journal} {Proc. Natl. Acad. Sci. Usa}\ }\textbf {\bibinfo {volume}
   {111}},\ \bibinfo {pages} {15350} (\bibinfo {year} {2014})}\BibitemShut
@@
 
-% \bibliography{references}
-
-    % \include{main_REV.bbl}
+%\bibliography{references}
+
+    % \include{main.bbl}
 \end{document}

### 2025-06-19 revision/referee-response-2.tex
Updated referee response and revised tex files

@@
 
-    The initial \red{vortex} configuration is set up such that the 
-superfluid velocity circulation in each half-box has the opposite sign to 
-the other half-box; \red{in this way, the superfluid velocity satisfies
-periodic boundary conditions over the entire computational 
-domain}.
-\red{It is important to appreciate that the two reconnection events do
-not occurr at the same time}. 
-In the timescale of the simulation \red{which we report in our manuscript}, 
-we only observe one pair of vortices which reconnects, as the reconnection 
-\red{of the other vortex pair occurs later, when the main impact of the first
-reconnection has vanished}.
+    In our manuscript, we indeed only describe the results referring to one pair of reconnecting 
+    vortices. We confirm that the helicity injected by the other pair is indeed positive.
 
-\red{We find that} during \red{this first reconnection}, the helicity contribution
-from the other vortex pair is negligible. \red{If we extend the
-simulation for a longer time and observe the second reconnection,
-we notice that} the second reconnection injects positive helicity 
-in the normal fluid, which then decays back to zero.
+%    The initial \red{vortex} configuration is set up such that the 
+%superfluid velocity circulation in each half-box has the opposite sign to 
+%the other half-box; \red{in this way, the superfluid velocity satisfies
+%periodic boundary conditions over the entire computational 
+%domain}.
+%\red{It is important to appreciate that the two reconnection events do
+%not occurr at the same time}. 
+%In the timescale of the simulation \red{which we report in our manuscript}, 
+%we only observe one pair of vortices which reconnects, as the reconnection 
+%\red{of the other vortex pair occurs later, when the main impact of the first
+%reconnection has vanished}.
 
-Additionally, we computed the normal fluid helicity in each respective 
-half-box, confirming that the first reconnection injects negative
-helicity (computed only in its half-box), and, later, the second reconnection
-injects positive helicity (in its own half-box).
+%\red{We find that} during \red{this first reconnection}, the helicity contribution
+%from the other vortex pair is negligible. \red{If we extend the
+%simulation for a longer time and observe the second reconnection,
+%we notice that} the second reconnection injects positive helicity 
+%in the normal fluid, which then decays back to zero.
 
-To \red{better} illustrate this point, we have modified the text to 
-explicity state that \red{the two} reconnections occur 
-asynchronously, \red{that the second reconnection is required by the
-periodic boundary conditions of our computational domain}, 
-\red{and that, physically, we focus the discussion of our results
-on the first reconnection only}.
-We have also added some extra details to Fig.2 in the \red{revised}
-manuscript which highlight this \red{feature} visually. \\
+%Additionally, we computed the normal fluid helicity in each respective 
+%half-box, confirming that the first reconnection injects negative
+%helicity (computed only in its half-box), and, later, the second reconnection
+%injects positive helicity (in its own half-box).
+
+%To \red{better} illustrate this point, we have modified the text to 
+%explicity state that \red{the two} reconnections occur 
+%asynchronously, \red{that the second reconnection is required by the
+%periodic boundary conditions of our computational domain}, 
+%\red{and that, physically, we focus the discussion of our results
+%on the first reconnection only}.
+%We have also added some extra details to Fig.2 in the \red{revised}
+%manuscript which highlight this \red{feature} visually. \\
 

### 2025-06-19 main_REV.tex
Updated referee response and revised tex files

--- 2025-06-13 main_REV.tex
@@
 % WE ADD REFERENCE TO OUR FIRST PAPER LATER IN THE TEXT
-%Punctuated energy injection resulting from the violent nature of vortex reconnections \cite{stasiak2024quantum} pave the way for an imbalance of chirality by multi-scale energy injection.
+%Punctuated energy injection resulting from the violent nature of vortex reconnections \cite{stasiak2025experimental} pave the way for an imbalance of chirality by multi-scale energy injection.
 %
@@
 The vortex pairs are separated by the distance $D_{\ell}$; each vortex within each pair is initially at distance $d_{\ell}$ to the other vortex, such that $d_{\ell}\ll D_{\ell}$ to ensures that the dynamics in the vicinity of the reconnection is dominated by local interactions, and that the far-field contribution from the other vortex pair is negligible.
-\red{In our simulations, we consider only the vortex dynamics up to and shortly after the first reconnection, as the reconnection events occur asynchronously (see Fig.~\ref{fig:total-helicity}).
+\red{All results reported hereafter refer only to the reconnection of one pair of vortices.} 
+%\red{In our simulations, the reconnections of the two pairs of vortices occur at different times; here we consider only the vortex dynamics up to and shortly after the first reconnection (see Fig.~\ref{fig:total-helicity}).
 Hence, all results reported and discussed herafter refer to the first reconnection.}.
@@
 Such structures are the signature of the violent irreversible energy transfers in vortex reconnections
-\cite{stasiak2024quantum}.
+\cite{stasiak2025experimental}.
 The second row shows the rendering of the local helicity $H(\x)=\v_n\cdot\bom$, where we observe a clear local helicity production, with an abrupt change of sign due to the rearrangement of the vortex topology.
@@
     \centering
-    \includegraphics*[width=0.48\textwidth]{helicity_normal_fluid.pdf}
+    \includegraphics*[width=0.48\textwidth]{helicity_total.pdf}
 \caption{Temporal evolution of the normal fluid helicity $\mathcal{H} = \int_{\mathcal{V}}H(\x)dV$ computed over the entire volume $\mathcal{V}$.
 For superfluid helium, it is proper to make the helicity dimensionless in terms of $\kappa^2$.
-\red{The 3D rendering shows the asynchronous nature of the reconnections in the initial configuration, with the same colour scheme as in Fig.~\ref{fig:visualisation}.}}
+$\tau_R = L_R/E^{1/2}_R$.
+%\red{The 3D rendering shows the asynchronous nature of the reconnections in the initial configuration, with the two reconnections occurring at different times; same colour scheme as in Fig.~\ref{fig:visualisation}.}
+}
 \label{fig:total-helicity}
@@
 In superfluid turbulence, the timescale between two consecutive reconnections can be smaller than $\tau$ provided that the
-vortex line density $\mathcal{L}$ (length of vortices per unit volume) is larger than $10^8 \text{m}^{-2}$ \cite{stasiak2024quantum,barenghi2004},
+vortex line density $\mathcal{L}$ (length of vortices per unit volume) is larger than $10^8 \text{m}^{-2}$ \cite{stasiak2025experimental,barenghi2004},
 a condition which is easily met in superfluid helium experiments \cite{roche2007,Babuin2014}.
@@
 ($T\gtrsim 1.5$K) not only injects punctuated
-energy in the normal fluid \cite{stasiak2024quantum}, but also triggers in the normal fluid
+energy in the normal fluid \cite{stasiak2025experimental}, but also triggers in the normal fluid
 a transfer of kinetic energy towards the large scales. 
@@
 $\mathcal{L}$ is large and where the isotropy of the vortex tangle 
-is broken by external forcing (for instance thermal counterflows \cite{vinen-1957a}), 
+is broken by external forcing (for instance thermal counterflows~\cite{vinen-1957a}), 
 the chirality of the flow generated by the 
 frequent \red{non-symmetrical} reconnections may be strong enough to induce an inverse energy 
-cascade \cite{notes_recon}.
+cascade~\cite{notes_recon}.
 %The asymmetry of the reconnecting vortex configurations is a key element; 
@@
   \end{acknowledgments}
+
+% \bibliography{references}
 
@@
   {NoStop}%
-\bibitem [{\citenamefont {Stasiak}\ \emph {et~al.}(2024)\citenamefont
+\bibitem [{\citenamefont {Stasiak}\ \emph {et~al.}(2025)\citenamefont
   {Stasiak}, \citenamefont {Xing}, \citenamefont {Alihosseini}, \citenamefont
   {Barenghi}, \citenamefont {Baggaley}, \citenamefont {Guo}, \citenamefont
-  {Galantucci},\ and\ \citenamefont {Krstulovic}}]{stasiak2024quantum}%
+  {Galantucci},\ and\ \citenamefont {Krstulovic}}]{stasiak2025experimental}%
   \BibitemOpen
@@
   {author} {\bibfnamefont {C.~F.}\ \bibnamefont {Barenghi}}, \bibinfo {author}
-  {\bibfnamefont {A.~W.}\ \bibnamefont {Baggaley}}, \bibinfo {author}
+  {\bibfnamefont {A.}~\bibnamefont {Baggaley}}, \bibinfo {author}
   {\bibfnamefont {W.}~\bibnamefont {Guo}}, \bibinfo {author} {\bibfnamefont
@@
   reconnections},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
-  {arXiv}\ ,\ \bibinfo {pages} {2411.08942}} (\bibinfo {year}
-  {2024})}\BibitemShut {NoStop}%
+  {Proc. Nat. Acad. of Sci.}\ }\textbf {\bibinfo {volume} {122}},\ \bibinfo
+  {pages} {e2426064122} (\bibinfo {year} {2025})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Waleffe}(1992)}]{waleffe-1992}%
@@
 
-% \bibliography{references}
-
-    % \include{main_REV.bbl}
 \end{document}

### 2025-06-24 revision/referee-response-2.tex
GK done

@@
 
-m
-As the Referee is certainly aware, vortex reconnections play an important role in turbulence.  We have never claimed that our system is turbulent, but we do think that our findings have a strong impact on quantum turbulence.  In the text, we have only referred to `turbulence' in the introduction to motivate our work and to explain its relevance to a broad audience, and at the very end to comment on its implications in the conclusions.
+As the Referee is certainly aware, vortex reconnections play an important role in turbulence.We have never claimed that our system is turbulent, but we do think that our findings have a strong impact on quantum turbulence.
+In the text, we have only referred to `turbulence' in the introduction to motivate our work and to explain its relevance to a broad audience, and at the very end to comment on its implications in the conclusions.
 Explaining cascades, turbulence and invariants is necessary to understand the role of helicity on transfer towards large scales.
@@
 
-\noindent \red{We trust} that we have provided enough arguments 
-\red{for the Referee} to see now the impact of our Letter.
+\noindent \red{We trust} that we have clarified to the Referee the goal and main results of our Letter, and at the same time, provided enough arguments to emphasize the impact of our Letter.
 

### 2025-06-25 revision/cover_letter_REV.tex
Added editor letter for the revision

\documentclass[a4paper,10pt]{letter}
\usepackage[margin=1in]{geometry}
\usepackage{lipsum}
\usepackage{xcolor}
\def\red#1{\textcolor{black}{#1}}

\begin{document}

% Sender Information
\begin{flushright}
    \begin{tabular}{l}
        \textbf{Piotr Stasiak} \\
        School of Mathematics, Statistics and Physics\\
        Newcastle University \\
        Newcastle  upon Tyne \\
        p.stasiak@newcastle.ac.uk \\
        \today
    \end{tabular}
\end{flushright}

\vspace{1cm}

% Recipient Information
The Editors,\\
Physical Review Letters\\
APS\\

\vspace{1cm}

Dear Editor,

\vspace{0.5cm}

We would like to thank the referees for taking the time to review our manuscript entitled \emph{``Inverse energy transfer in three-dimensional quantum vortex flows''}. We have addressed all of the comments of the referees.

For Referee A, we have added further details in the manuscript to address the major concerns, particularly regarding the conservation and symmetry of the normal fluid helicity, and the relevance of Kelvin waves in the creation of unbalanced chiral modes.

For Referee B, we believe that the referee has missed the main focus of the paper, which was to provide an explanation of the inverse energy transfer due to vortex reconnections in terms of a chiral imbalance of helical modes, and not to explain [Krstulovic\&Polanco PRL 2020], of which Krstulovic is a collaborator and co-author of this work. The paper by Krstulovic\&Polanco, fundamentally differs from ours in terms of the model used and the analysis, and we cite this work at the very end of our manuscript as a possible connection, and not as an explanation as the referees comments seem to suggest. We hope that we have made our comments sufficiently clear to the referee for the relevance of our work.

\vspace{0.5cm}

On behalf of the authors,

\vspace{1cm}

\textbf{Piotr Stasiak}

\end{document}

### 2025-06-25 revision/cover_letter_REV.tex
Updated letter

@@
 % Sender Information
-\begin{flushright}
-    \begin{tabular}{l}
-        \textbf{Piotr Stasiak} \\
-        School of Mathematics, Statistics and Physics\\
-        Newcastle University \\
-        Newcastle  upon Tyne \\
-        p.stasiak@newcastle.ac.uk \\
-        \today
-    \end{tabular}
-\end{flushright}
+% \begin{flushright}
+%     \begin{tabular}{l}
+%         \textbf{Piotr Stasiak} \\
+%         School of Mathematics, Statistics and Physics\\
+%         Newcastle University \\
+%         Newcastle  upon Tyne \\
+%         p.stasiak@newcastle.ac.uk \\
+%         \today
+%     \end{tabular}
+% \end{flushright}
 
-\vspace{1cm}
+% \vspace{1cm}
 
@@
 
-For Referee B, we believe that the referee has missed the main focus of the paper, which was to provide an explanation of the inverse energy transfer due to vortex reconnections in terms of a chiral imbalance of helical modes, and not to explain [Krstulovic\&Polanco PRL 2020], of which Krstulovic is a collaborator and co-author of this work.
-The paper by Krstulovic\&Polanco, fundamentally differs from ours in terms of the model used and the analysis, and we cite this work at the very end of our manuscript as a possible connection, and not as an explanation as the referees comments seem to suggest.
-We hope that we have made our comments sufficiently clear to the referee for the relevance of our work.
-
-\vspace{0.5cm}
-
-On behalf of the authors,
+For Referee B, we believe that the referee has missed the main focus of the paper, which was to report an inverse energy transfer and provide an explanation due to vortex reconnections in terms of a chiral imbalance of helical modes, and not to explain [Krstulovic\&Polanco PRL 2020].
+We cite this work in the very last paragraph of our Letter to establish a possible connection; our findings are not at all an explanation of it.
+The paper by Krstulovic\&Polanco, fundamentally differs from ours in terms of the model used and the analysis.
+We hope that the main aim of the paper is now clear to the referee and we hope that they can see the relevance of our work.
 
@@
 
-\textbf{Piotr Stasiak}
-
+\textbf{Piotr Stasiak}\\
+\textbf{Andrew Baggaley}\\
+\textbf{Carlo Barenghi}\\
+\textbf{Giorgio Krstulovic}\\
+\textbf{Luca Galantucci}\\
 \end{document}

### 2025-06-26 main_REV.tex
GK done
Updated figures
Updated plots and andrews affiliation

@@
 \usepackage{float}
-\usepackage{caption}
+\usepackage{caption,cancel}
 \usepackage{cleveref}
@@
 \author{P. Z. Stasiak}
+\affiliation{School of Mathematics, Statistics and Physics, Newcastle University, Newcastle upon Tyne, NE1 7RU, United Kingdom}
+
 \author{A. Baggaley}
+\affiliation{School of Mathematics, Statistics and Physics, Newcastle University, Newcastle upon Tyne, NE1 7RU, United Kingdom}
+\affiliation{Department of Mathematics and Statistics, Lancaster University, Lancaster, LA1 4YF, UK}
+
 \author{C.F. Barenghi}
@@
 	\centering
-    \begin{subfigure}[b]{0.24\textwidth}
-		\centering
-		\includegraphics*[width=\textwidth]{snap-1.pdf}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\textwidth}
-		\centering
-		\includegraphics*[width=\textwidth]{snap-2.pdf}
-	\end{subfigure}
-    \begin{subfigure}[b]{0.24\textwidth}
-		\centering
-		\includegraphics*[width=\textwidth]{snap-3.pdf}
-	\end{subfigure}
-    \begin{subfigure}[b]{0.24\textwidth}
-		\centering
-		\includegraphics*[width=\textwidth]{snap-4.pdf}
-
-	\end{subfigure} \hfill
-    %
-	\begin{subfigure}[b]{0.24\textwidth}
-		\centering
-		\includegraphics*[width=\textwidth]{snaps-hel-1.pdf}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.24\textwidth}
-		\centering
-		\includegraphics*[width=\textwidth]{snaps-hel-2.pdf}
-	\end{subfigure}
-    \begin{subfigure}[b]{0.24\textwidth}
-		\centering
-		\includegraphics*[width=\textwidth]{snaps-hel-3.pdf}
-	\end{subfigure}
-    \begin{subfigure}[b]{0.24\textwidth}
-		\centering
-		\includegraphics*[width=\textwidth]{snaps-hel-4.pdf}
-	\end{subfigure} \hfill
+  \includegraphics[width=\textwidth]{snapshots.pdf}
+  %   \begin{subfigure}[b]{0.24\textwidth}
+	% 	\centering
+	% 	\includegraphics*[width=\textwidth]{snap-1.pdf}
+	% \end{subfigure}
+	% \begin{subfigure}[b]{0.24\textwidth}
+	% 	\centering
+	% 	\includegraphics*[width=\textwidth]{snap-2.pdf}
+	% \end{subfigure}
+  %   \begin{subfigure}[b]{0.24\textwidth}
+	% 	\centering
+	% 	\includegraphics*[width=\textwidth]{snap-3.pdf}
+	% \end{subfigure}
+  %   \begin{subfigure}[b]{0.24\textwidth}
+	% 	\centering
+	% 	\includegraphics*[width=\textwidth]{snap-4.pdf}
+
+	% \end{subfigure} \hfill
+  %   %
+	% \begin{subfigure}[b]{0.24\textwidth}
+	% 	\centering
+	% 	\includegraphics*[width=\textwidth]{snaps-hel-1.pdf}
+	% \end{subfigure}
+	% \begin{subfigure}[b]{0.24\textwidth}
+	% 	\centering
+	% 	\includegraphics*[width=\textwidth]{snaps-hel-2.pdf}
+	% \end{subfigure}
+  %   \begin{subfigure}[b]{0.24\textwidth}
+	% 	\centering
+	% 	\includegraphics*[width=\textwidth]{snaps-hel-3.pdf}
+	% \end{subfigure}
+  %   \begin{subfigure}[b]{0.24\textwidth}
+	% 	\centering
+	% 	\includegraphics*[width=\textwidth]{snaps-hel-4.pdf}
+	% \end{subfigure} \hfill
 	\caption{
@@
 The energy at reconnection $E_R$ is given by $E(t_R)$, where $t_R$ is the time at reconnection.
-The energy spectrum $E(k)$ is displayed in Fig.~\ref{fig:kinetic-energy}.
-\begin{figure}[h!]
+The energy spectrum $E(k)$ is displayed in Fig.~3a.
+\begin{figure}
     \centering
-    \begin{subfigure}{0.49\textwidth}
-        \centering
-        \includegraphics*[width=\textwidth]{energy-spec.pdf}
-        \caption{}\label{fig:kinetic-energy}
-    \end{subfigure}
-    \begin{subfigure}{0.49\textwidth}
-        \centering
-        \includegraphics*[width=\textwidth]{flux-spec.pdf}
-        \caption{}\label{fig:energy-flux}
-    \end{subfigure}
+    \includegraphics[width=0.49\textwidth]{energy-flux-spec.pdf}
+
+    % \begin{subfigure}{0.49\textwidth}
+    %     \centering
+    %     \includegraphics*[width=\textwidth]{energy-spec.pdf}
+    %     \caption{}\label{fig:kinetic-energy}
+    % \end{subfigure}
+    % \begin{subfigure}{0.49\textwidth}
+    %     \centering
+    %     \includegraphics*[width=\textwidth]{flux-spec.pdf}
+    %     \caption{}\label{fig:energy-flux}
+    % \end{subfigure}
+% \begin{subcaptiongroup*}
+% 	\phantomsubcaption\label{fig:minimum-distance}
+% 	\phantomsubcaption\label{fig:prefactors}
+% \end{subcaptiongroup*}
+
     \caption{\emph{(a):} Normal fluid kinetic energy spectrum $E(k)$ before 
@@
 \emph{Inset:} Post reconnection evolution of the integral length scale, $L$.
-Times and temperatures are labelled as in Fig.~\ref{fig:kinetic-energy}.}
+Times and temperatures are labelled as in Fig.~3a.}
+\label{fig:spectra}
 \end{figure}
@@
 \end{equation}
-The inset of Fig.~\ref{fig:energy-flux} shows that
+The inset of Fig.~3b shows that
 $L$ indeed  increases steadily in the post-reconnection regime. Note that times have been normalised by the largest eddy-turnover-time at the reconnection event, evidencing  it fast evolution.
 
-To explain the inverse energy transfer shown in Fig.~\ref{fig:kinetic-energy},
+To explain the inverse energy transfer shown in Fig.~3b,
 we look whether the reconnection triggers a chirality imbalance. 
@@
 the chirality of the flow generated by the 
-frequent \red{non-symmetrical} reconnections may be strong enough to induce an inverse energy 
-cascade~\cite{notes_recon}.
+frequent \red{non-symmetrical} reconnections may be strong enough to induce an inverse energy cascade~\cite{notes_recon}.
 %The asymmetry of the reconnecting vortex configurations is a key element; 
@@
 the inverse energy cascade which is observed numerically in  
-large-scale simulations of counterflow turbulence at large heat fluxes \cite{polanco2020}, which is
-indeed inherently not isotropic.
+large-scale simulations of counterflow turbulence at large heat fluxes \cite{polanco2020}, which is indeed inherently not isotropic.
+\magenta{However, formalising the connection between high counterflow, unbalanced helicity injection and inverse energy cascade is  challenging, as the model used in \cite{polanco2020} and the one used in our work describe superfluid helium at very different scales.}
 %, hence triggering non-fully reconnections. 

### 2025-06-26 main_REV.tex
Updated figure

@@
 \usepackage{graphicx}% Include figure files
-\usepackage{dcolumn}% Align table columns on decimal point
+\usepackage{dcolumn}% Align table columns on decimal poi<?xml version="1.0" encoding="UTF-8" standalone="no"?>
+<!-- Created with Inkscape (http://www.inkscape.org/) -->
+
+<svg
+   version="1.1"
+   id="svg2379"
+   width="18.273407"
+   height="12.954988"
+   xmlns:inkscape="http://www.inkscape.org/namespaces/inkscape"
+   xmlns:sodipodi="http://sodipodi.sourceforge.net/DTD/sodipodi-0.dtd"
+   xmlns="http://www.w3.org/2000/svg"
+   xmlns:svg="http://www.w3.org/2000/svg">
+  <defs
+     id="defs2383" />
+  <sodipodi:namedview
+     id="namedview2381"
+     pagecolor="#ffffff"
+     bordercolor="#666666"
+     borderopacity="1.0"
+     inkscape:pageshadow="2"
+     inkscape:pageopacity="0.0"
+     inkscape:pagecheckerboard="0" />
+  <inkscape:clipboard
+     style="font-style:normal;font-variant:normal;font-weight:normal;font-stretch:normal;font-size:14.42808189px;line-height:1.25;font-family:'Liberation Sans';font-variant-ligatures:normal;font-variant-position:normal;font-variant-caps:normal;font-variant-numeric:normal;font-variant-alternates:normal;font-variant-east-asian:normal;font-feature-settings:normal;font-variation-settings:normal;text-indent:0;text-align:start;text-decoration-line:none;text-decoration-style:solid;text-decoration-color:#000000;letter-spacing:normal;word-spacing:normal;text-transform:none;writing-mode:lr-tb;direction:ltr;text-orientation:mixed;dominant-baseline:auto;baseline-shift:baseline;white-space:normal;opacity:1;vector-effect:none;fill:#000000;fill-opacity:1;stroke:#000000;stroke-width:0.7802948;stroke-linecap:butt;stroke-linejoin:miter;stroke-miterlimit:4;stroke-dasharray:none;stroke-dashoffset:0;stroke-opacity:1;-inkscape-stroke:none;stop-color:#000000;stop-opacity:1;-inkscape-font-specification:'Liberation Sans'"
+     min="18.259847,226.98512"
+     max="36.533254,239.94011"
+     geom-min="18.649995,227.37527"
+     geom-max="36.143107,239.54997" />
+  <g
+     id="g2385"
+     transform="matrix(3.7795276,0,0,3.7795276,-18.259848,-226.98513)">
+    <text
+       xml:space="preserve"
+       style="font-style:normal;font-weight:normal;font-size:3.81743px;line-height:1.25;font-family:sans-serif;fill:#000000;fill-opacity:1;stroke:#000000;stroke-width:0.206453;stroke-miterlimit:4;stroke-dasharray:none;stroke-opacity:1"
+       x="4.2326026"
+       y="69.187035"
+       id="text37212-4"
+       transform="scale(1.104076,0.90573475)"><tspan
+         sodipodi:role="line"
+         id="tspan37210-3"
+         style="font-style:normal;font-variant:normal;font-weight:normal;font-stretch:normal;font-family:'Liberation Sans';-inkscape-font-specification:'Liberation Sans';stroke:#000000;stroke-width:0.206453;stroke-miterlimit:4;stroke-dasharray:none;stroke-opacity:1"
+         x="4.2326026"
+         y="69.187035">(b)</tspan></text>
+  </g>
+</svg>
+t
 \usepackage{bm}% bold math

### 2025-06-26 main_REV.tex
FInalised figures
Removed coloured text

--- 2025-06-26 main_REV.tex
@@
 \usepackage{graphicx}% Include figure files
-\usepackage{dcolumn}% Align table columns on decimal point
+\usepackage{dcolumn}% Align table columns on decimal poi<?xml version="1.0" encoding="UTF-8" standalone="no"?>
 \usepackage{bm}% bold math
@@
 $(t-t_R)/\tau_R=-7.47\times10^{-2}$, $-3.09\times10^{-3}$, $8.79\times10^{-4}$ and $5.39\times10^{-3}$, where $\tau_R = L_R/E^{1/2}_R$.
-The quantities $E_R$ and $L_R$ are the energy $E$ and integral length scales \red{$L$} of the normal fluid at reconnection time $t_R$.
+The quantities $E_R$ and $L_R$ are the energy $E$ and integral length scales $L$ of the normal fluid at reconnection time $t_R$.
 The green
@@
 three-dimensional turbulent BECs \cite{middleton-spencer2022}. 
-\red{
 In this forward energy cascade a fundamental role is played by the dynamics and interactions of quantum vortices,
@@
 and triggering the Kelvin-wave cascade \cite{vinen-2001}.
-}
 In 2D, similarly to classical turbulence, 
@@
 The vortex pairs are separated by the distance $D_{\ell}$; each vortex within each pair is initially at distance $d_{\ell}$ to the other vortex, such that $d_{\ell}\ll D_{\ell}$ to ensures that the dynamics in the vicinity of the reconnection is dominated by local interactions, and that the far-field contribution from the other vortex pair is negligible.
-\red{All results reported hereafter refer only to the reconnection of one pair of vortices.} 
+All results reported hereafter refer only to the reconnection of one pair of vortices. 
 %\red{In our simulations, the reconnections of the two pairs of vortices occur at different times; here we consider only the vortex dynamics up to and shortly after the first reconnection (see Fig.~\ref{fig:total-helicity}).
@@
 indicating that the flow is persistently chiral. We conclude that the reconnection triggers indeed a chiral imbalance.
-\red{
 For the sake of completeness, it is worth noting that the total helicity of the flow (obtained by adding the superfluid helicity to that of the normal fluid $\mathcal{H}$) is not conserved.
-}
-From Fig.~\ref{fig:mutual-friction-decomp}, \red{ we consider a time $t^*$ after reconnection where the ratio $|f^+|^2/|f^-|^2$ has sufficiently decayed to a roughly 5\% difference and} we determine the non-dimensional timescale \red{$\tau = (t^*-t_R)/\tau_R$} during which the mutual friction force is chiral as a result of reconnections: $\tau \approx 0.01$ and $\tau \approx 0.005$
+From Fig.~\ref{fig:mutual-friction-decomp}, we consider a time $t^*$ after reconnection where the ratio $|f^+|^2/|f^-|^2$ has sufficiently decayed to a roughly 5\% difference and we determine the non-dimensional timescale $\tau = (t^*-t_R)/\tau_R$ during which the mutual friction force is chiral as a result of reconnections: $\tau \approx 0.01$ and $\tau \approx 0.005$
 for $T=1.9$K and $T=2.1$K, respectively, corresponding dimensionally to $\tau \approx 0.1$s for both temperatures. 
@@
 %The helical character of the mutual friction produces a chiral imbalance in the normal fluid, driving this inverse transfer, as previously observed in turbulent Navier-Stokes flows
-This inverse energy transfer \red{is triggered by} the helical character of the
-mutual friction, \red{directly arising from the} Kelvin waves released by the reconnecting
+This inverse energy transfer is triggered by the helical character of the
+mutual friction, directly arising from the Kelvin waves released by the reconnecting
 cusp, which produces a chiral imbalance in the normal fluid, as 
@@
 Our findings have profound implications for the nature of turbulence in 
-finite temperature superfluids, \red{where vortex reconnections play a key role}. 
+finite temperature superfluids, where vortex reconnections play a key role. 
 In circumstances where the vortex density 
@@
 the chirality of the flow generated by the 
-frequent \red{non-symmetrical} reconnections may be strong enough to induce an inverse energy cascade~\cite{notes_recon}.
+frequent non-symmetrical reconnections may be strong enough to induce an inverse energy cascade~\cite{notes_recon}.
 %The asymmetry of the reconnecting vortex configurations is a key element; 
@@
 %account the reconnection.
-The microscopic mechanism that we have described \red{may be relevant in triggering}
+The microscopic mechanism that we have described may be relevant in triggering
 the inverse energy cascade which is observed numerically in  
 large-scale simulations of counterflow turbulence at large heat fluxes \cite{polanco2020}, which is indeed inherently not isotropic.
-\magenta{However, formalising the connection between high counterflow, unbalanced helicity injection and inverse energy cascade is  challenging, as the model used in \cite{polanco2020} and the one used in our work describe superfluid helium at very different scales.}
+However, formalising the connection between high counterflow, unbalanced helicity injection and inverse energy cascade is  challenging, as the model used in \cite{polanco2020} and the one used in our work describe superfluid helium at very different scales.
 %, hence triggering non-fully reconnections. 

### 2025-06-26 revision/referee-response.tex
Updated referee response file

@@
 
-    The presence of the mutual friction force introduces an \red{additional source of} dissipation into the normal fluid.
-Overall, by \red{also} computing the helicity in the superfluid component, we observe that the total helicity during the reconnection event is not conserved.
+    The presence of the mutual friction force introduces an additional source of dissipation into the normal fluid.
+Overall, by also computing the helicity in the superfluid component, we observe that the total helicity during the reconnection event is not conserved.
 We decided to omit this plot from the manuscript so as to not introduce further concepts of superfluid helicity to a paper whose narrative is normal fluid centric.
@@
 Additionally, we computed the normal fluid helicity in each respective half box which also confirms this.
-To illustrate this point, we have modified the text to explicity state thet reconnections occur asynchronously \red{and that we focus on the first one}, and we have added some extra details to Fig.2 in the manuscript which highlight this visually.
+To illustrate this point, we have modified the text to explicity state thet reconnections occur asynchronously and that we focus on the first one, and we have added some extra details to Fig.2 in the manuscript which highlight this visually.
 \\
@@
 
-    \red{We appreciate the referee’s careful reading of the manuscript and their observation regarding a perceived inconsistency between the plots of the energy and energy flux spectra.
+    We appreciate the referee’s careful reading of the manuscript and their observation regarding a perceived inconsistency between the plots of the energy and energy flux spectra.
 The perceived inconsistency arises from the scalings employed.
@@
 If, in fact, we plot the spectra in dimensional units (Figures 1 attached) no inconsistency emerges.
-In the revised version of the code, following the referee's suggestion, we have scaled $E(k)$ by $E_R L_R$.}
+In the revised version of the code, following the referee's suggestion, we have scaled $E(k)$ by $E_R L_R$.
 
@@
 Indeed, this article is only cited at the end of our manuscript, as a possible physical setting where the new physical phenomena described in our manuscript could be relevant.
-\red{The relevance of the large counterflow velocities in our mechanism for inverse energy transfer is in addition addressed in the next point.}
+The relevance of the large counterflow velocities in our mechanism for inverse energy transfer is in addition addressed in the next point.
 
@@
 
-Indeed, the helicity injection produced by random vortex reconnections is not sign-defined, but the helicity injected by a single one, it is.  In isotropic turbulence, the helicity injection produced by vortex reconnections is certainly positive and negative \red{and the overall helicity injected
+Indeed, the helicity injection produced by random vortex reconnections is not sign-defined, but the helicity injected by a single one, it is.  In isotropic turbulence, the helicity injection produced by vortex reconnections is certainly positive and negative and the overall helicity injected
 might cancel out.
-However,} in the case where the system is highly anisotropic and the vortex density is sufficiently large \red{(as it is the case when counterflow velocities are large, where vortices tend to lie in a plane perpendicular to the heat flow)}, such symmetry breaking induced by the counterflow velocity could favour an asymmetry in the reconnection events triggering the overall production of helicity of one given sign.
+However, in the case where the system is highly anisotropic and the vortex density is sufficiently large (as it is the case when counterflow velocities are large, where vortices tend to lie in a plane perpendicular to the heat flow), such symmetry breaking induced by the counterflow velocity could favour an asymmetry in the reconnection events triggering the overall production of helicity of one given sign.
 For this reason, at the end of the conclusion, we mentioned counterflow turbulence as such an example and raised the question of whether the findings of Polanco\&Krstulovic could be ultimately related to the new mechanism reported in our Letter.  Providing a definitive answer to this open question is undoubtedly challenging and beyond the scope of our work.
@@
 This model does not describe quantised vortices, and the energy injection was made through an external term, whose acting scale can be chosen arbitrarily.  The inverse cascade is triggered by the nonlinear term when the counterflow is strong enough, which leads to a strong anisotropy.
-In our coupled model, the normal fluid energy injection is produced by vortex reconnections, and it is indeed transferred towards large scales \red{by non-linear terms, at $k < 40$ (Fig.
+In our coupled model, the normal fluid energy injection is produced by vortex reconnections, and it is indeed transferred towards large scales by non-linear terms, at $k < 40$ (Fig.
 3b), \textit{i.e.} at scales much larger than the vortex core (we recall that our box is
-$1mm^3$)}. We remind the Referee that one needs to be careful while comparing HVBK and our coupled model as they describe the physics at very different scales.  Again, by writing the sentence about Polanco\&Krstulovic, we simply raise a question that needs further investigation.\\
+$1mm^3$). We remind the Referee that one needs to be careful while comparing HVBK and our coupled model as they describe the physics at very different scales.  Again, by writing the sentence about Polanco\&Krstulovic, we simply raise a question that needs further investigation.\\
 
@@
 
-The Referee raises a good point.  In a recent paper [arXiv:2501.08309], three of us studied the wakes generated by moving superfluid vortices (with respect to the normal fluid).
+The Referee raises a good point.
+In a recent paper [arXiv:2501.08309], three of us studied the wakes generated by moving superfluid vortices (with respect to the normal fluid).
 In this case, however, energy results to be transferred to \textit{small} scales, discarding the scenario proposed by the Referee.
-\red{We attach here (Fig.
-2) the plot of the energy flux spectrum corresponding to the development of the wakes: all values are positive, showing a direct energy cascade.} \\
+We attach here (Fig.
+2) the plot of the energy flux spectrum corresponding to the development of the wakes: all values are positive, showing a direct energy cascade.
+\\
 

### 2025-06-30 revision/referee-response.tex
Final updates before re-submission

--- 2025-06-13 revision/referee-response.tex
@@
 \usepackage{xcolor}
-\def\red#1{\textcolor{red}{#1}}
+\def\red#1{\textcolor{black}{#1}}
 \def\blue#1{\textcolor{blue}{#1}}
@@
     The presence of the mutual friction force introduces an \red{additional source of} dissipation into the normal fluid.
-Overall, by \red{also} computing the helicity in the superfluid component, we observe that the total helicity during the reconnection event is not conserved.
-We decided to omit this plot from the manuscript so as to not introduce further concepts of superfluid helicity to a paper whose narrative is normal fluid centric.
-We have addressed the referee's concern by inserting an additional statement to clarify that the total helicity during the reconnection event is not conserved.
-\\
+By also computing the helicity in the superfluid component, we observe that during the reconnection event
+the total helicity (sum of normal fluid helicity and superfluid helicity) is not conserved. We omitted the plot of the superfluid helicity
+from the original manuscript so as to \red{avoid introducing}
+the further concept 
+of superfluid helicity to a paper whose narrative is \red{dedicated to the
+normal fluid}. In the revised manuscript we have addressed the 
+referee's concern by inserting (in page 4) an additional statement 
+to clarify that the total helicity during the reconnection event is 
+\textbf{not} conserved. \\
 
@@
 
-    The initial configuration is set up such that the superfluid velocity circlation in each half box has the opposite sign to the other half box, this is required to satisfy the periodic boundary conditions in the superfluid component.
-In the timescale of the simulation, we only observe one pair of vortices which reconnects, as the reconnection events occur asynchronously.
-During the reconnection, due to the large injection the helicity from the other pair is anyway negligible.
-The extended version of the simulation shows that the second reconnection injects positive helicity in the normal fluid, which then decays back to zero.
-Additionally, we computed the normal fluid helicity in each respective half box which also confirms this.
-To illustrate this point, we have modified the text to explicity state thet reconnections occur asynchronously \red{and that we focus on the first one}, and we have added some extra details to Fig.2 in the manuscript which highlight this visually.
-\\
+    In our manuscript, we indeed only describe the results referring to one pair of reconnecting 
+    vortices. We confirm that the helicity injected by the other pair is indeed positive.
+
+%    The initial \red{vortex} configuration is set up such that the 
+%superfluid velocity circulation in each half-box has the opposite sign to 
+%the other half-box; \red{in this way, the superfluid velocity satisfies
+%periodic boundary conditions over the entire computational 
+%domain}.
+%\red{It is important to appreciate that the two reconnection events do
+%not occurr at the same time}. 
+%In the timescale of the simulation \red{which we report in our manuscript}, 
+%we only observe one pair of vortices which reconnects, as the reconnection 
+%\red{of the other vortex pair occurs later, when the main impact of the first
+%reconnection has vanished}.
+
+%\red{We find that} during \red{this first reconnection}, the helicity contribution
+%from the other vortex pair is negligible. \red{If we extend the
+%simulation for a longer time and observe the second reconnection,
+%we notice that} the second reconnection injects positive helicity 
+%in the normal fluid, which then decays back to zero.
+
+%Additionally, we computed the normal fluid helicity in each respective 
+%half-box, confirming that the first reconnection injects negative
+%helicity (computed only in its half-box), and, later, the second reconnection
+%injects positive helicity (in its own half-box).
+
+%To \red{better} illustrate this point, we have modified the text to 
+%explicity state that \red{the two} reconnections occur 
+%asynchronously, \red{that the second reconnection is required by the
+%periodic boundary conditions of our computational domain}, 
+%\red{and that, physically, we focus the discussion of our results
+%on the first reconnection only}.
+%We have also added some extra details to Fig.2 in the \red{revised}
+%manuscript which highlight this \red{feature} visually. \\
 
@@
     The mutual friction force is helical as a result of the presence of Kelvin wave packets released along the vortices after the relaxation of the cusp generated at reconnection.
-The two elements, helical character of the mutual friction force and the presence of Kelvin wave are hence inter-twinned.
-We have
-underlined this aspect in the revised version of the manuscript, by slightly modifying the sentence pointed by the referee.  
+The two elements, the helical character
+of the mutual friction force and the presence of Kelvin wave, are 
+therefore inter-twinned. In the revised manuscript we have 
+underlined this aspect  by slightly modifying the sentence pointed out.
+by the referee.  
 %    The referee is correct in thinking that the inverse energy transfer is due to the Kelvin waves.
@@
 
-As the Referee is certainly aware, vortex reconnections play an important role in turbulence.  We have never claimed that our system is turbulent, but we do think that our findings have a strong impact on quantum turbulence.  In the text, we have only referred to `turbulence' in the introduction to motivate our work and to explain its relevance to a broad audience, and at the very end to comment on its implications in the conclusions.
+As the Referee is certainly aware, vortex reconnections play an important role in turbulence.We have never claimed that our system is turbulent, but we do think that our findings have a strong impact on quantum turbulence.
+In the text, we have only referred to `turbulence' in the introduction to motivate our work and to explain its relevance to a broad audience, and at the very end to comment on its implications in the conclusions.
 Explaining cascades, turbulence and invariants is necessary to understand the role of helicity on transfer towards large scales.
-We still believe that the use of the word turbulence is appropriate in our manuscript.
-We have nevertheless added a sentence in the introduction to remind the reader of the importance of vortex reconnections in quantum turbulent flows and a comment in the conclusions about when our finding might be important for quantum turbulence.
-\\
+We still believe that the use of the word turbulence is
+appropriate in our manuscript \red{to put our results into the most 
+relevant context}.
+
+\red{Nevertheless, to take the referee's comment into account,}
+we have added a sentence in the introduction \red{(page 1)}
+to remind the reader of the importance of vortex reconnections 
+in quantum turbulent flows, and a comment in the conclusions 
+about when our finding might be important for quantum turbulence. \\
 
@@
 
-\noindent We hope that we have provided enough arguments to the Referee and they see now the impact of our Letter.
+\noindent \red{We trust} that we have clarified to the Referee the goal and main results of our Letter, and at the same time, provided enough arguments to emphasize the impact of our Letter.
 

### 2025-06-30 revision/editor_letter.tex
Final updates before re-submission

--- 2025-06-25 revision/cover_letter_REV.tex
@@
 
-For Referee A, we have added further details in the manuscript to address the major concerns, particularly regarding the conservation and symmetry of the normal fluid helicity, and the relevance of Kelvin waves in the creation of unbalanced chiral modes.
+Regarding Referee A, we have added further details in the manuscript to address in detail the major concerns, particularly regarding the conservation and symmetry of the normal fluid helicity, and the relevance of Kelvin waves in the creation of unbalanced chiral modes.
 
-For Referee B, we believe that the referee has missed the main focus of the paper, which was to report an inverse energy transfer and provide an explanation due to vortex reconnections in terms of a chiral imbalance of helical modes, and not to explain [Krstulovic\&Polanco PRL 2020].
-We cite this work in the very last paragraph of our Letter to establish a possible connection; our findings are not at all an explanation of it.
+Regarding Referee B, we believe that the referee has missed the main focus of the paper, which was to report an inverse energy transfer and provide an explanation in terms of vortex reconnections triggering a chiral imbalance of helical modes, and not to explain the article Krstulovic\&Polanco PRL 2020 (that one of us
+co-authors).
+We cite this work only in the very last paragraph of our Letter to establish a possible connection and to describe a physical setting where the new physical phenomena described in our manuscript could be relevant; our findings are not at all an explanation of it.
 The paper by Krstulovic\&Polanco, fundamentally differs from ours in terms of the model used and the analysis.

### 2025-10-06 main_REV.tex
Updated figures with new corrected colour scheme and hopf link data

@@
     \centering
-    \includegraphics*[width=0.48\textwidth]{helicity_total.pdf}
-\caption{Temporal evolution of the normal fluid helicity $\mathcal{H} = \int_{\mathcal{V}}H(\x)dV$ computed over the entire volume $\mathcal{V}$.
-For superfluid helium, it is proper to make the helicity dimensionless in terms of $\kappa^2$.
-$\tau_R = L_R/E^{1/2}_R$.
+
+      \begin{subfigure}{0.49\textwidth}
+        \centering
+        \includegraphics*[width=\textwidth]{helicity_total.pdf}
+        \caption{}\label{fig:}
+    \end{subfigure}
+    \begin{subfigure}{0.49\textwidth}
+        \centering
+        \includegraphics*[width=\textwidth]{integral-scale-scaled.pdf}
+        \caption{}\label{fig:}
+
+    \end{subfigure}
+\caption{\blue{Temporal evolution of the normal fluid helicity $\mathcal{H} = \int_{\mathcal{V}}H(\x)dV$ computed over the entire volume $\mathcal{V}$.
+For superfluid helium, it is proper to make the helicity dimensionless in terms of $\kappa^2$.}
 %\red{The 3D rendering shows the asynchronous nature of the reconnections in the initial configuration, with the two reconnections occurring at different times; same colour scheme as in Fig.~\ref{fig:visualisation}.}
@@
     \centering
-    \includegraphics[width=0.49\textwidth]{energy-flux-spec.pdf}
-
-    % \begin{subfigure}{0.49\textwidth}
-    %     \centering
-    %     \includegraphics*[width=\textwidth]{energy-spec.pdf}
-    %     \caption{}\label{fig:kinetic-energy}
-    % \end{subfigure}
-    % \begin{subfigure}{0.49\textwidth}
-    %     \centering
-    %     \includegraphics*[width=\textwidth]{flux-spec.pdf}
-    %     \caption{}\label{fig:energy-flux}
-    % \end{subfigure}
+    % \includegraphics[width=0.49\textwidth]{energy-flux-spec.pdf}
+
+    \begin{subfigure}{0.49\textwidth}
+        \centering
+        \includegraphics*[width=\textwidth]{energy-spec-scaled.pdf}
+        \caption{}\label{fig:kinetic-energy}
+    \end{subfigure}
+    \begin{subfigure}{0.49\textwidth}
+        \centering
+        \includegraphics*[width=\textwidth]{flux-spec-scaled.pdf}
+        \caption{}\label{fig:energy-flux}
+    \end{subfigure}
 % \begin{subcaptiongroup*}

### 2025-10-09 main_REV.tex

--- 2025-06-26 main_REV.tex
@@
 times (from left to right)
-$(t-t_R)/\tau_R=-7.47\times10^{-2}$, $-3.09\times10^{-3}$, $8.79\times10^{-4}$ and $5.39\times10^{-3}$, where $\tau_R = L_R/E^{1/2}_R$.
-The quantities $E_R$ and $L_R$ are the energy $E$ and integral length scales $L$ of the normal fluid at reconnection time $t_R$.
-The green
+$(t-t_R)/\tau_R=-7.47\times10^{-2}$, $-3.09\times10^{-3}$, $8.79\times10^{-4}$ and $5.39\times10^{-3}$, where $\tau_R = L_R/E^{1/2}_R$. The green
 tubes represent the superfluid vortex lines (the tubes’ radii have been 
@@
     \centering
-    \includegraphics*[width=0.48\textwidth]{helicity_total.pdf}
-\caption{Temporal evolution of the normal fluid helicity $\mathcal{H} = \int_{\mathcal{V}}H(\x)dV$ computed over the entire volume $\mathcal{V}$.
-For superfluid helium, it is proper to make the helicity dimensionless in terms of $\kappa^2$.
-$\tau_R = L_R/E^{1/2}_R$.
+
+      \includegraphics[width=0.49\textwidth]{helicity_integralScale.pdf}
+    %   \begin{subfigure}{0.49\textwidth}
+    %     \centering
+    %     \includegraphics*[width=\textwidth]{helicity_total.pdf}
+    %     \caption{}\label{fig:}
+    % \end{subfigure}
+    % \begin{subfigure}{0.49\textwidth}
+    %     \centering
+    %     \includegraphics*[width=\textwidth]{integral-scale-scaled.pdf}
+    %     \caption{}\label{fig:}
+
+    % \end{subfigure}
+\caption{\red{ \emph(a) Temporal evolution of the normal fluid helicity $\mathcal{H} = \int_{\mathcal{V}}H(\x)dV$ computed over the entire volume $\mathcal{V}$.
+\emph(b) Post reconnection evolution of the integral length scale, $L_0$ scaled by the reconnection time integral scale $L_R$.
+The bold solid lines represent the orthogonal reconnections (right axis), while the slightly faded lines represent the data at the same temperature for Hopf-link reconnections (left axis) from Ref.~\cite{stasiak2025experimental}.
+%For superfluid helium, it is proper to make the helicity dimensionless in terms of $\kappa^2$.
+}
 %\red{The 3D rendering shows the asynchronous nature of the reconnections in the initial configuration, with the two reconnections occurring at different times; same colour scheme as in Fig.~\ref{fig:visualisation}.}
@@
     \centering
-    \includegraphics[width=0.49\textwidth]{energy-flux-spec.pdf}
+    \includegraphics[width=0.49\textwidth]{energySpec-fluxSpec.pdf}
 
@@
     %     \centering
-    %     \includegraphics*[width=\textwidth]{energy-spec.pdf}
+    %     \includegraphics*[width=\textwidth]{energy-spec-scaled.pdf}
     %     \caption{}\label{fig:kinetic-energy}
@@
     %     \centering
-    %     \includegraphics*[width=\textwidth]{flux-spec.pdf}
+    %     \includegraphics*[width=\textwidth]{flux-spec-scaled.pdf}
     %     \caption{}\label{fig:energy-flux}
     % \end{subfigure}
-% \begin{subcaptiongroup*}
-% 	\phantomsubcaption\label{fig:minimum-distance}
-% 	\phantomsubcaption\label{fig:prefactors}
-% \end{subcaptiongroup*}
+\begin{subcaptiongroup*}
+	\phantomsubcaption\label{fig:energy-spec}
+	\phantomsubcaption\label{fig:flux-spec}
+\end{subcaptiongroup*}
 
@@
 and after reconnection (dotted lines) for $T=1.9K$ (red)
-and $T=2.1K$ (blue).\emph{(b):} Spectral normal fluid kinetic energy flux, $\Pi (k)$. It is normalised using the integral scale and the normal fluid energy at reconnection.
-\emph{Inset:} Post reconnection evolution of the integral length scale, $L$.
+and $T=2.1K$ (blue).\emph{(b):} Spectral normal fluid kinetic energy flux, $\Pi (k)$.
+\red{It is normalised using the box size and the quantum of circulation $\kappa$}.
 Times and temperatures are labelled as in Fig.~3a.}
@@
 % in Fig.~\ref{fig:visualisation}} \NOTE{GK: the figure shows small scale structures...}
-This behaviour is quantified by the evolution of the integral length scale $L$, defined as
+This behaviour is quantified by the evolution of the integral length scale $L_0$, defined as
 \begin{equation}
-    L = \frac{\pi}{2 E}\int_0^{\infty}\frac{E(k)}{k}dk, %\Big/ \int_0^{\infty}\!\!E(k)dk.
+    L_0 = \frac{\pi}{2 E}\int_0^{\infty}\frac{E(k)}{k}dk, %\Big/ \int_0^{\infty}\!\!E(k)dk.
 \end{equation}
 The inset of Fig.~3b shows that
-$L$ indeed  increases steadily in the post-reconnection regime. Note that times have been normalised by the largest eddy-turnover-time at the reconnection event, evidencing  it fast evolution.
+$L_R$ indeed  increases steadily in the post-reconnection regime. Note that times have been normalised by the largest eddy-turnover-time at the reconnection event, evidencing  it fast evolution.
 

### 2025-10-10 revision-2/referee-response.tex
Added comments to referee A

\documentclass[a4paper,10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{cite}
\usepackage{amsmath}
\usepackage{graphicx}% Include figure files
\usepackage{bm}% bold math
\usepackage{float}
\usepackage{xcolor}
\def\red#1{\textcolor{black}{#1}}
\def\blue#1{\textcolor{blue}{#1}}

\def\refcomment#1{\textbf{\blue{\emph{#1}}}\\}
\hbadness=99999  % or any number >=10000

\begin{document}
\section*{\centering Point-by-point response to referee comments}

We thank the reviewers for taking the time to read over and give constructive feedback on our paper titled “\emph{Inverse energy transfer in three-dimensional quantum vortex flows}", submitted to PRL. Please see below the point-by-point response to the comments made by the reviewers.

\subsection*{Referee A}

\refcomment{For issue 1), authors
commented “We omitted the plot of the superfluid helicity from the
original manuscript,” but I did not understand where or which part was
omitted.}

\refcomment{For issue 2), the total sign of helicity for two
reconnections is neutral; one is negative and the other is positive.
Therefore, total symmetry breaking does not occur. This means that a
lot of reconnections do not cause total symmetry breaking or chiral
imbalance in quantum turbulence. As a result, the inverse cascade will
not happen.}

We would like to highlight one subtlety of orthogonal reconnection simulations, which is that the two reconnections occur asynchronously. Given a large enough separation between vortices within the pair, as was this case for the configuration in our work, the large timescales required to observe a reconnection can lead to the pairs having very different reconnection times. Small deviations build up over time and the minimum distance $\delta$ between the vortices within each pair is not identical. As a result, the two reconnections do not occur at the same time. Pre-reconnection, it is true that the there is no global symmetry breaking, as the normal fluid helicity is not only negligible but is cancelled out globally. In fact, even at the reconnection of the first pair of vortices, the normal fluid helicity generated by the second pair does not change in light of the reconnection and remains negligible. This can be seen by computing the evolution of the normal fluid helicity in half-boxes containing exactly one pair of vortices. Therefore we do indeed have global symmetry breaking, even though we say that we are only considering one vortex pair. If we extended the plot of helicity in Fig.2a, one would see that the helicity injected is of the negative sign, with the global helicity returning back to 0. \\

To further to make this point, in Fig.2 of the paper we include the reconnection data of Hopf-links that constitute a range of reconnection angles. The helicity evolution shows a strong injection of helicity and an increase in the integral length scale post reconnection. A similar analysis that we did on the helical decomposition also showed the same inverse energy transfer, but less stronger than for the orthogonal reconnection. We hope that this evidence is enough for the referee to see that we do indeed have symmetry breaking in the system. \\

Furthermore, we would like to remind the referee that the effect that we are reporting o occurs locally, and our results do not attempt to suggest that this mechanism is responsible for inverse energy cascades in 3D quantum turbulence such as in counterflow channels. However, we would like to refer the referee to recent experimental results in counterflow channels such as in Ref~\cite{marakov2015,gao2017,mastracci2019,yui2020}. In these work, the experimental team often report the observation of large-scale normal fluid turbulence in thermal counterflow, which is still unexplained. In Ref.\cite{mastracci2019} the authors suggest that the large scale normal fluid turbulence may result from wake structures. Using data taken from a recent preprint \cite{galantucci2025} that three of us were part of, we calculated that the the flux of normal fluid due to wake structure is positive, implying an energy transfer to \emph{smaller} scales rather than larger scales. \\

\refcomment{Regarding issue 3), a new normalization does not improve
the order of the kinetic energy spectrum and kinetic energy flux,
although Fig. 1 with dimensions in the response letter indeed shows a
reasonable order.}

In the revised manuscript, we have adapted the figures in the paper to use a normalization that is based on a temperature dependent scaling, which was the reason why the figures before showed an apparent inconsistency between the energy spectrum and the flux. The figures now show the same order as one would find when using dimensional units.

\begin{thebibliography}{4}
    \bibitem{marakov2015}
    A. Marakov, J. Gao, W. Guo, S.W. Van Sciver, G.G. Ihas, D.N. McKinsey, and W.F. Vinen, Visualization of the normal-fluid turbulence in counterflowing superfluid \textsuperscript{4}He, \emph{Phys. Rev. B} \textbf{91}, 094503 (2015).

    \bibitem{gao2017}
    J. Gao, E. Varga, W. Guo, and W.F. Vinen, Energy spectrum of thermal counterflow turbulence in superfluid helium-4, \emph{Phys. Rev. B} \textbf{96}, 094511 (2017)

    \bibitem{mastracci2019}
    B. Mastracci, S. Bao, W. Guo, and W.F. Vinen, Particle tracking velocimetry applied to thermal counterflow in superfluid \textsuperscript{4}He: motion of the normal fluid at small heat fluxes, \emph{Phys. Rev. Fluids} \textbf{4}, 083305 (2019).

    \bibitem{yui2020}
    S. Yui, H. Kobayashi, M. Tsubota, and W. Guo, Fully coupled dynamics of the two fluids in superfluid \textsuperscript{4}He: Anomalous anisotropic velocity fluctuations in counterflow, \emph{Phys. Rev. Lett.} \textbf{124}, 155301 (2020).

    \bibitem{galantucci2025}
    L. Galantucci, G. Krstulovic, and C. F. Barenghi, Quantum vortices leave a macroscopic signature in the normal fluid. \emph{arXiv preprint arXiv:2501.08309} (2025).

\end{thebibliography}

\end{document}

### 2025-10-10 main_REV.tex
Added comments to referee A

@@
 	\centering
-  \includegraphics[width=\textwidth]{snapshots.pdf}
+  \includegraphics[width=0.95 \textwidth]{snapshots-2.pdf}
   %   \begin{subfigure}[b]{0.24\textwidth}
@@
 	\caption{
+    \red{
 Three-dimensional rendering of the time evolution of
@@
 undergoing a vortex reconnection at $T = 1.9$K at dimensionless
-times (from left to right)
-$(t-t_R)/\tau_R=-7.47\times10^{-2}$, $-3.09\times10^{-3}$, $8.79\times10^{-4}$ and $5.39\times10^{-3}$, where $\tau_R = L_R/E^{1/2}_R$. The green
-tubes represent the superfluid vortex lines (the tubes’ radii have been 
+times 
+% (from left to right) $(t-t_R)/\tau_R=-7.47\times10^{-2}$, $-3.09\times10^{-3}$, $8.79\times10^{-4}$ and $5.39\times10^{-3}$,
+where $\tau_R = L^2/\kappa$. 
+The green tubes represent the superfluid vortex lines (the tubes’ radii have been 
 greatly exaggerated for visual purpose). In the top sequence,
@@
 $\bom^2/\bom^2_{max}$. Note the Kelvin wave on the superfluid
-vortex at $(t-t_R)/\tau_R=8.79\times10^{-4}$ . In the bottom sequence, the red/blue volume
+vortex at $(t-t_R)/\tau_R\approx0.001$. In the bottom sequence, the red/blue volume
 rendering at the same times represent scaled positive/negative normal fluid
 helicity.	
+    }
 %Three-dimensional rendering of an orthogonal vortex configuration 
@@
 The vortex pairs are separated by the distance $D_{\ell}$; each vortex within each pair is initially at distance $d_{\ell}$ to the other vortex, such that $d_{\ell}\ll D_{\ell}$ to ensures that the dynamics in the vicinity of the reconnection is dominated by local interactions, and that the far-field contribution from the other vortex pair is negligible.
-All results reported hereafter refer only to the reconnection of one pair of vortices. 
+All results reported hereafter \red{related to the orthogonal reconnection} refer only to the reconnection of one pair of vortices. 
+\red{In our findings we also report similar observations using Hopf-links from Ref.~\cite{stasiak2025experimental}, which we show in Fig.\ref{fig:total-helicity}.}
 %\red{In our simulations, the reconnections of the two pairs of vortices occur at different times; here we consider only the vortex dynamics up to and shortly after the first reconnection (see Fig.~\ref{fig:total-helicity}).
@@
 \emph(b) Post reconnection evolution of the integral length scale, $L_0$ scaled by the reconnection time integral scale $L_R$.
-The bold solid lines represent the orthogonal reconnections (right axis), while the slightly faded lines represent the data at the same temperature for Hopf-link reconnections (left axis) from Ref.~\cite{stasiak2025experimental}.
+The bold solid lines represent the orthogonal reconnections (right axis).
+In \emph{(a)} and left-axis of \emph{(b)}, the slightly faded lines represent the data at the same temperature for Hopf-link reconnections from Ref.~\cite{stasiak2025experimental}.
 %For superfluid helium, it is proper to make the helicity dimensionless in terms of $\kappa^2$.

### 2025-10-13 revision-2/referee-response.tex
First draft of the second response to referees - PZS

@@
 
+Originally we wanted to include the plot of the superfluid helicity in the plot of the normal fluid helicity, however we decided against this as in this paper we decided to only focus on the normal fluid aspect.
+It was irrelevant for the point we were trying to make, which is that the normal fluid helicity spikes at reconnection leading to a chiral imbalance and inverse energy transfer.\\
+
 \refcomment{For issue 2), the total sign of helicity for two
@@
 However, we would like to refer the referee to recent experimental results in counterflow channels such as in Ref~\cite{marakov2015,gao2017,mastracci2019,yui2020}.
-In these work, the experimental team often report the observation of large-scale normal fluid turbulence in thermal counterflow, which is still unexplained.
+In these works, the experimental team often report the observation of large-scale normal fluid turbulence in thermal counterflow, which is still unexplained.
 In Ref.\cite{mastracci2019} the authors suggest that the large scale normal fluid turbulence may result from wake structures.
-Using data taken from a recent preprint \cite{galantucci2025} that three of us were part of, we calculated that the the flux of normal fluid due to wake structure is positive, implying an energy transfer to \emph{smaller} scales rather than larger scales.
+Using data taken from a recent preprint \cite{galantucci2025} that three of us were part of, we calculated that the the flux of normal fluid due to wake structure is positive, implying an energy transfer to \emph{smaller} scales rather than larger scales, suggesting that wake structures are not likely to be the reason behind the large-scale normal fluid turbulence observed.
 \\
@@
 The figures now show the same order as one would find when using dimensional units.
+
+\subsection*{Referee B}
 

### 2025-10-30 supp-mat/supp-mat.tex
Add CFBs text, and remove colouring and green text
Add files via upload
minimal changes
Expanded numerical methods in the supplementary materials

--- 2024-11-20 supp-mat/supp-mat.tex
@@
 \def\red{\textcolor{red}}
+\hbadness=99999  % or any number >=10000
 
@@
 
-\title{Supplementary Materials: Inverse energy transfer in finite-temperature superfluid vortex reconnections}
+\title{Supplementary Materials: Inverse energy transfer in three-dimensional quantum vortex flows}
 
@@
 \author{C.F. Barenghi}
+\affiliation{School of Mathematics, Statistics and Physics, Newcastle University, Newcastle upon Tyne, NE1 7RU, United Kingdom}
+
 \author{A. Baggaley}
 \affiliation{School of Mathematics, Statistics and Physics, Newcastle University, Newcastle upon Tyne, NE1 7RU, United Kingdom}
+\affiliation{Department of Mathematics and Statistics, Lancaster University, Lancaster, LA1 4YF, UK}
+
+\author{G. Krstulovic}
+\affiliation{Universit\'e C\^ote d'Azur, Observatoire de la C\^ote d'Azur, CNRS,Laboratoire Lagrangre, Boulevard de l'Observatoire CS 34229 - F 06304 NICE Cedex 4, France}
 
@@
 \affiliation{Istituto per le Applicazioni del Calcolo ``M. Picone" IAC CNR, Via dei Taurini 19, 00185 Roma, Italy}
-
-\author{G. Krstulovic}
-\affiliation{Universit\'e C\^ote d'Azur, Observatoire de la C\^ote d'Azur, CNRS,Laboratoire Lagrangre, Boulevard de l'Observatoire CS 34229 - F 06304 NICE Cedex 4, France}
 
@@
 	\centering
-	\includegraphics[width=0.4\textwidth]{schematic.png}
-	\caption{Schematic diagram of the initial vortex configuration.}
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=0.8\textwidth]{schematic.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\textwidth}
+		\centering
+		\includegraphics[width=0.9\textwidth]{schematic-2.png}
+	\end{subfigure}
+	\caption{Schematic diagram of the orthogonal vortex configuration.}
 	\label{fig:schematic}
@@
 
-Using Schwarz mesoscopic model \cite{schwarzThreedimensionalVortexDynamics1988a}, vortex lines can be described as space curves $\s(\xi,t)$ of infinitesimal thickness, with a single quantum of circulation $\kappa=h/m_4=9.97\times10^{-8}\text{m}^2/\text{s}$, where $h$ is Planck's constant, $m_4=6.65\times10^{-27}\text{kg}$ is the mass of one helium atom, $\xi$ is the natural parameterisation, arclength, and $t$ is time.
+Using Schwarz mesoscopic model \cite{schwarzThreedimensionalVortexDynamics1988a}, vortex lines can be described as space curves $\s(\xi,t)$ of infinitesimal thickness, with a single quantum of circulation $\kappa=h/m_4=9.97\times10^{-8}\text{m}^2/\text{s}$, where $h$ is Planck's constant, $m_4=6.65\times10^{-27}\text{kg}$ is the mass of one helium atom, $\xi$ is the natural parameterization, arclength, and $t$ is time.
 These conditions are a good approximation, since the vortex core radius of superfluid \textsuperscript{4}He($a_0=10^{-10}\text{m}$) is much smaller than any of the length scales of interest in turbulent flows.
@@
 where $\mathcal{D}$ is a coefficient dependent on the vortex Reynolds number and intrinsic properties of the normal fluid.
-The regularisation of the mutual fricition force onto the normal fluid grid is physically motivated by the strongly localised injection of vorticity during the momentum exchange of point-like particles and viscous flow in classical fluid dynamics \cite{gualtieri2015exact,gualtieri2017turbulence}.
-In short, the localised vorticity induced by the relative motion between the vortex lines and the normal fluid is diffused to discretisation of the grid spacing $\Delta x$ in a time interval $\epsilon_R$.
-In this way, the delta-forced fricition as defined in Eq.~\ref{eq:mutual-friction} is regularised by a Gaussian function, the fundamental solution of the diffusion equation.
+The regularization of the mutual friction force onto the normal fluid grid is physically motivated by the strongly localized injection of vorticity during the momentum exchange of point-like particles and viscous flow in classical fluid dynamics \cite{gualtieri2015exact,gualtieri2017turbulence}.
+In short, the localized vorticity induced by the relative motion between the vortex lines and the normal fluid is diffused to discretization of the grid spacing $\Delta x$ in a time interval $\epsilon_R$.
+In this way, the delta-forced friction as defined in Eq.~\ref{eq:mutual-friction} is regularized by a Gaussian function, the fundamental solution of the diffusion equation.
 Further details of the method for classical fluids are contained in \cite{gualtieri2015exact,gualtieri2017turbulence} and for FOUCAULT in \cite{galantucciNewSelfconsistentApproach2020b}.
@@
 In this Letter, we report all results using dimensionless units, where the characteristic length scale is $\tilde{\lambda} = D/D_0$, where $D^3=(1\times10^{-3}\mathrm{m})^3$ is the dimensional cube size, $D_0^3=(2\pi)^3$ is the non-dimensional cubic computational domain.
-The time scale is given by $\tilde{\tau}=\tilde{\lambda}^2\nu_n^0\nu_n$, where the non-dimensional viscosity $\nu_n^0$ resolves the small scales of the normal fluid.
-In these simulations, these quanties are $\tilde{\lambda}=1.59\times10^{-4}$m, $\nu_n^0=0.32$ and $\tilde{\tau}=0.366$s at $T=1.9K$ and $\tilde{\tau}=0.485$s at $T=2.1K$.
-We consider an initial configuration of two pairs of orthongal vortices, initialised as shown in the schematic of Fig.~\ref{fig:schematic}.
+The time scale is given by $\tilde{\tau}=\tilde{\lambda}^2\nu_n^0/\nu_n$, where the non-dimensional viscosity $\nu_n^0$ resolves the small scales of the normal fluid.
+In this work, we consider two vortex configurations - initially orthogonal vortices and Hopf links.\\
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.7\textwidth]{hopflink-snapshot.pdf}
+	\caption{Schematic diagram of the Hopf link vortex configuration.}
+	\label{fig:Hopf-link}
+\end{figure}
+
+\paragraph{Orthogonal reconnection:} The characteristic quantities are $\tilde{\lambda}=1.59\times10^{-4}$m, $\nu_n^0=0.32$ and $\tilde{\tau}=0.366$s at $T=1.9K$ and $\tilde{\tau}=0.485$s at $T=2.1K$.
+The vortices are initialized as two pairs of orthogonal vortices, as shown in the schematic of Fig.~\ref{fig:schematic}.
+The separation between vortices in each pair $d$ is set to be $d_v=0.5$ in dimensionless units, and the shortest distance between pairs is $D_v=\sqrt{(\pi-d_v/2)^2+\pi^2}\approx 3.08$, so that $d_v\ll D_v$.
+The Lagrangian discretization of vortex lines is $\Delta \xi = 0.025$ (a total of 1340 discretization points across the 4 vortex lines), using a timestep of $\Delta t_{VF} = 5.56\times10^{-6}$.
+For the normal fluid, a total of $N=256^3$ mesh point were used, with a timestep of $\Delta t_{NS} = 45\Delta t_{VF}$.
+\\
+
+\paragraph{Hopf link:} The characterstic quantities are $\tilde{\lambda}=1.59\times10^{-4}$m, $\nu_n^0=0.16$ and $\tilde{\tau}=0.1836$s at $T=1.9K$ and $\tilde{\tau}=0.2439$s at $T=2.1K$.
+Vortices are initialized as shown in Fig.~\ref{fig:Hopf-link}, where the blue vortex ring is chosen at an initial offset $n_x\Delta x$ and $n_y \Delta y$ where $n_x,n_y\in\lbrace-3,\cdots 3\rbrace$ and $\Delta x = \Delta y = 0.125$ in units of the code.
+This gives a total of 49 individual reconnections for each temperature.
+Both of the rings have radius $R\approx 1$ also in units of the code.
+Furthermore, each reconnection is supplemented with a normal fluid ring around the superfluid vortex ring, which is generated by superimposing a normal fluid ring generated by a propagating ring of the same radius.
+In this way, we eliminate a transient phase of generating normal fluid structures.
+The Lagrangian discretization of the vortex lines is $\Delta\xi = 0.025$ (a total of 668 discretization points across both of the rings), using a timestep of $\Delta_{VF} = 1.25\times 10^{-5}$.
+For the normal fluid, a total of $N=256^3$ mesh points were used, with a timestep of $\Delta t_{NS} = 40\Delta t_{VF}$.
 

### 2025-10-30 revision-2/referee-response.tex
Major revisions to text- LG

--- 2025-10-10 revision-2/referee-response.tex
@@
 
+\def\red#1{\textcolor{red}{#1}}
+\def\magenta#1{\textcolor{magenta}{#1}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newcommand*{\NOTE}[1]{\textbf{\color{red}[#1]}}
+\newcommand*{\CHANGE}[1]{{\color{magenta}#1}}
+\newcommand*{\DEL}[1]{{\color{green}#1}}
+
 \begin{document}
@@
 
+Originally we wanted to include the plot of the superfluid helicity in the plot of the normal fluid helicity.
+We decided against this as in this paper we decide to only focus on the normal fluid aspect.
+\CHANGE{Nevertheless, we have included a sentence in the manuscript emphasizing that the total helicity of the flow, normal fluid plus superfluid, is nor conserved in the reconnection process.}\\
+
 \refcomment{For issue 2), the total sign of helicity for two
@@
 
-We would like to highlight one subtlety of orthogonal reconnection simulations, which is that the two reconnections occur asynchronously.
+%We would like to highlight one subtlety of orthogonal reconnection simulations, which is that the two reconnections occur asynchronously.
 Given a large enough separation between vortices within the pair, as was this case for the configuration in our work, the large timescales required to observe a reconnection can lead to the pairs having very different reconnection times.
@@
 
-To further to make this point, in Fig.2 of the paper we include the reconnection data of Hopf-links that constitute a range of reconnection angles.
+\CHANGE{
+To generalise our findings, we perform the study of the chiral imbalance generated by reconnections occurring in Hopf-links, constituted by two, linked, orthogonal vortex rings,
+whose initial relative position is varied (see new figures in Supplemental material). This allows to observe reconnections taking place at different angles.
+Also in this geometrical setting, we observe a strong helicity injection, an increase of the integral scale of the flow, negative spectral fluxes and mutual friction force 
+chirality. We have included the data referring to Hopf-link reconnections in the manuscript and in the Supplemental material.
+Hence, we can claim, with supporting evidence, that reconnections trigger inverse energy transfer. However, this transfer of energy towards large scales may lead
+to an inverse cascade only if reconnections are not exactly symmetrycal, \textit{i.e.} (simplifying) if the number of reconnections of a given type is not exactly balanced by 
+the same number of reconnections between vortices of opposite circulation. We suggest that this might be the case when symmetry is broken by external forcing, as in thermal counterflow.}
+
+%further to make this point, in Fig.2 of the paper we include the reconnection data of Hopf-links that constitute a range of reconnection angles.
 The helicity evolution shows a strong injection of helicity and an increase in the integral length scale post reconnection.
@@
 
-Furthermore, we would like to remind the referee that the effect that we are reporting o occurs locally, and our results do not attempt to suggest that this mechanism is responsible for inverse energy cascades in 3D quantum turbulence such as in counterflow channels.
+%Furthermore, we would like to remind the referee that the effect that we are reporting o occurs locally, and our results do not attempt to suggest that this mechanism is responsible for inverse energy cascades in 3D quantum turbulence such as in counterflow channels.
 However, we would like to refer the referee to recent experimental results in counterflow channels such as in Ref~\cite{marakov2015,gao2017,mastracci2019,yui2020}.
-In these work, the experimental team often report the observation of large-scale normal fluid turbulence in thermal counterflow, which is still unexplained.
+In these works, the experimental team often report the observation of large-scale normal fluid turbulence in thermal counterflow, which is still unexplained.
 In Ref.\cite{mastracci2019} the authors suggest that the large scale normal fluid turbulence may result from wake structures.
-Using data taken from a recent preprint \cite{galantucci2025} that three of us were part of, we calculated that the the flux of normal fluid due to wake structure is positive, implying an energy transfer to \emph{smaller} scales rather than larger scales.
+Using data taken from a recent preprint \cite{galantucci2025} that three of us were part of, we calculated that the the flux of normal fluid due to wake structure is positive, implying an energy transfer to \emph{smaller} scales rather than larger scales, suggesting that wake structures are not likely to be the reason behind the large-scale normal fluid turbulence observed.
 \\
@@
 
-In the revised manuscript, we have adapted the figures in the paper to use a normalization that is based on a temperature dependent scaling, which was the reason why the figures before showed an apparent inconsistency between the energy spectrum and the flux.
+In the revised manuscript, we have adapted the figures in the paper in order to use a normalization that is temperature independent scaling.
+%, which was the reason why the figures before showed an apparent inconsistency between the energy spectrum and the flux.
 The figures now show the same order as one would find when using dimensional units.
 
-\begin{thebibliography}{4}
-    \bibitem{marakov2015}
-    A.
+\refcomment{The finding of inverse energy transfer by single reconnection is
+interesting. However, other events cause forward energy transfer of
+normal fluid, e.g., nonlinear interaction, wake propagation, energy
+dissipations by mutual friction and viscosity, and so on. Therefore,
+it is unclear whether the inverse energy cascade of normal fluid is
+generated by reconnections in quantum turbulence. This stage is
+premature to recommend to Physical Review Letters.}
+
+\CHANGE{We think that by including the data regarding Hopf-link reconnections, we generalised our findings beyond a particular type of reconnection. This inverse energy transfer,
+triggered by classical-like phenomena (chiral imbalance, which as in classical turbulence produces energy flowing towards large scales), is strikingly dissimilar from 
+the direct energy transfer observed in vortex reconnections occurring in classical viscous fluids. Our work shows that vortex reconnections in quantum fluids may possess 
+different characteristics from the ones taking place in classical fluids, depending on the fluid component we focus on: if we analyse superfluid vortices, the approach and 
+separation is akin to classical dynamics (see our recent work, Stasiak et al., PNAS Vol. 122 No. 21 e2426064122 (2025)); if we observe the normal fluid we observe a non-classical 
+energy transfer. Furthermore, this work adds additional elements to the lively discussion in the community regarding similarities and differences between classical and quantum 
+turbulence. We think that together with the suggestion that reconnections may trigger an inverse energy cascade, these are the main findings of our investigation, which are of 
+relevance for a broad audience such as PRL's readers. We have slightly changed the conclusions to emphasise these aspects.}
+
+\subsection*{Referee B}
+
+%\begin{thebibliography}{4}
+%    \bibitem{marakov2015}
+%    A.
 Marakov, J.
@@
 
-    \bibitem{gao2017}
-    J. Gao, E. Varga, W. Guo, and W.F. Vinen, Energy spectrum of thermal counterflow turbulence in superfluid helium-4, \emph{Phys. Rev. B} \textbf{96}, 094511 (2017)
+%    \bibitem{gao2017}
+%    J. Gao, E. Varga, W. Guo, and W.F. Vinen, Energy spectrum of thermal counterflow turbulence in superfluid helium-4, \emph{Phys. Rev. B} \textbf{96}, 094511 (2017)
 
-    \bibitem{mastracci2019}
-    B.
+%    \bibitem{mastracci2019}
+%    B.
 Mastracci, S.
@@
 
-    \bibitem{yui2020}
-    S.
+%    \bibitem{yui2020}
+%    S.
 Yui, H.
@@
 
-    \bibitem{galantucci2025}
-    L. Galantucci, G. Krstulovic, and C. F. Barenghi, Quantum vortices leave a macroscopic signature in the normal fluid. \emph{arXiv preprint arXiv:2501.08309} (2025).
+%    \bibitem{galantucci2025}
+%    L. Galantucci, G. Krstulovic, and C. F. Barenghi, Quantum vortices leave a macroscopic signature in the normal fluid. \emph{arXiv preprint arXiv:2501.08309} (2025).
 
-\end{thebibliography}
+%\end{thebibliography}
 

### 2025-10-30 main_REV.tex
Major revisions to text- LG

--- 2025-10-06 main_REV.tex
@@
 \newcommand*{\NOTE}[1]{\textbf{\color{red}[#1]}}
-\newcommand*{\CHANGE}[1]{{\color{brown}#1}}
+\newcommand*{\CHANGE}[1]{{\color{magenta}#1}}
 \newcommand*{\DEL}[1]{{\color{green}#1}}
@@
 is injected 
-into the thermal (normal) component of helium~II at small length scales, but is transferred nonlinearly  to larger length scales, increasing the integral length scale of the normal
-fluid.  
+into the thermal (normal) component of helium~II at small length scales, but is transferred nonlinearly  to larger length scales, 
+increasing the integral length scale of the normal fluid.  
 We show that this inverse energy transfer is triggered by the helical imbalance generated 
@@
 	\caption{
+\CHANGE{
 Three-dimensional rendering of the time evolution of
-an initially orthogonal vortex configuration 
-undergoing a vortex reconnection at $T = 1.9$K at dimensionless
-times (from left to right)
-$(t-t_R)/\tau_R=-7.47\times10^{-2}$, $-3.09\times10^{-3}$, $8.79\times10^{-4}$ and $5.39\times10^{-3}$, where $\tau_R = L_R/E^{1/2}_R$.
-The quantities $E_R$ and $L_R$ are the energy $E$ and integral length scales $L$ of the normal fluid at reconnection time $t_R$.
-The green
-tubes represent the superfluid vortex lines (the tubes’ radii have been 
+an initially orthogonal superfluid vortex configuration 
+undergoing a reconnection at $t=t_R$. Temperature is $T = 1.9$K and time is made
+dimensionless with 
+% (from left to right) $(t-t_R)/\tau_R=-7.47\times10^{-2}$, $-3.09\times10^{-3}$, $8.79\times10^{-4}$ and $5.39\times10^{-3}$,
+$\tau_R = L^2/\kappa$. }
+Green tubes represent the superfluid vortex lines (the tubes’ radii have been 
 greatly exaggerated for visual purpose). In the top sequence,
@@
 $\bom^2/\bom^2_{max}$. Note the Kelvin wave on the superfluid
-vortex at $(t-t_R)/\tau_R=8.79\times10^{-4}$ . In the bottom sequence, the red/blue volume
+vortex at $(t-t_R)/\tau_R\approx0.001$. In the bottom sequence, the red/blue volume
 rendering at the same times represent scaled positive/negative normal fluid
@@
 Thus, as a consequence of vortex reconnections,
-we observe an increase of the chiral imbalance of the quantum fluid, producing a transfer of kinetic energy from small to large scales, similarly to the phenomenology observed in 3D helical-decimated classical flows.
+we observe an increase of the chiral imbalance of the quantum fluid, producing a transfer of kinetic energy from small to large scales, similarly to the phenomenology observed in 3D helically-decimated classical flows.
  Unlike classical fluids, such a chiral imbalance arises naturally as physical process in the normal fluid.% because of vortex reconnections. 
@@
 \begin{equation}
-    \dot{\s}(\xi,t) = \v_s + \frac{\beta}{1+\beta}\left[\v_{ns}\cdot\s'\right]\s' + \beta\s'\times\v_{ns} + \beta'\s'\times\left[\s'\times\v_{ns}\right],
+    \dot{\s}(\xi,t) = \v_s + \frac{\rho_n}{\rho}\left[\v_{ns}\cdot\s'\right]\s' + \beta\s'\times\v_{ns} + \beta'\s'\times\left[\s'\times\v_{ns}\right],
 \end{equation}
@@
 The regularisation of mutual friction is performed using a physically self-consistent scheme \cite{galantucciNewSelfconsistentApproach2020b}. %, gualtieri2015exact, gualtieri2017turbulence}. 
-We consider a periodical box of size $2\pi$ (so that  wavevectors are integers).
-
-To study the reconnection dynamics, we consider two pairs of initially orthogonal vortices (where the corresponding vortices of each pair have opposite circulation in order to preserve periodicity along the boundaries)
-at two distinct temperatures, $T=1.9K$ and $T=2.1K$.
-The vortex pairs are separated by the distance $D_{\ell}$; each vortex within each pair is initially at distance $d_{\ell}$ to the other vortex, such that $d_{\ell}\ll D_{\ell}$ to ensures that the dynamics in the vicinity of the reconnection is dominated by local interactions, and that the far-field contribution from the other vortex pair is negligible.
-All results reported hereafter refer only to the reconnection of one pair of vortices. 
+We consider a periodical box of size $L=2\pi$ (so that  wavevectors are integers).
+
+To study the reconnection dynamics, we consider 
+\CHANGE{
+two distinct initial conditions at temperatures $T=1.9K$ and $T=2.1K$: (a) a pair of initially orthogonal vortices (a second pair of orthogonal vortices, with
+corresponding vortices of each pair having opposite circulation, is included in the computation in order to preserve periodicity along the boundaries \cite{suppMat};  
+the vortex pairs are separated by the distance $D_{\ell}$, while each vortex within each pair is initially at distance $d_{\ell}$ to the other vortex, such that $d_{\ell}\ll D_{\ell}$ in order to ensure that the dynamics in the vicinity of the reconnection is dominated by local interactions); (b) a set of 49 Hopf-links,
+each consisting in two, perpendicular, linked vortex rings at varying initial distances from each other \cite{suppMat}.
+}
+
+%All results reported hereafter \red{related to the orthogonal reconnection} refer only to the reconnection of one pair of vortices. 
+%\red{In our findings we also report similar observations using Hopf-links from Ref.~\cite{stasiak2025experimental}, which we show in Fig.\ref{fig:total-helicity}.}
 %\red{In our simulations, the reconnections of the two pairs of vortices occur at different times; here we consider only the vortex dynamics up to and shortly after the first reconnection (see Fig.~\ref{fig:total-helicity}).
@@
 
-The evolution of the vortex reconnection of a single pair is reported in Fig.~\ref{fig:visualisation}. 
-The first row shows the reconnecting superfluid vortices (in green) accompanied by normal fluid structures generated by mutual friction, here displayed as enstrophy rendering $\bom(\x)^2=|\nabla\times \v_n|^2$.
-Such structures are the signature of the violent irreversible energy transfers in vortex reconnections
+The evolution of the reconnection of an initially orthogonal single vortex pair is reported in Fig.~\ref{fig:visualisation}. 
+The first row shows the reconnecting superfluid vortices (in green) accompanied by normal fluid structures generated by the mutual friction, 
+here displayed as enstrophy rendering $\bom(\x)^2=|\nabla\times \v_n|^2$. Such structures are the signature of the violent irreversible energy transfers in vortex reconnections 
 \cite{stasiak2025experimental}.
-The second row shows the rendering of the local helicity $H(\x)=\v_n\cdot\bom$, where we observe a clear local helicity production, with an abrupt change of sign due to the rearrangement of the vortex topology.
-Remarkably, during reconnection there is a net
-sudden normal fluid helicity production, as shown in Fig.~\ref{fig:total-helicity}. We will come back to this finding later.
+The second row of Fig.~\ref{fig:visualisation} shows the rendering of the local helicity density $H(\x)=\v_n\cdot\bom$: we observe a clear local helicity production, with an abrupt change of sign due to the rearrangement of the vortex topology.
+Remarkably, during the reconnection process there is a sudden net overall
+normal fluid helicity production, as shown in Fig.~\ref{fig:total-helicity} (a). 
+\CHANGE{
+Indeed, the temporal evolution of the total normal fluid helicity 
+$\mathcal{H} = \int_{\mathcal{V}}H(\x)dV$ computed over the entire volume $\mathcal{V}$ shows that at reconnection time $t_R$ there is a significant overall 
+injection of helicity of a given sign. In particular, in the reconnections we monitor the injected helicity is negative (positive) for the orthogonal (Hopf-link) 
+reconnections.
+}
+%We will come back to this finding later.
 \begin{figure}[t]
@@
 
+    %  \includegraphics[width=0.49\textwidth]{helicity_integralScale.pdf}
        \begin{subfigure}{0.49\textwidth}
@@
          \includegraphics*[width=\textwidth]{helicity_total.pdf}
-        \caption{}\label{fig:}
+    %     \caption{}\label{fig:}
      \end{subfigure}
@@
          \centering
-        \includegraphics*[width=\textwidth]{integral-scale-scaled.pdf}
-        \caption{}\label{fig:}
+         \includegraphics*[width=\textwidth]{energy-spec-scaled.pdf}
+    %     \caption{}\label{fig:}
 
      \end{subfigure}
-\caption{\blue{Temporal evolution of the normal fluid helicity $\mathcal{H} = \int_{\mathcal{V}}H(\x)dV$ computed over the entire volume $\mathcal{V}$.
-For superfluid helium, it is proper to make the helicity dimensionless in terms of $\kappa^2$.}
-%\red{The 3D rendering shows the asynchronous nature of the reconnections in the initial configuration, with the two reconnections occurring at different times; same colour scheme as in Fig.~\ref{fig:visualisation}.}
+\caption{\CHANGE{ \emph(a): Temporal evolution of the total normal fluid helicity $\mathcal{H}$, normalised by the quantum of circulation $\kappa$. 
+Bold solid lines refer to orthogonal reconnections, slightly faded lines refer to the set of Hopf-links reconnections. Red color refers to $T=1.9K$, blue to $T=2.1K$.
+\emph(b): Normal fluid kinetic energy spectrum $E(k)$ before 
+reconnection (dashed lines), at reconnection (solid lines) 
+and after reconnection (dotted lines), for a pair of initially orthogonal vortices. Red (blue) lins correspond to  $T=1.9K$ ($T=2.1K$).}
+%For superfluid helium, it is proper to make the helicity dimensionless in terms of $\kappa^2$.
 }
+%\red{The 3D rendering shows the asynchronous nature of the reconnections in the initial configuration, with the two reconnections occurring at different times; same colour scheme as in Fig.~\ref{fig:visualisation}.}                    }
 \label{fig:total-helicity}
@@
 where $E$ is the total normal fluid energy and $k$ is the magnitude of the three-dimensional wavenumber. 
-The energy at reconnection $E_R$ is given by $E(t_R)$, where $t_R$ is the time at reconnection.
-The energy spectrum $E(k)$ is displayed in Fig.~3a.
+%The energy at reconnection $E_R$ is given by $E(t_R)$, where $t_R$ is the time at reconnection.
+The energy spectrum $E(k)$ for orthogonal reconnections is displayed in Fig.~\ref{fig:total-helicity} (b) (corresponding plots for the
+Hopf-links reconnections show a similar behaviour \cite{suppMat}).
+It clearly emerges that, during the reconnection, energy is predominantly injected into the normal fluid at intermediate and small length scales. 
+For $kL>30$ in correspondence of the reconnection time $t_R$,
+we observe a significant increase of the normal fluid energy spectral density:
+$E(k,\, t\approx t_R)/E(k,\, t\ll t_R) \approx 10^2$. 
+%
+In the post-reconnection regime, we simultaneously observe a small 
+decrease of the spectrum at intermediate 
+and small scales ($kL > 30$) and an increase at large scales, 
+suggesting the existence of a mechanism by 
+which energy generated at small length scales is transferred to larger scales.
+
 \begin{figure}
     \centering
-    % \includegraphics[width=0.49\textwidth]{energy-flux-spec.pdf}
+    %\includegraphics[width=0.49\textwidth]{energySpec-fluxSpec.pdf}
 
@@
          \centering
-        \includegraphics*[width=\textwidth]{energy-spec-scaled.pdf}
-        \caption{}\label{fig:kinetic-energy}
+         \includegraphics*[width=\textwidth]{flux-spec-scaled.pdf}
+    %     \caption{}\label{fig:kinetic-energy}
      \end{subfigure}
@@
          \centering
-        \includegraphics*[width=\textwidth]{flux-spec-scaled.pdf}
-        \caption{}\label{fig:energy-flux}
+         \includegraphics*[width=\textwidth]{integral-scale-scaled.pdf}
+    %     \caption{}\label{fig:energy-flux}
      \end{subfigure}
-% \begin{subcaptiongroup*}
-% 	\phantomsubcaption\label{fig:minimum-distance}
-% 	\phantomsubcaption\label{fig:prefactors}
-% \end{subcaptiongroup*}
-
-    \caption{\emph{(a):} Normal fluid kinetic energy spectrum $E(k)$ before 
-reconnection (dashed lines), at reconnection (solid lines) 
-and after reconnection (dotted lines) for $T=1.9K$ (red)
-and $T=2.1K$ (blue).\emph{(b):} Spectral normal fluid kinetic energy flux, $\Pi (k)$. It is normalised using the integral scale and the normal fluid energy at reconnection.
-\emph{Inset:} Post reconnection evolution of the integral length scale, $L$.
-Times and temperatures are labelled as in Fig.~3a.}
+%\begin{subcaptiongroup*}
+%	\phantomsubcaption\label{fig:energy-spec}
+%	\phantomsubcaption\label{fig:flux-spec}
+%\end{subcaptiongroup*}
+
+    \caption{\CHANGE{
+    \emph{(a)}: Spectral normal fluid kinetic energy flux, $\Pi (k)$ for orthogonal reconnections. %, normalised using the box size $L$ and the quantum of circulation $\kappa$}. 
+    Times and temperatures are labelled as in Fig.~\ref{fig:total-helicity} (b).
+    \emph{(b)}: Post reconnection temporal evolution of the integral length scale, $L_0(t)$ scaled by the reconnection time integral scale $L_R=L_0(t_R)$. 
+    Slightly faded lines refer to the set of Hopf-links reconnections (left axis) and bold solid lines refer to orthogonal reconnections (right axis). 
+    Red (blue) lins correspond to  $T=1.9K$ ($T=2.1K$).}
+    }
 \label{fig:spectra}
@@
 
-It clearly emerges that, during the reconnection, energy is predominantly injected into the normal fluid at intermediate and small length scales. 
-For $k>5$ in correspondence of the reconnection time $t_R$,
-we observe a significant increase of the normal fluid energy spectral density:
-$E(k,\, t\approx t_R)/E(k,\, t\ll t_R) \approx 10^2$. 
-%
-In the post-reconnection regime, we simultaneously observe a small 
-decrease of the spectrum at intermediate 
-and small scales ($k > 5$) and an increase at large scales, 
-suggesting the existence of a mechanism by 
-which energy generated at small length scales is transferred to larger scales. 
 To shed light on this mechanism, as customary for turbulent flows, we analyse the spectral energy flux 
@@
 \end{equation}
-where $\widehat{\cdot}$ indicates the Fourier transform.
+where $\widehat{\cdot}$ indicates the Fourier transform. The computation of $\Pi(k)$ is reported in Fig.~\ref{fig:spectra} (a) 
+for orthogonal reconnections (similar behaviour is observed in Hopf-links reconnections \cite{suppMat}).
 
@@
 we also observe that, near the time of reconnection,
-the peak value of $|\Pi(k)|$ is in the range $15 < k < 25$.
+the peak value of $|\Pi(k)|$ is in the range \CHANGE{$50 < kL <150$}.
 %
@@
 % in Fig.~\ref{fig:visualisation}} \NOTE{GK: the figure shows small scale structures...}
-This behaviour is quantified by the evolution of the integral length scale $L$, defined as
+This behaviour is quantified by the temporal evolution of the integral length scale $L_0(t)$, defined as
 \begin{equation}
-    L = \frac{\pi}{2 E}\int_0^{\infty}\frac{E(k)}{k}dk, %\Big/ \int_0^{\infty}\!\!E(k)dk.
+    L_0(t) = \frac{\pi}{2 E}\int_0^{\infty}\frac{E(k,t)}{k}dk, %\Big/ \int_0^{\infty}\!\!E(k)dk.
 \end{equation}
-The inset of Fig.~3b shows that
-$L$ indeed  increases steadily in the post-reconnection regime. Note that times have been normalised by the largest eddy-turnover-time at the reconnection event, evidencing  it fast evolution.
-
-To explain the inverse energy transfer shown in Fig.~3b,
-we look whether the reconnection triggers a chirality imbalance. 
+\CHANGE{
+and reported in Fig.~\ref{fig:spectra} (b). The figure clearly shows that
+$L_0$ indeed increases steadily in the post-reconnection regime after a small transient in the Hopf-links configuration.}
+%Note that times have been normalised by the largest eddy-turnover-time at the reconnection event, evidencing  it fast evolution.
+
+To explain the inverse energy transfer shown in Fig.~\ref{fig:spectra} (b),
+we look whether the reconnection triggers a chirality imbalance in the flow.  
 We decompose the incompressible Fourier modes of the normal fluid velocity 
@@
 \textit{i.e.} if the ratio $|f^+|^2/|f^-|^2 \neq 1$, with $|f^\pm|^2$ the total squared norm of the mutual friction components. 
-In Fig.~\ref{fig:mutual-friction-decomp}, we show the temporal evolution of $|f^+|^2/|f^-|^2$, for both temperatures. 
+In Fig.~\ref{fig:mutual-friction-decomp}, we show the temporal evolution of $|f^+|^2/|f^-|^2$ for both temperatures, for orthogonal reconnections
+(Hopf-links reconnections show a similar behaviour \cite{suppMat}). 
 %
@@
     \includegraphics*[width=0.48\textwidth]{fmfDecompFig.pdf}
-    \caption{Temporal evolution of projected mutual friction force components $f^\pm$/ Inset: temporal evolution of total helical components.}.
+    \caption{Temporal evolution of the ratio of helically-projected mutual friction force components $f^\pm$, for orthogonal reconnections. 
+    Inset: temporal evolution of total helical components.}.
     \label{fig:mutual-friction-decomp}
@@
 decreases significantly at reconnection and remains smaller than unity even at later times, 
-indicating that the flow is persistently chiral. We conclude that the reconnection triggers indeed a chiral imbalance.
+indicating that the flow is persistently chiral. We conclude that the reconnection triggers indeed a chiral imbalance, \CHANGE{leading to the observed inverse energy transfer}.
 For the sake of completeness, it is worth noting that the total helicity of the flow (obtained by adding the superfluid helicity to that of the normal fluid $\mathcal{H}$) is not conserved.
@@
 \cite{biferaleInverseEnergyCascade2012a,plunianInverseCascadeEnergy2020a}.
+\CHANGE{
+This inverse energy transfer contrasts with the direct energy transfer observed 
+in classical vortex reconnections \cite{yao-hussain-2020} showing that vortex reconnections 
+in quantum fluids may show similarities and differences with their classical counterpart 
+depending on the fluid component investigated: if we consider the approach and separation 
+of superfluid vortex filaments, we recover a classical behaviour
+\cite{stasiak2025experimental}, while if we analyse the normal fluid energy transfer we
+observe a strong non-classical effect. The results presented hence contribute to 
+identifying similarities and differences between classical and quantum turbulence 
+\cite{galantucci-2025}. 
+}
 
@@
 the chirality of the flow generated by the 
-frequent non-symmetrical reconnections may be strong enough to induce an inverse energy cascade~\cite{notes_recon}.
+frequent, \CHANGE{likely} non-symmetrical, reconnections may be strong enough to induce an inverse energy cascade~\cite{notes_recon}.
 %The asymmetry of the reconnecting vortex configurations is a key element; 
@@
 Computations were carried out at the Mésocentre SIGAMM hosted at the Observatoire de la Côte d’Azur.
-
 \end{acknowledgments}
 
-% \bibliography{references}
+%\bibliography{references}
 
@@
 %Control: production of eprint (0) enabled
-\begin{thebibliography}{57}%
+\begin{thebibliography}{59}%
 \makeatletter
@@
   {24006} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Yao}\ and\ \citenamefont
+  {Hussain}(2020)}]{yao-hussain-2020}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Yao}}\ and\ \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Hussain}},\
+  }\bibfield  {title} {\bibinfo {title} {A physical model of turbulence cascade
+  via vortex reconnection sequence and avalanche},\ }\href
+  {https://doi.org/10.1017/jfm.2019.905} {\bibfield  {journal} {\bibinfo
+  {journal} {Journal of Fluid Mechanics}\ }\textbf {\bibinfo {volume} {883}},\
+  \bibinfo {pages} {A51} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Galantucci}(2025)}]{galantucci-2025}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Galantucci}},\ }\bibfield  {title} {\bibinfo {title} {Quantum turbulent
+  flows: a model for classical turbulence?},\ }\href
+  {https://doi.org/10.1017/jfm.2025.10730} {\bibfield  {journal} {\bibinfo
+  {journal} {Journal of Fluid Mechanics}\ }\textbf {\bibinfo {volume} {1022}},\
+  \bibinfo {pages} {F1} (\bibinfo {year} {2025})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Vinen}(1957)}]{vinen-1957a}%

### 2025-11-10 revision-2/referee-response.tex
GK corrections

@@
 
+We thank the Referee for reading our revised version.
+We would like to insist, as it seems that is has not yet realized by the Referee, that our work is not about explaining the findings of Polanco and Krstulovic about the inverse cascade observed in that work for high counterflow.
+We have only mentioned that there might be a connection, but no claim is made.
+As a matter of fact, the comment is mild and we suggest that further studies are needed, so we open an new possible avenue of research.
+We have not mentioned such a claim in the abstract and not even in the introduction.
+
+The referee make a claim that on head-on collision of quantum rings.
+We believe that the Referee is missing an important point.
+One could perhaps find a specific configuration such that the helicity imbalance is weaken or even suppressed.
+However, our point is that such is not the generic case, and it will not be relevant for experiments in quantum turbulence.
+The Referee should notice that in the orthogonal reconnection, discussed in the first version of our paper, the helicity for each pair is zero.
+In this revised version, we have included around 50 new reconnections of a Hopf-Link, which are topologically very different as the vortex filaments do have a non-zero initial helicity.
+The simulations of the Hopf-Link reproduce what we have observed with the orthogonal reconnection.
+We thus conclude, that our fining are robust and generic and physically relevant.
+
 %\begin{thebibliography}{4}

### 2025-11-10 main_REV.tex
GK corrections

@@
 \newcommand*{\CHANGE}[1]{{\color{magenta}#1}}
+\newcommand*{\GK}[1]{{\color{blue}#1}}
 \newcommand*{\DEL}[1]{{\color{green}#1}}
@@
 We numerically illustrate that during a superfluid vortex reconnection energy 
-is injected 
-into the thermal (normal) component of helium~II at small length scales, but is transferred nonlinearly  to larger length scales, 
-increasing the integral length scale of the normal fluid.  
-We show that this inverse energy transfer is triggered by the helical imbalance generated 
+is injected into the thermal (normal) component of helium~II at small length scales, but is transferred nonlinearly  to larger length scales, increasing the integral length scale of the normal fluid. 
+We show, \GK{by studying about fifty different reconnections,} that this inverse energy transfer is triggered by the helical imbalance generated 
 %at reconnection 
 in the normal fluid flow by
-the mutual friction force coupling the superfluid vortices and the normal component. We finally discuss
+the mutual friction force coupling the superfluid vortices and the normal component. 
+We finally discuss
 %by decomposing the velocity and the mutual friction (which couples superfluid and normal fluid) into helical modes, showing 
@@
 each consisting in two, perpendicular, linked vortex rings at varying initial distances from each other \cite{suppMat}.
-}
+}\GK{Note that the two types of initial conditions are topologically very different, as for the Hopf-Link the superfluid initial helicity is non-zero due to their linking (it is zero for the orthogonal case).
+For both configurations, the initial normal fluid helicity is zero.}
 
@@
 \cite{stasiak2025experimental}, while if we analyse the normal fluid energy transfer we
-observe a strong non-classical effect. The results presented hence contribute to 
+observe a strong non-classical effect.
+\GK{The robusteness of our results has been demonstrated by studying almost fifty different reconnections having an initial different topology.} The results presented hence contribute to
 identifying similarities and differences between classical and quantum turbulence 

### 2025-11-10 revision-2/editor_letter.tex
GK corrections

\documentclass[a4paper,10pt]{letter}
\usepackage[margin=1in]{geometry}
\usepackage{lipsum}
\usepackage{xcolor}
\def\red#1{\textcolor{black}{#1}}

\begin{document}

% Sender Information
% \begin{flushright}
%     \begin{tabular}{l}
%         \textbf{Piotr Stasiak} \\
%         School of Mathematics, Statistics and Physics\\
%         Newcastle University \\
%         Newcastle  upon Tyne \\
%         p.stasiak@newcastle.ac.uk \\
%         \today
%     \end{tabular}
% \end{flushright}

% \vspace{1cm}

% Recipient Information
The Editors,\\
Physical Review Letters\\
APS\\

\vspace{1cm}

Dear Editor,

\vspace{0.5cm}

We would like first to acknowledge the Refeerees for reading our last submission. We would like to request a third round of referral of our manuscript. Our request is based on the following points.

-  Referee A, has showed themself very positive about our work. In their first report, the Referee says ``\emph{While this finding is intriguing, several issues must be addressed before a recommendation for publication can be made.}'' Whereas in their second review, they concluded their report with ``\emph{This stage is premature to recommend to Physical Review Letters}'', which is not a rejection per se, but rather a request for for further improvements.  In their second report, there are only minor issues left, that we have carefully addressed in our answers. Moreover, we have included in this revised version of the manuscript an analysis of about fifty new reconnection events having a different initial topology. The new set of simulations confirms our original results and makes our results extremely robust.

- Referee B has shown some  bias and a non-professional behavior from their first report. The Referee has tried to build a complete case about one single sentence on our conclusions, which was indented to open a possible question leading to a new research project. We have tried to explain this issue to the Referee in our first answer, but they seem to have completely ignore it, maintaining their unprofessional aggressivity. Furthermore, it seems to us, that the Referee has tried to bring new arguments, simply in order to push down the manuscript, confirming our belief that the Referee has some type of conflict of interest from the beginning. For the sake of professionalism, we have written an answer to Referee B last report, but we are reluctant to think that their bias could change.

We therefore think that referral process has not been fair, and we would like thus to request that our revised version is sent back to Referee A and third Referee is solicited.

Thank you for considering this manuscript; we look forward to your response.

\vspace{1cm}

\textbf{Piotr Stasiak}\\
\textbf{Andrew Baggaley}\\
\textbf{Carlo Barenghi}\\
\textbf{Giorgio Krstulovic}\\
\textbf{Luca Galantucci}\\
\end{document}

### 2025-11-17 revision-2/referee-response.tex
Updated editor letter and referee responses - CFB

--- 2025-10-30 revision-2/referee-response.tex
@@
 
-Originally we wanted to include the plot of the superfluid helicity in the plot of the normal fluid helicity.
+\CHANGE{Originally we did not include the plot of the superfluid helicity
+as we wanted our paper to focus on the properties of the normal fluid.
+Following the reviewers' comments and for better
+clarity, we  now include a sentence
+which emphasizes that the total helicity (the sum of normal fluid's helicity
+and superfluid's helicity) is not conserved.}\\
+
+%Originally we wanted to include the plot of the superfluid helicity in the plot of the normal fluid helicity.
 We decided against this as in this paper we decide to only focus on the normal fluid aspect.
@@
 \CHANGE{
-To generalise our findings, we perform the study of the chiral imbalance generated by reconnections occurring in Hopf-links, constituted by two, linked, orthogonal vortex rings,
-whose initial relative position is varied (see new figures in Supplemental material). This allows to observe reconnections taking place at different angles.
-Also in this geometrical setting, we observe a strong helicity injection, an increase of the integral scale of the flow, negative spectral fluxes and mutual friction force 
-chirality. We have included the data referring to Hopf-link reconnections in the manuscript and in the Supplemental material.
-Hence, we can claim, with supporting evidence, that reconnections trigger inverse energy transfer. However, this transfer of energy towards large scales may lead
-to an inverse cascade only if reconnections are not exactly symmetrycal, \textit{i.e.} (simplifying) if the number of reconnections of a given type is not exactly balanced by 
-the same number of reconnections between vortices of opposite circulation. We suggest that this might be the case when symmetry is broken by external forcing, as in thermal counterflow.}
+To answer the Referee and generalise our findings, we have also
+performed a study of the chiral imbalance generated by reconnections 
+of Hopf-links (two linked vortex rings)
+whose initial relative position is varied.
+This allows to observe reconnections taking place at different 
+angles. For Hopft-links, we observe the same strong helicity injection, 
+increase of the 
+integral scale, negative spectral fluxes and mutual friction force 
+chirality  
+that we have observed for open orthogonal vortex lines. 
+These new results are described both in
+the manuscript and in the Supplemental material.
+Hence, we can claim with evidence that reconnections trigger inverse 
+energy transfer. However, we stress that
+this transfer of energy towards large scales may lead
+to an inverse cascade only if reconnections are not exactly symmetrical, 
+\textit{i.e.} (simplifying) if the number of reconnections of a given type 
+is not exactly balanced by the same number of reconnections between vortices of opposite circulation. We suggest that this might be the case when the
+flow's symmetry is broken by external forcing, as in thermal counterflow.}  \\
 
@@
 
-In the revised manuscript, we have adapted the figures in the paper in order to use a normalization that is temperature independent scaling.
+\CHANGE{The new figures which we present in the revised manuscrit use
+a temperature-independent normalization.
+%In the revised manuscript, we have adapted the figures in the paper in order to use a normalization that is temperature independent scaling.
 %, which was the reason why the figures before showed an apparent inconsistency between the energy spectrum and the flux.
-The figures now show the same order as one would find when using dimensional units.
+The figures now show the same order, expected by the Referee,
+as one would find when using dimensional units.} \\
 
@@
 separation is akin to classical dynamics (see our recent work, Stasiak et al., PNAS Vol. 122 No. 21 e2426064122 (2025)); if we observe the normal fluid we observe a non-classical 
-energy transfer. Furthermore, this work adds additional elements to the lively discussion in the community regarding similarities and differences between classical and quantum 
+energy transfer. Essentially, we have recognized a novel property of two-fluid
+hysdrodynamics. Furthermore, our work adds additional elements to the lively discussion in the community regarding similarities and differences between classical and quantum 
 turbulence. We think that together with the suggestion that reconnections may trigger an inverse energy cascade, these are the main findings of our investigation, which are of 
@@
 \subsection*{Referee B}
+
+We thank the Referee for reading our revised version.
+We would like to insist, as it seems that is has not yet realized by the Referee, that our work is not about explaining the findings of Polanco and Krstulovic about the inverse cascade observed in that work for high counterflow.
+We have only mentioned that there might be a connection, but no claim is made.
+As a matter of fact, the comment is mild and we suggest that further studies are needed, so we open an new possible avenue of research.
+We have not mentioned such a claim in the abstract and not even in the introduction.
+
+The referee make a claim about head-on collision of quantum rings. 
+One could perhaps find a specific configuration such that the helicity 
+imbalance is weakened or even suppressed, however, our point is that this
+is not necessarily the generic case and will not be relevant to experiments
+of quantum turbulence. The Referee should notice that for orthogonal 
+reconnection (discussed in the first version of our paper) the helicity 
+for each pair is zero. In this newly revised version, we have included 
+around 50 new reconnections of Hopf-links, which are topologically 
+very different, as the initial helicity is non-zero. These simulations of 
+Hopf-links reproduce what we have observed for orthogonal reconnections. 
+We thus conclude, that our finding are robust and generic,
+ and physically relevant.
 

### 2025-11-17 revision-2/editor_letter.tex
Updated editor letter and referee responses - CFB

@@
 
-We would like first to acknowledge the Refeerees for reading our last submission. We would like to request a third round of referral of our manuscript. Our request is based on the following points.
+We would like first to thank the Refeerees for reading our last submission. We would like to request a third round of referral of our manuscript. Our request is based on the following points.
 
--  Referee A, has showed themself very positive about our work.
-In their first report, the Referee says ``\emph{While this finding is intriguing, several issues must be addressed before a recommendation for publication can be made.}'' Whereas in their second review, they concluded their report with ``\emph{This stage is premature to recommend to Physical Review Letters}'', which is not a rejection per se, but rather a request for for further improvements.
-In their second report, there are only minor issues left, that we have carefully addressed in our answers.
-Moreover, we have included in this revised version of the manuscript an analysis of about fifty new reconnection events having a different initial topology.
-The new set of simulations confirms our original results and makes our results extremely robust.
+-  Referee A, has been very positive about our work. In the first report, 
+Referee A said ``\emph{While this finding is intriguing, several issues 
+must be addressed before a recommendation for publication can be made.}'' 
+In the second review, Referee A concluded with 
+``\emph{This stage is premature to recommend to Physical Review Letters}'', 
+which is not a rejection per se, but rather a request for for further 
+improvements.  In their second report, there are only minor issues left, 
+that we have now carefully addressed in our answers. Moreover, 
+in this newly revised version of the manuscript we have incuded an 
+analysis of about fifty new reconnection events having a different 
+initial topology. The new set of simulations confirms our original 
+results and makes our results extremely robust.
 
-- Referee B has shown some  bias and a non-professional behavior from their first report.
-The Referee has tried to build a complete case about one single sentence on our conclusions, which was indented to open a possible question leading to a new research project.
-We have tried to explain this issue to the Referee in our first answer, but they seem to have completely ignore it, maintaining their unprofessional aggressivity.
-Furthermore, it seems to us, that the Referee has tried to bring new arguments, simply in order to push down the manuscript, confirming our belief that the Referee has some type of conflict of interest from the beginning.
-For the sake of professionalism, we have written an answer to Referee B last report, but we are reluctant to think that their bias could change.
+- Referee B has shown bias and non-professional behavior from their first 
+report. The Referee has tried to build a complete case against our work
+based on a single sentence in our conclusion section, which was only indented 
+to open a possible question leading to a new research project. 
+We explained this issue in our first revision, but the the Referee
+unprofessionally ignored it. Furthermore, it seems to us that the Referee 
+has tried to bring new arguments simply in order to push down the manuscript, 
+confirming our belief that there is some conflict of interest.
+For professional sake, we answered the last report of Referee B, 
+but we doubt that their bias could change.
 
-We therefore think that referral process has not been fair, and we would like thus to request that our revised version is sent back to Referee A and third Referee is solicited.
+We therefore think that referral process has not been entirely fair: 
+we would like 
+thus to request that our revised version is sent back to Referee A and 
+third Referee is solicited.
 

### 2025-11-17 supp-mat/supp-mat.tex
Updated editor letter and referee responses - CFB

@@
 
-A \emph{two-way model} is crucial to understand the accurately interept the back-reaction effect of the normal fluid on the vortex line and vice-versa \cite{stasiakCrossComponentEnergyTransfer2024}.
+A \emph{two-way model} is crucial to understand the accurately interpret the back-reaction effect of the normal fluid on the vortex line and vice-versa \cite{stasiakCrossComponentEnergyTransfer2024}.
 We self-consistently evolve the normal fluid $\v_n$ with a modified Navier-Stokes equation
@@
 
+\section{Helical decomposition of the hopf link}
+
 \bibliography{references}% Produces the bibliography via BibTeX.

### 2025-11-17 main_REV.tex
Updated manuscript with revised figures

@@
 Reconnections occur frequently in 3D quantum turbulence and are essential to
-the energy transfer towards small scales by engendering the the breakdown of coherent vortex structures
+the energy transfer towards small scales by engendering the breakdown of coherent vortex structures
 and triggering the Kelvin-wave cascade \cite{vinen-2001}.
@@
 we observe an increase of the chiral imbalance of the quantum fluid, producing a transfer of kinetic energy from small to large scales, similarly to the phenomenology observed in 3D helically-decimated classical flows.
- Unlike classical fluids, such a chiral imbalance arises naturally as physical process in the normal fluid.% because of vortex reconnections. 
+ Unlike classical fluids, such a chiral imbalance arises naturally as a physical process in the normal fluid.% because of vortex reconnections. 
 %This is contrast to classical fluid dynamics,  where the helical characteristics of the flows producing 
@@
 
-    %  \includegraphics[width=0.49\textwidth]{helicity_integralScale.pdf}
-       \begin{subfigure}{0.49\textwidth}
-         \centering
-         \includegraphics*[width=\textwidth]{helicity_total.pdf}
-    %     \caption{}\label{fig:}
-     \end{subfigure}
-     \begin{subfigure}{0.49\textwidth}
-         \centering
-         \includegraphics*[width=\textwidth]{energy-spec-scaled.pdf}
-    %     \caption{}\label{fig:}
-
-     \end{subfigure}
+    \includegraphics[width=0.49\textwidth]{helicity_and_energy-spectrum.pdf}
+    %    \begin{subfigure}{0.49\textwidth}
+    %      \centering
+    %      \includegraphics*[width=\textwidth]{helicity_total.pdf}
+    % %     \caption{}\label{fig:}
+    %  \end{subfigure}
+    %  \begin{subfigure}{0.49\textwidth}
+    %      \centering
+    %      \includegraphics*[width=\textwidth]{energy-spec-scaled.pdf}
+    % %     \caption{}\label{fig:}
+
+    %  \end{subfigure}
 \caption{\CHANGE{ \emph(a): Temporal evolution of the total normal fluid helicity $\mathcal{H}$, normalised by the quantum of circulation $\kappa$. 
@@
     \centering
-    %\includegraphics[width=0.49\textwidth]{energySpec-fluxSpec.pdf}
-
-     \begin{subfigure}{0.49\textwidth}
-         \centering
-         \includegraphics*[width=\textwidth]{flux-spec-scaled.pdf}
-    %     \caption{}\label{fig:kinetic-energy}
-     \end{subfigure}
-     \begin{subfigure}{0.49\textwidth}
-         \centering
-         \includegraphics*[width=\textwidth]{integral-scale-scaled.pdf}
-    %     \caption{}\label{fig:energy-flux}
-     \end{subfigure}
+    \includegraphics[width=0.49\textwidth]{flux_and_integral-scale.pdf}
+
+    %  \begin{subfigure}{0.49\textwidth}
+    %      \centering
+    %      \includegraphics*[width=\textwidth]{flux-spec-scaled.pdf}
+    % %     \caption{}\label{fig:kinetic-energy}
+    %  \end{subfigure}
+    %  \begin{subfigure}{0.49\textwidth}
+    %      \centering
+    %      \includegraphics*[width=\textwidth]{integral-scale-scaled.pdf}
+    % %     \caption{}\label{fig:energy-flux}
+    %  \end{subfigure}
 %\begin{subcaptiongroup*}

### 2025-11-19 main_REV.tex
Final update to manuscript - PZS
Final update of paper
Cleaned the directory

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newcommand*{\NOTE}[1]{\textbf{\color{red}[#1]}}
-\newcommand*{\CHANGE}[1]{{\color{magenta}#1}}
-\newcommand*{\GK}[1]{{\color{blue}#1}}
-\newcommand*{\DEL}[1]{{\color{green}#1}}
+\newcommand*{\NOTE}[1]{\textbf{\color{black}[#1]}} %Red
+\newcommand*{\CHANGE}[1]{{\color{black}#1}}    %Magenta
+\newcommand*{\GK}[1]{{\color{black}#1}}           %Blue
+\newcommand*{\DEL}[1]{{\color{black}#1}}         %Green
 
@@
 %The rate of change $I^\pm(\k)$ of the energies $E^{\pm}(\k)$ arising from the mutual friction is proportional to the corresponding helical coefficients $f^\pm$, \textit{i.e.} $I^\pm(\k) = \mathrm{Re} [f^\pm (v_n^\pm)^*] /\rho_n$, and the related signed helicity injection is $I_H^\pm(\k) = k \mathrm{Re} [f^\pm (v_n^\pm)^*] /\rho_n$.
-
 A chiral imbalance occurs if the mutual friction force is helical, 
-\textit{i.e.} if the ratio $|f^+|^2/|f^-|^2 \neq 1$, with $|f^\pm|^2$ the total squared norm of the mutual friction components. 
-In Fig.~\ref{fig:mutual-friction-decomp}, we show the temporal evolution of $|f^+|^2/|f^-|^2$ for both temperatures, for orthogonal reconnections
+\textit{i.e.} if $\mathcal{F}_R \neq 1$, where
+\begin{equation}
+	\mathcal{F}_R(t) = \frac{\int dk |f^+(k,t)|^2}{\int dk |f^-(k,t)|^2},
+\end{equation}
+with $|f^\pm|^2$ the squared norm of the mutual friction
+helical decomposition coefficients. 
+In Fig.~\ref{fig:mutual-friction-decomp}, we show the temporal evolution of $\mathcal{F}_R$ for both temperatures, for orthogonal reconnections
 (Hopf-links reconnections show a similar behaviour \cite{suppMat}). 
@@
     \centering
-    \includegraphics*[width=0.48\textwidth]{fmfDecompFig.pdf}
+    \includegraphics*[width=0.48\textwidth]{fmfDecompFig-1.pdf}
     \caption{Temporal evolution of the ratio of helically-projected mutual friction force components $f^\pm$, for orthogonal reconnections. 
-    Inset: temporal evolution of total helical components.}.
+    Inset: temporal evolution of total helical components.}
     \label{fig:mutual-friction-decomp}
@@
 For the sake of completeness, it is worth noting that the total helicity of the flow (obtained by adding the superfluid helicity to that of the normal fluid $\mathcal{H}$) is not conserved.
-From Fig.~\ref{fig:mutual-friction-decomp}, we consider a time $t^*$ after reconnection where the ratio $|f^+|^2/|f^-|^2$ has sufficiently decayed to a roughly 5\% difference and we determine the non-dimensional timescale $\tau = (t^*-t_R)/\tau_R$ during which the mutual friction force is chiral as a result of reconnections: $\tau \approx 0.01$ and $\tau \approx 0.005$
+From Fig.~\ref{fig:mutual-friction-decomp}, we consider a time $t^*$ after reconnection where the ratio $\mathcal{F}_R$ has sufficiently decayed to a roughly 5\% difference and we determine the non-dimensional timescale $\tau = (t^*-t_R)/\tau_R$ during which the mutual friction force is chiral as a result of reconnections: $\tau \approx 0.01$ and $\tau \approx 0.005$
 for $T=1.9$K and $T=2.1$K, respectively, corresponding dimensionally to $\tau \approx 0.1$s for both temperatures. 
